### 2024-06-10 paper.tex
paper

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2024

% submissions should not be anonymous, so use the 
% [preprint] option:
\usepackage[preprint]{paper}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib,preprint]{neurips_2024}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

\title{Smart Model Elimination for Efficient Automated Machine Learning}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  Eric Su Zhang\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  St. Mark's School of Texas\\
  10600 Preston Rd, Dallas, TX 75230\\
  \texttt{ericspring08@gmail.com} \\
  % examples of more authors
  \And
  Benjamin Standefer \\
  St. Mark's School of Texas \\
  10600 Preston Rd, Dallas, TX 75230 \\
  \texttt{bjmstandefer@gmail.com} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\begin{document}

\maketitle

\begin{abstract}
  Automated Machine Learning or AutoML has emerged as a popular field of research. Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated. We propose a novel framework that automatically eliminates models that are unlikely to be performant by training a Boosting Model on hundreds of kaggle datasets. Out of the 30 model options, our framework can predict a top five model within its top eight 80\% of the time.
\end{abstract}

\section{Submission of papers to NeurIPS 2024}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NeurIPS 2024 must be prepared according to the
instructions presented here. Papers may only be up to {\bf four} pages long,
including figures. 
In these four content pages, authors may link to supplementary artifacts including videos, working demonstrations, digital posters, websites, or source code.  
Please do not link to additional text.  
All such supplementary material should be wholly created by the authors and should directly support the submission content. 
Additional pages \emph{containing only acknowledgments and
references} are allowed. Papers that exceed the page limit will not be
reviewed or in any other way considered for presentation.

The margins in 2024 are the same as those in previous years of the NeurIPS conference.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Style files}

The file \verb+neurips_hs_2024.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2024 is \verb+neurips_2024.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
  Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{Preprint option}
As the high school project submissions are not anonymous, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. 
Please \textbf{do
  not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted at NeurIPS.

The file \verb+neurips_hs_2024.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper nouns),
flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2024+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{neurips_2024}
\end{verbatim}

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote, indicate
footnotes with a number\footnote{Sample of the first footnote.} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark enough for
purposes of reproduction. The figure number and caption always appear after the
figure. Place one line space before the figure caption and one line space after
the figure. The figure caption should be lower case (except for first word and
proper nouns); figures are numbered consecutively.

You may use color figures.  However, it is best for the figure captions and the
paper body to be legible if the paper is printed in either black/white or in
color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Math}
Note that display math in bare TeX commands will not create correct line numbers for submission. Please use LaTeX (or AMSTeX) commands for unnumbered display math. (You really shouldn't be using \$\$ anyway; see \url{https://tex.stackexchange.com/questions/503/why-is-preferable-to} and \url{https://tex.stackexchange.com/questions/40492/what-are-the-differences-between-align-equation-and-displaymath} for more information.)

\subsection{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
  available out-of-the-box on most Linux machines.

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
  "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
  the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\begin{ack}
Use unnumbered first level headings for the acknowledgments. All acknowledgments
go at the end of the paper before the list of references. Moreover, you are required to declare
funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2024/PaperInformation/FundingDisclosure}.
\end{ack}

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
Note that the Reference section does not count towards the page limit.
\medskip

{
\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
}

\end{document}

### 2024-06-10 MTF/gen_dataset.py

@@ -8,102 +8,99 @@ from models import classifiers
 import time
 import os
 
-# Parse arguments
-parser = ap.ArgumentParser(description='Generate dataset')
-parser.add_argument('-i', '--input', type=str,
-                    help='input_dataset', required=True)
-parser.add_argument('-o', '--output', type=str,
-                    help='output_dataset', required=True)
 
-args = parser.parse_args()
-
-
-# Load dataset
-df = pd.read_csv(args.input)
+def gen_dataset(input, output):
+    # Load dataset
+    try:
+        df = pd.read_csv(input)
 
 # check if dataset is greater than 10000
-if df.shape[0] > 10000:
-    df = df.sample(10000)
+        if df.shape[0] > 2000:
+            df = df.sample(2000)
 # extract last column as target
-target = df.iloc[:, -1]
-df.drop(df.columns[-1], axis=1, inplace=True)
+        target = df.iloc[:, -1]
+        df.drop(df.columns[-1], axis=1, inplace=True)
 
 # convert target to binary
 # get the unique values
-unique_values = target.unique()
+        unique_values = target.unique()
 
 # check if the target is binary
-if len(unique_values) > 2:
-    print('Target is not binary')
-    raise ValueError('Target must be binary')
-else:
-    # convert to binary
-    target = target.apply(lambda x: 1 if x == unique_values[0] else 0)
+        if len(unique_values) > 2:
+            print('Target is not binary')
+            return "Target is not binary"
+        else:
+            # convert to binary
+            target = target.apply(lambda x: 1 if x == unique_values[0] else 0)
 
-numerical_features = []
-categorical_features = []
+        numerical_features = []
+        categorical_features = []
 
 # Loop through all columns
-for col in df.columns:
-    # Check if column is numeric
-    # check the number of unique values
-    if df[col].nunique() > 15:
-        numerical_features.append(col)
-    else:
-        categorical_features.append(col)
+        for col in df.columns:
+            # Check if column is numeric
+            # check the number of unique values
+            if df[col].nunique() < 15 or df[col].dtype == 'object':
+                categorical_features.append(col)
+            else:
+                numerical_features.append(col)
 
-scaler = MinMaxScaler()
+        scaler = MinMaxScaler()
 
 # replace with mode for unknown values
-df = df.fillna(df.mode().iloc[0])
+        df = df.fillna(df.mode().iloc[0])
 
-preprocessor = ColumnTransformer(
-    transformers=[('ohe',
-                   OneHotEncoder(handle_unknown='ignore',
[…]

### 2024-06-10 MTF/get_attributes.py

@@ -1,0 +1,105 @@
+import numpy as np
+import pandas as pd
+import os
+
+
+def get_attributes(data_path):
+    data = pd.read_csv(data_path)
+    # Get the attributes of the data
+    attributes = {}
+
+    # Get the number of rows and columns
+    attributes['num_rows'] = data.shape[0]
+    print("Number of rows: ", data.shape[0])
+    attributes['num_cols'] = data.shape[1]
+    print("Number of columns: ", data.shape[1])
+
+    # get the output distribution of 1 percentage
+    attributes['output_distribution'] = max(data.iloc[:, -
+                                                      1].value_counts(normalize=True))
+    print("Output distribution: ", max(
+        data.iloc[:, -1].value_counts(normalize=True)))
+
+    # Get the percenage of missing values in dataset
+    attributes['missing_values'] = data.isnull().sum().sum() / \
+        (data.shape[0] * data.shape[1])
+    print("Missing values: ", data.isnull().sum().sum())
+
+    # get percentage of numerical and categorical columns
+    numerical_features = 0
+    binary_categorical = 0
+    categorical_average_count = 0
+    categorical_count = 0
+    iqr_values = []
+    q1_values = []
+    q3_values = []
+    for col in data.columns:
+        if data[col].nunique() > 15:
+            numerical_features += 1
+
+            # get the interquartile range
+            q1 = data[col].quantile(0.25)
+            q3 = data[col].quantile(0.75)
+            iqr = q3 - q1
+
+            iqr_values.append(iqr)
+            q1_values.append(q1)
+            q3_values.append(q3)
+        else:
+            categorical_count += 1
+            # categorical
+            # check if binary or not
+            if data[col].nunique() == 2:
+                binary_categorical += 1
+
+            categorical_average_count += data[col].nunique()
+
+    attributes['numerical_columns'] = numerical_features/data.shape[1]
+    attributes['binary_categorical'] = binary_categorical/categorical_count
+    attributes['categorical_average_count'] = categorical_average_count / \
+        categorical_count
+    attributes['average_iqr'] = np.mean(iqr_values)
+    attributes['average_q1'] = np.mean(q1_values)
+    attributes['average_q3'] = np.mean(q3_values)
+    attributes['iqr_std'] = np.mean(np.std(iqr_values))
+    attributes['q1_std'] = np.mean(np.std(q1_values))
[…]

### 2024-06-10 MTF/run_gen_dataset.py

@@ -1,6 +1,9 @@
 import os
 import argparse as ap
 import subprocess
+from gen_dataset import gen_dataset
+from get_attributes import get_attributes
+import pandas as pd
 
 parser = ap.ArgumentParser(description='Generate datasets')
 
@@ -24,10 +27,31 @@ output_folder = args.output
 # read the datasets folder
 datasets = os.listdir(datasets_folder)
 
+columns = ["num_rows", "num_cols", "output_distribution", "missing_values",
+           "numerical_columns", "binary_categorical",
+           "categorical_average_count", "average_iqr", "average_q1",
+           "average_q3", "iqr_std", "q1_std", "q3_std",
+           "z_score_average", "z_score_std", "average_correlation",
+           "correlation_std", "dataset"]
+
+attributes_df = pd.DataFrame(columns=columns)
+
 for index, dataset in enumerate(datasets):
     if dataset.endswith('.csv'):
         print(f"[{index}] Generating {dataset}")
         # print subprocess output
-        result = subprocess.run(
-            f"python3 gen_dataset.py -i {datasets_folder}/{dataset} -o {os.path.join(output_folder, dataset.split('.')[0])}", shell=True, capture_output=True)
-        print(result.stdout.decode('utf-8'))
+        error_ = gen_dataset(os.path.join(datasets_folder, dataset),
+                             os.path.join(output_folder, dataset.split('.')[0]))
+
+        if error_:
+            print(f"Error: {error_}")
+            continue
+
+        attributes = get_attributes(os.path.join(
+            output_folder, dataset.split('.')[0], 'dataset.csv'))
+
+        attributes['dataset'] = dataset
+
+        attributes_df = attributes_df._append(attributes, ignore_index=True)
+
+attributes_df.to_csv('attributes.csv', index=False)

### 2024-06-10 MTF/test.py

@@ -1,0 +1,65 @@
+import os
+import argparse as ap
+import subprocess
+from gen_dataset import gen_dataset
+from get_attributes import get_attributes
+import pandas as pd
+
+datasets_folder = "../kaggle-dataset-download/DATASETS/"
+
+# read the datasets folder
+datasets = os.listdir(datasets_folder)
+
+columns = ["num_rows", "num_cols", "output_distribution", "missing_values",
+           "numerical_columns", "binary_categorical",
+           "categorical_average_count", "average_iqr", "average_q1",
+           "average_q3", "iqr_std", "q1_std", "q3_std",
+           "z_score_average", "z_score_std", "average_correlation",
+           "correlation_std", "dataset"]
+
+attributes_df = pd.DataFrame(columns=columns)
+
+count_target_by_name = 0
+count_target_by_last = 0
+combined = 0
+
+for index, dataset in enumerate(datasets):
+    if dataset.endswith('.csv'):
+        # check if are column names
+        try:
+            df = pd.read_csv(datasets_folder + dataset)
+            columns = df.columns
+
+            possible_target_columns = ["target", "class", "label", "output", "y", "target_variable", "disease", "diag",
+                                       "diagnosis", "result", "status", "outcome", "response", "response_variable", "dependent_variable", "dependent"]
+
+            # lowercase every column name
+            columns = [column.lower() for column in columns]
+
+            target_column_val = "None"
+            # check if there is a possible target column
+            for target_column in possible_target_columns:
+                if target_column in columns:
+                    if df[target_column].nunique() == 2:
+                        count_target_by_name += 1
+                        target_column_val = df[target_column].unique()
+                        break
+
+            # check if last column is binary
+            last_column = df.columns[-1]
+
+            if df[last_column].nunique() == 2:
+                count_target_by_last += 1
+
+            print(
+                f"Dataset {index + 1}/{len(datasets)}: {dataset} - {df.shape} - {target_column} - {count_target_by_last} - {count_target_by_name} - {combined}")
+
+            # if either
+            if any(target_column in columns for target_column in possible_target_columns) or df[last_column].nunique() == 2:
+                combined += 1
+        except:
+            pass
+
+print(f"Count target by last column: {count_target_by_last}")
+print(f"Count target by name: {count_target_by_name}")
+print(f"Combined: {combined}")

### 2024-06-10 paper.tex
start intro

@@
 
-\section{Submission of papers to NeurIPS 2024}
+\section{Introduction}
 
-Please read the instructions below carefully and follow them faithfully.
+Machine learning (ML) is a type of artificial intelligence (AI) that uses a variety of algorithms to interpret data and extrapolate from it, making predictions based on observed trends.
+Individual models are trained on datasets to become smarter so as to make predictions based on new data.
+The development and optimization of these models is a time-consuming process involving statistical nuances and complex learning strategies.
+This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research.
+
+One sector of the global industry that has the most potential for beneficial integration of AutoML frameworks is healthcare, particularly in developing countries.
+These countries have severe shortages of healthcare workers and limited tools for diagnosis.
+For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000.
+The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030.
+The use of AI in healthcare has been varied.
+Medical AI's typically automate repetitive tasks, making time consumption a primary concern.
+This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue.
+
+Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected.
+However, these frameworks require that every model to be run to filter out.
+In theory, this means that much energy is spent training models that are unlikely to be selected.
+We propose SMEML, a novel model selection algorithm that automatically eliminates models that it believes will not be performant.
 

### 2024-06-11 paper.tex
all section names

@@
 
-\subsection{Style}
+\subsection{Survey}
 
-Papers to be submitted to NeurIPS 2024 must be prepared according to the
-instructions presented here. Papers may only be up to {\bf four} pages long,
-including figures. 
-In these four content pages, authors may link to supplementary artifacts including videos, working demonstrations, digital posters, websites, or source code.  
-Please do not link to additional text.  
-All such supplementary material should be wholly created by the authors and should directly support the submission content. 
-Additional pages \emph{containing only acknowledgments and
-references} are allowed. Papers that exceed the page limit will not be
-reviewed or in any other way considered for presentation.
+\section{Methodology}
 
-The margins in 2024 are the same as those in previous years of the NeurIPS conference.
+\subsection{Data Collection}
 
-Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
-NeurIPS website as indicated below. Please make sure you use the current files
-and not previous versions. Tweaking the style files may be grounds for
-rejection.
+\subsection{Model Elimination}
 
-\subsection{Style files}
+\section{Experiments}
 
-The file \verb+neurips_hs_2024.pdf+ contains these instructions and illustrates the
-various formatting requirements your NeurIPS paper must satisfy.
+\section{Discussion}
 
-The only supported style file for NeurIPS 2024 is \verb+neurips_2024.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
-  Microsoft Word, and RTF are no longer supported!}
-
-The \LaTeX{} style file contains three optional arguments: \verb+final+, which
-creates a camera-ready copy, \verb+preprint+, which creates a preprint for
-submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
-\verb+natbib+ package for you in case of package clash.
-
-\paragraph{Preprint option}
-As the high school project submissions are not anonymous, please use the \verb+preprint+ option. This will create a
-nonanonymized version of your work with the text ``Preprint. Work in progress.''
-in the footer. 
-Please \textbf{do
-  not} use the \verb+final+ option, which should \textbf{only} be used for
-papers accepted at NeurIPS.
-
-The file \verb+neurips_hs_2024.tex+ may be used as a ``shell'' for writing your
-paper. All you have to do is replace the author, title, abstract, and text of
-the paper with your own.
-
-The formatting instructions contained in these style files are summarized in
-Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas) wide and
-9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
-type with a vertical spacing (leading) of 11~points.  Times New Roman is the
-preferred typeface throughout, and will be selected for you by default.
-Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
-indentation.
-
-The paper title should be 17~point, initial caps/lower case, bold, centered
-between two horizontal rules. The top rule should be 4~points thick and the
-bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
-below the title to rules. All pages should start at 1~inch (6~picas) from the
-top of the page.
-
-For the final version, authors' names are set in boldface, and each name is
-centered above the corresponding address. The lead author's name is to be listed
-first (left-most), and the co-authors' names (if different address) are set to
-follow. If there is only one co-author, list both author and co-author side by
-side.
-
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-\section{Headings: first level}
-\label{headings}
-
-All headings should be lower case (except for first word and proper nouns),
-flush left, and bold.
-
-First-level headings should be in 12-point type.
-
-\subsection{Headings: second level}
-
-Second-level headings should be in 10-point type.
-
-\subsubsection{Headings: third level}
-
-Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the heading in
-bold, flush left, and inline with the text, with the heading followed by 1\,em
-of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.  Citations may be
-author/year or numeric, as long as you maintain internal consistency.  As to the
-format of the references themselves, any style is acceptable as long as it is
-used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations appropriate for
-use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may add the
-following before loading the \verb+neurips_2024+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add the optional
-argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{neurips_2024}
-\end{verbatim}
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote, indicate
-footnotes with a number\footnote{Sample of the first footnote.} in the
-text. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a horizontal rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-\begin{figure}
-  \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-All artwork must be neat, clean, and legible. Lines should be dark enough for
-purposes of reproduction. The figure number and caption always appear after the
-figure. Place one line space before the figure caption and one line space after
-the figure. The figure caption should be lower case (except for first word and
-proper nouns); figures are numbered consecutively.
-
-You may use color figures.  However, it is best for the figure captions and the
-paper body to be legible if the paper is printed in either black/white or in
-color.
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible.  The table number and
-title always appear before the table.  See Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical rules.} We
-strongly suggest the use of the \verb+booktabs+ package, which allows for
-typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
-\begin{table}
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule(r){1-2}
-    Name     & Description     & Size ($\mu$m) \\
-    \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\subsection{Math}
-Note that display math in bare TeX commands will not create correct line numbers for submission.
-Please use LaTeX (or AMSTeX) commands for unnumbered display math.
-(You really shouldn't be using \$\$ anyway; see \url{https://tex.stackexchange.com/questions/503/why-is-preferable-to} and \url{https://tex.stackexchange.com/questions/40492/what-are-the-differences-between-align-equation-and-displaymath} for more information.)
-
-\subsection{Final instructions}
-
-Do not change any aspects of the formatting parameters in the style files.  In
-particular, do not modify the width or length of the rectangle the text should
-fit into, and do not change font sizes (except perhaps in the
-\textbf{References} section; see below). Please note that pages should be
-numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and not, for
-example, ``A4.''
-
-Your PDF file must only
-contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
-achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
-  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
-  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
-  available out-of-the-box on most Linux machines.
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
-  "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
-  the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
-for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
-workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
-you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
-figure width as a multiple of the line width as in the example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly hyphenate a
-line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
-necessary.
+\section{Conclusion}
 
 \begin{ack}
-Use unnumbered first level headings for the acknowledgments. All acknowledgments
-go at the end of the paper before the list of references. Moreover, you are required to declare
-funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
-More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2024/PaperInformation/FundingDisclosure}.
+
 \end{ack}
@@
 
-References follow the acknowledgments. Use unnumbered first-level heading for
-the references. Any choice of citation style is acceptable as long as you are
-consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
-when listing the references.
-Note that the Reference section does not count towards the page limit.
 \medskip
-
 {
@@
 
-[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
-connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
-(eds.), {\it Advances in Neural Information Processing Systems 7},
-pp.\ 609--616. Cambridge, MA: MIT Press.
-
-[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
-  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
-TELOS/Springer--Verlag.
-
-[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
-recall at excitatory recurrent synapses and cholinergic modulation in rat
-hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
-}
+% references here
 

### 2024-06-11 paper.tex
Update paper.tex
added table

@@
 
+\documentclass{article}
+\usepackage{geometry}
+\usepackage{longtable}
+\usepackage{graphicx}
+
+\geometry{a4paper, margin=1in}
+
+\begin{document}
+
+\begin{longtable}{|l|l|l|l|l|}
+\hline
+\textbf{Factor} & \textbf{H2O} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} \\
+\hline
+\endfirsthead
+
+\multicolumn{5}{c}%
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} \\
+\hline
+\endhead
+
+\hline \multicolumn{5}{|r|}{\textit{Continued on next page}} \\
+\hline
+\endfoot
+
+\hline
+\endlastfoot
+
+\textbf{Ease of Use} & Easy-to-use GUI and API & Python library, requires coding experience & Very user-friendly web interface, detailed API & Simple API \\
+\hline
+\textbf{Supported Algorithms} & Linear, Tree, DNN, Clustering, etc.
+& Genetic Programming & Linear, Tree, LightGBM, CatBoost, Clustering, etc.
+(no DNN) & Linear, Tree, Clustering - More limited and lightweight \\
+\hline
+\textbf{Feature Engineering} & Basic & Basic & Advanced - includes feature interactions & Limited \\
+\hline
+\textbf{Time Management} & Time Constraints are Settable & Generations and population size & Time constraints are Settable & Optimized for quick results \\
+\textbf{Ensemble Methods} & Yes & Yes & Yes & Yes \\
+\hline
+\textbf{Hyperparameter Tuning} & Automated & Genetic algorithm & Automated and customizable & Automated and efficient tuning \\
+\hline
+\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) \\
+\hline
+\hline
+\textbf{Scalability} & Good (distributed computing) & Limited & Good & Good (resource-efficient) \\
+\hline
+\textbf{Customization} & High & Moderate & High & Low-Moderate \\
+\hline
+
+\end{longtable}
+
+\end{document}
+
 \section{Methodology}

### 2024-06-12 MTF/convert_to_image.py
good results

@@ -1,23 +1,0 @@
-import argparse as ap
-import os
-import pandas as pd
-import matplotlib.pyplot as plt
-
-parser = ap.ArgumentParser()
-
-parser.add_argument('-f', help='Folder')
-
-args = parser.parse_args()
-
-folder = args.f
-
-# go through all the files in the folder
-for parent_folder in os.listdir(folder):
-    # check if folder has file dataset.csv
-    if not os.path.exists(os.path.join(folder, parent_folder, 'dataset.csv')):
-        continue
-    print(f'Converting {parent_folder}')
-    df = pd.read_csv(os.path.join(folder, parent_folder, 'dataset.csv'))
-
-    plt.imsave(os.path.join(folder, parent_folder,
-               'dataset.png'), df.values, cmap='gray')

### 2024-06-12 MTF/gen_dataset.py

@@ -8,30 +8,86 @@ from models import classifiers
 import time
 import os
 
+possible_target_columns = [
+    "target",
+    "class",
+    "label",
+    "output",
+    "result",
+    "score",
+    "value",
+    "response",
+    "prediction",
+    "predict",
+    "outcome",
+    "y",
+    "yhat",
+    "disease",
+    "classification",
+    "heart",
+    "cancer",
+    "diagnosis",
+    "status",
+    "grade",
+    "rating",
+    "death",
+    "survival",
+    "risk",
+    "quality",
+    "failure",
+    "success",
+    "pass",
+    "fail",
+    "positive",
+    "negative",
+    "win",
+    "lose",
+    "kidney",
+    "diabetes",
+    "renal",
+    "chickenpox",
+    "influenza",
+    "congenital",
+    "infection",
+    "infect",
+    "infectious",
+    "virus",
+    "bacteria"
+]
+
 
 def gen_dataset(input, output):
     # Load dataset
     try:
         df = pd.read_csv(input)
 
-# check if dataset is greater than 10000
-        if df.shape[0] > 2000:
-            df = df.sample(2000)
-# extract last column as target
-        target = df.iloc[:, -1]
-        df.drop(df.columns[-1], axis=1, inplace=True)
+        columns = df.columns
+        if len(columns) <= 2:
+            print('Dataset has less than 2 columns')
+            return "Dataset has less than 2 columns"
 
-# convert target to binary
-# get the unique values
+        has_target_column = False
+        target_column = ""
+        for i, column in enumerate(columns):
+            print("Column: ", column)
+            if column.lower() in possible_target_columns and df[column].nunique() == 2:
+                target_column = column
+                has_target_column = True
+                break
+
+        if not has_target_column:
+            print('No target column found')
+            return "No target column found"
+
+        target = df[target_column]
         unique_values = target.unique()
 
-# check if the target is binary
-        if len(unique_values) > 2:
-            print('Target is not binary')
-            return "Target is not binary"
-        else:
-            # convert to binary
-            target = target.apply(lambda x: 1 if x == unique_values[0] else 0)
+        target = target.apply(lambda x: 1 if x == unique_values[0] else 0)
+
+        if df.shape[0] > 2000:
+            df = df.sample(2000)
+
+        df.drop(df.columns[-1], axis=1, inplace=True)
 
         numerical_features = []
         categorical_features = []

### 2024-06-12 MTF/get_attributes.py

@@ -20,11 +20,6 @@ def get_attributes(data_path):
     print("Output distribution: ", max(
         data.iloc[:, -1].value_counts(normalize=True)))
 
-    # Get the percenage of missing values in dataset
-    attributes['missing_values'] = data.isnull().sum().sum() / \
-        (data.shape[0] * data.shape[1])
-    print("Missing values: ", data.isnull().sum().sum())
-
     # get percentage of numerical and categorical columns
     numerical_features = 0
     binary_categorical = 0
@@ -84,22 +79,24 @@ def get_attributes(data_path):
     attributes['z_score_std'] = z_score_std
     print("Z-score std: ", z_score_std)
 
-    # correlation matrix of the dataset
-    corr_matrix = data.corr()
+    if data.shape[0] * data.shape[1] > 100000:
+        attributes['average_correlation'] = np.nan
+        attributes['correlation_std'] = np.nan
+    else:
+        # correlation matrix of the dataset
+        corr_matrix = data.corr()
 
-    # get the average correlation of the dataset (excluding the diagonal values)
-    corr_values = []
+        # get the average correlation of the dataset (excluding the diagonal values)
+        corr_values = []
 
-    for i in range(corr_matrix.shape[0]):
-        for j in range(corr_matrix.shape[1]):
-            if i != j:
-                corr_values.append(corr_matrix.iloc[i, j])
+        for i in range(corr_matrix.shape[0]):
+            for j in range(corr_matrix.shape[1]):
+                if i != j:
+                    corr_values.append(corr_matrix.iloc[i, j])
 
-    attributes['average_correlation'] = np.mean(corr_values)
-    print("Average correlation: ", np.mean(corr_values))
-    attributes['correlation_std'] = np.mean(np.std(corr_values))
-    print("Correlation std: ", np.mean(np.std(corr_values)))
-
-    print(attributes)
+        attributes['average_correlation'] = np.mean(corr_values)
+        print("Average correlation: ", np.mean(corr_values))
+        attributes['correlation_std'] = np.mean(np.std(corr_values))
+        print("Correlation std: ", np.mean(np.std(corr_values)))
 
     return attributes

### 2024-06-12 MTF/run_gen_dataset.py

@@ -27,7 +27,7 @@ output_folder = args.output
 # read the datasets folder
 datasets = os.listdir(datasets_folder)
 
-columns = ["num_rows", "num_cols", "output_distribution", "missing_values",
+columns = ["num_rows", "num_cols", "output_distribution",
            "numerical_columns", "binary_categorical",
            "categorical_average_count", "average_iqr", "average_q1",
            "average_q3", "iqr_std", "q1_std", "q3_std",
@@ -35,6 +35,7 @@ columns = ["num_rows", "num_cols", "output_distribution", "missing_values",
            "correlation_std", "dataset"]
 
 attributes_df = pd.DataFrame(columns=columns)
+
 
 for index, dataset in enumerate(datasets):
     if dataset.endswith('.csv'):

### 2024-06-12 MTF/test.py

@@ -10,56 +10,84 @@ datasets_folder = "../kaggle-dataset-download/DATASETS/"
 # read the datasets folder
 datasets = os.listdir(datasets_folder)
 
-columns = ["num_rows", "num_cols", "output_distribution", "missing_values",
-           "numerical_columns", "binary_categorical",
-           "categorical_average_count", "average_iqr", "average_q1",
-           "average_q3", "iqr_std", "q1_std", "q3_std",
-           "z_score_average", "z_score_std", "average_correlation",
-           "correlation_std", "dataset"]
-
-attributes_df = pd.DataFrame(columns=columns)
-
 count_target_by_name = 0
 count_target_by_last = 0
 combined = 0
+
+target_names = []
 
 for index, dataset in enumerate(datasets):
     if dataset.endswith('.csv'):
         # check if are column names
         try:
             df = pd.read_csv(datasets_folder + dataset)
-            columns = df.columns
 
-            possible_target_columns = ["target", "class", "label", "output", "y", "target_variable", "disease", "diag",
-                                       "diagnosis", "result", "status", "outcome", "response", "response_variable", "dependent_variable", "dependent"]
+        except Exception as e:
+            print("Error: ", e)
+            continue
+        if df.empty:
+            continue
 
-            # lowercase every column name
-            columns = [column.lower() for column in columns]
+        columns = df.columns
 
-            target_column_val = "None"
-            # check if there is a possible target column
-            for target_column in possible_target_columns:
-                if target_column in columns:
-                    if df[target_column].nunique() == 2:
-                        count_target_by_name += 1
-                        target_column_val = df[target_column].unique()
-                        break
+        possible_target_columns = [
+            "target",
+            "class",
+            "label",
+            "output",
+            "result",
+            "score",
+            "value",
+            "response",
+            "prediction",
+            "predict",
+            "outcome",
+            "y",
+            "yhat",
+            "disease",
+            "classification",
+            "heart",
+            "cancer",
+            "diagnosis",
+            "status",
+            "grade",
+            "rating",
+            "death",
+            "survival",
+            "risk",
+            "quality",
+            "failure",
+            "success",
+            "pass",
+            "fail",
+            "positive",
+            "negative",
+            "win",
+            "lose",
+            "kidney",
+            "diabetes",
+            "renal",
+            "chickenpox",
+            "influenza",
+            "congenital",
+            "infection",
+            "infect",
+            "infectious",
+            "virus",
[…]

### 2024-06-12 kaggle-dataset-download/koogle.py

@@ -10,8 +10,8 @@ api.authenticate()
 datasets = []
 start_page = 1
 page_count = 10
-topics = ['disease', 'covid', 'coronavirus',
-          'virus', 'infection', "cancer", 'heart', 'lungs']
+topics = ["kidney", "diabetes", "renal",
+          "chickenpox", "influenza", "congenital"]
 for i in range(start_page, start_page + page_count + 1):
     for j in range(len(topics)):
         dataset_page = api.dataset_list(

### 2024-06-12 MTF/gen_dataset.py
start implementing

@@ -1,162 +1,0 @@
-import pandas as pd
-import numpy as np
-import argparse as ap
-from sklearn.preprocessing import OneHotEncoder, MinMaxScaler
-from sklearn.compose import ColumnTransformer
-from sklearn.model_selection import train_test_split
-from models import classifiers
-import time
-import os
-
-possible_target_columns = [
-    "target",
-    "class",
-    "label",
-    "output",
-    "result",
-    "score",
-    "value",
-    "response",
-    "prediction",
-    "predict",
-    "outcome",
-    "y",
-    "yhat",
-    "disease",
-    "classification",
-    "heart",
-    "cancer",
-    "diagnosis",
-    "status",
-    "grade",
-    "rating",
-    "death",
-    "survival",
-    "risk",
-    "quality",
-    "failure",
-    "success",
-    "pass",
-    "fail",
-    "positive",
-    "negative",
-    "win",
-    "lose",
-    "kidney",
-    "diabetes",
-    "renal",
-    "chickenpox",
-    "influenza",
-    "congenital",
-    "infection",
-    "infect",
-    "infectious",
-    "virus",
-    "bacteria"
-]
-
-
-def gen_dataset(input, output):
-    # Load dataset
-    try:
-        df = pd.read_csv(input)
-
-        columns = df.columns
-        if len(columns) <= 2:
-            print('Dataset has less than 2 columns')
-            return "Dataset has less than 2 columns"
-
-        has_target_column = False
-        target_column = ""
-        for i, column in enumerate(columns):
-            print("Column: ", column)
-            if column.lower() in possible_target_columns and df[column].nunique() == 2:
-                target_column = column
-                has_target_column = True
-                break
-
-        if not has_target_column:
-            print('No target column found')
-            return "No target column found"
-
-        target = df[target_column]
-        unique_values = target.unique()
-
-        target = target.apply(lambda x: 1 if x == unique_values[0] else 0)
-
-        if df.shape[0] > 2000:
-            df = df.sample(2000)
-
-        df.drop(df.columns[-1], axis=1, inplace=True)
-
-        numerical_features = []
-        categorical_features = []
-
-# Loop through all columns
-        for col in df.columns:
-            # Check if column is numeric
-            # check the number of unique values
-            if df[col].nunique() < 15 or df[col].dtype == 'object':
-                categorical_features.append(col)
-            else:
-                numerical_features.append(col)
-
[…]

### 2024-06-12 MTF/get_attributes.py

@@ -1,102 +1,0 @@
-import numpy as np
-import pandas as pd
-import os
-
-
-def get_attributes(data_path):
-    data = pd.read_csv(data_path)
-    # Get the attributes of the data
-    attributes = {}
-
-    # Get the number of rows and columns
-    attributes['num_rows'] = data.shape[0]
-    print("Number of rows: ", data.shape[0])
-    attributes['num_cols'] = data.shape[1]
-    print("Number of columns: ", data.shape[1])
-
-    # get the output distribution of 1 percentage
-    attributes['output_distribution'] = max(data.iloc[:, -
-                                                      1].value_counts(normalize=True))
-    print("Output distribution: ", max(
-        data.iloc[:, -1].value_counts(normalize=True)))
-
-    # get percentage of numerical and categorical columns
-    numerical_features = 0
-    binary_categorical = 0
-    categorical_average_count = 0
-    categorical_count = 0
-    iqr_values = []
-    q1_values = []
-    q3_values = []
-    for col in data.columns:
-        if data[col].nunique() > 15:
-            numerical_features += 1
-
-            # get the interquartile range
-            q1 = data[col].quantile(0.25)
-            q3 = data[col].quantile(0.75)
-            iqr = q3 - q1
-
-            iqr_values.append(iqr)
-            q1_values.append(q1)
-            q3_values.append(q3)
-        else:
-            categorical_count += 1
-            # categorical
-            # check if binary or not
-            if data[col].nunique() == 2:
-                binary_categorical += 1
-
-            categorical_average_count += data[col].nunique()
-
-    attributes['numerical_columns'] = numerical_features/data.shape[1]
-    attributes['binary_categorical'] = binary_categorical/categorical_count
-    attributes['categorical_average_count'] = categorical_average_count / \
-        categorical_count
-    attributes['average_iqr'] = np.mean(iqr_values)
-    attributes['average_q1'] = np.mean(q1_values)
-    attributes['average_q3'] = np.mean(q3_values)
-    attributes['iqr_std'] = np.mean(np.std(iqr_values))
-    attributes['q1_std'] = np.mean(np.std(q1_values))
-    attributes['q3_std'] = np.mean(np.std(q3_values))
-    print("Numerical columns: ", numerical_features/data.shape[1])
-    print("Binary categorical: ", binary_categorical/categorical_count)
-    print("Categorical average count: ",
[…]

### 2024-06-12 MTF/models.py

@@ -1,70 +1,0 @@
-from sklearn.svm import SVC
-from sklearn.linear_model import SGDClassifier
-from sklearn.linear_model import RidgeClassifierCV
-from sklearn.linear_model import RidgeClassifier
-from sklearn.ensemble import RandomForestClassifier
-from sklearn.neighbors import RadiusNeighborsClassifier
-from sklearn.discriminant_analysis import QuadraticDiscriminantAnalysis
-from sklearn.linear_model import Perceptron
-from sklearn.linear_model import PassiveAggressiveClassifier
-from sklearn.neighbors import NearestCentroid
-from sklearn.neural_network import MLPClassifier
-from sklearn.linear_model import LogisticRegressionCV
-from sklearn.linear_model import LogisticRegression
-from sklearn.svm import LinearSVC
-from sklearn.discriminant_analysis import LinearDiscriminantAnalysis
-from sklearn.semi_supervised import LabelSpreading
-from sklearn.semi_supervised import LabelPropagation
-from sklearn.neighbors import KNeighborsClassifier
-from sklearn.ensemble import HistGradientBoostingClassifier
-from sklearn.ensemble import GradientBoostingClassifier
-from sklearn.naive_bayes import GaussianNB
-from sklearn.ensemble import ExtraTreesClassifier
-from sklearn.tree import ExtraTreeClassifier
-from sklearn.dummy import DummyClassifier
-from sklearn.tree import DecisionTreeClassifier
-from sklearn.naive_bayes import BernoulliNB
-from sklearn.ensemble import AdaBoostClassifier
-from xgboost import XGBClassifier
-from lightgbm import LGBMClassifier
-from catboost import CatBoostClassifier
-from sklearn.naive_bayes import MultinomialNB
-from sklearn.naive_bayes import ComplementNB
-from sklearn.naive_bayes import CategoricalNB
-import numpy as np
-
-classifiers = np.array([
-    SVC(kernel='rbf', C=1.0, verbose=False),
-    SGDClassifier(loss='hinge', max_iter=1000, tol=1e-3),
-    RidgeClassifierCV(alphas=[0.1, 1.0, 10.0]),
-    RidgeClassifier(alpha=1.0),
-    Perceptron(max_iter=1000, tol=1e-3),
-    PassiveAggressiveClassifier(max_iter=1000, tol=1e-3),
[…]

### 2024-06-12 MTF/run_gen_dataset.py

@@ -1,58 +1,0 @@
-import os
-import argparse as ap
-import subprocess
-from gen_dataset import gen_dataset
-from get_attributes import get_attributes
-import pandas as pd
-
-parser = ap.ArgumentParser(description='Generate datasets')
-
-parser.add_argument('-f',
-                    '--folder',
-                    type=str,
-                    help='Folder containing datasets',
-                    required=True)
-
-parser.add_argument('-o',
-                    '--output',
-                    type=str,
-                    help='Output folder',
-                    required=True)
-
-args = parser.parse_args()
-
-datasets_folder = args.folder
-output_folder = args.output
-
-# read the datasets folder
-datasets = os.listdir(datasets_folder)
-
-columns = ["num_rows", "num_cols", "output_distribution",
-           "numerical_columns", "binary_categorical",
-           "categorical_average_count", "average_iqr", "average_q1",
-           "average_q3", "iqr_std", "q1_std", "q3_std",
-           "z_score_average", "z_score_std", "average_correlation",
-           "correlation_std", "dataset"]
-
-attributes_df = pd.DataFrame(columns=columns)
-
-
-for index, dataset in enumerate(datasets):
-    if dataset.endswith('.csv'):
-        print(f"[{index}] Generating {dataset}")
-        # print subprocess output
-        error_ = gen_dataset(os.path.join(datasets_folder, dataset),
-                             os.path.join(output_folder, dataset.split('.')[0]))
-
-        if error_:
-            print(f"Error: {error_}")
-            continue
-
-        attributes = get_attributes(os.path.join(
-            output_folder, dataset.split('.')[0], 'dataset.csv'))
-
-        attributes['dataset'] = dataset
-
-        attributes_df = attributes_df._append(attributes, ignore_index=True)
-
-attributes_df.to_csv('attributes.csv', index=False)

### 2024-06-12 MTF/test.py

@@ -1,93 +1,0 @@
-import os
-import argparse as ap
-import subprocess
-from gen_dataset import gen_dataset
-from get_attributes import get_attributes
-import pandas as pd
-
-datasets_folder = "../kaggle-dataset-download/DATASETS/"
-
-# read the datasets folder
-datasets = os.listdir(datasets_folder)
-
-count_target_by_name = 0
-count_target_by_last = 0
-combined = 0
-
-target_names = []
-
-for index, dataset in enumerate(datasets):
-    if dataset.endswith('.csv'):
-        # check if are column names
-        try:
-            df = pd.read_csv(datasets_folder + dataset)
-
-        except Exception as e:
-            print("Error: ", e)
-            continue
-        if df.empty:
-            continue
-
-        columns = df.columns
-
-        possible_target_columns = [
-            "target",
-            "class",
-            "label",
-            "output",
-            "result",
-            "score",
-            "value",
-            "response",
-            "prediction",
-            "predict",
-            "outcome",
-            "y",
-            "yhat",
-            "disease",
-            "classification",
-            "heart",
-            "cancer",
-            "diagnosis",
-            "status",
-            "grade",
-            "rating",
-            "death",
-            "survival",
-            "risk",
-            "quality",
-            "failure",
-            "success",
-            "pass",
-            "fail",
-            "positive",
-            "negative",
-            "win",
-            "lose",
-            "kidney",
-            "diabetes",
-            "renal",
-            "chickenpox",
-            "influenza",
-            "congenital",
-            "infection",
-            "infect",
-            "infectious",
-            "virus",
-            "bacteria"
-        ]
-
-        # lowercase every column name
-        has_target_column = False
-        for i, column in enumerate(columns):
-            print("Column: ", column)
-            if column.lower() in possible_target_columns and df[column].nunique() == 2:
-                has_target_column = True
-                target_names.append(column)
-                break
-
-        if has_target_column:
-            count_target_by_name += 1
-
-print("Count target by name: ", count_target_by_name)
-print("Target names: ", target_names)

### 2024-06-12 SMEML/SMEML.py

@@ -1,0 +1,162 @@
+import pickle as pkl
+import numpy as np
+from sklearn.model_selection import train_test_split
+from xgboost import XGBRegressor
+from sklearn.multioutput import MultiOutputRegressor
+import os
+
+classifier_names = [
+    'SVC',
+    'SGDClassifier',
+    'RidgeClassifierCV',
+    'RidgeClassifier',
+    'Perceptron',
+    'PassiveAggressiveClassifier',
+    'LogisticRegressionCV',
+    'LogisticRegression',
+    'LinearSVC',
+    'RandomForestClassifier',
+    'HistGradientBoostingClassifier',
+    'GradientBoostingClassifier',
+    'ExtraTreesClassifier',
+    'AdaBoostClassifier',
+    'XGBClassifier',
+    'LGBMClassifier',
+    'CatBoostClassifier',
+    'RadiusNeighborsClassifier',
+    'KNeighborsClassifier',
+    'NearestCentroid',
+    'QuadraticDiscriminantAnalysis',
+    'LinearDiscriminantAnalysis',
+    'GaussianNB',
+    'BernoulliNB',
+    'MLPClassifier',
+    'ExtraTreeClassifier',
+    'DecisionTreeClassifier',
+    'LabelSpreading',
+    'LabelPropagation',
+    'DummyClassifier'
+]
+
+
+class SMEML:
+    def __init__(self):
+        self.X = None
+        self.y = None
+
+    def train(self, X, y):
+        self.X = X
+        self.y = y
+        attributes = self.get_dataset_attributes()
+
+        # train the model
+        smeml_model = pkl.load(
+            open(os.path.join(os.path.dirname(os.path.abspath(__file__)), 'model.pkl'), 'rb'))
+
+        input = list(attributes.values())
+        input = np.array(input).reshape(1, -1)
+
+        results = smeml_model.predict(input)
+
+        top_3 = np.argsort(results[0])[-3:]
+
+        print("Top 3 classifiers: ", [classifier_names[i] for i in top_3])
+
+        return results, attributes
+
+    def get_dataset_attributes(self):
+        attributes = {}
+
+        attributes['num_rows'] = self.X.shape[0]
+        print("Number of rows: ", self.X.shape[0])
+        attributes['num_cols'] = self.X.shape[1]
+        print("Number of columns: ", self.X.shape[1])
+
+        # get the output distribution of 1 percentage
+        attributes['output_distribution'] = max(self.X.iloc[:, -
[…]

### 2024-06-12 SMEML/gen_dataset.py

@@ -1,0 +1,162 @@
+import pandas as pd
+import numpy as np
+import argparse as ap
+from sklearn.preprocessing import OneHotEncoder, MinMaxScaler
+from sklearn.compose import ColumnTransformer
+from sklearn.model_selection import train_test_split
+from models import classifiers
+import time
+import os
+
+possible_target_columns = [
+    "target",
+    "class",
+    "label",
+    "output",
+    "result",
+    "score",
+    "value",
+    "response",
+    "prediction",
+    "predict",
+    "outcome",
+    "y",
+    "yhat",
+    "disease",
+    "classification",
+    "heart",
+    "cancer",
+    "diagnosis",
+    "status",
+    "grade",
+    "rating",
+    "death",
+    "survival",
+    "risk",
+    "quality",
+    "failure",
+    "success",
+    "pass",
+    "fail",
+    "positive",
+    "negative",
+    "win",
+    "lose",
+    "kidney",
+    "diabetes",
+    "renal",
+    "chickenpox",
+    "influenza",
+    "congenital",
+    "infection",
+    "infect",
+    "infectious",
+    "virus",
+    "bacteria"
+]
+
+
+def gen_dataset(input, output):
+    # Load dataset
+    try:
+        df = pd.read_csv(input)
+
+        columns = df.columns
+        if len(columns) <= 2:
+            print('Dataset has less than 2 columns')
+            return "Dataset has less than 2 columns"
+
+        has_target_column = False
+        target_column = ""
+        for i, column in enumerate(columns):
+            print("Column: ", column)
+            if column.lower() in possible_target_columns and df[column].nunique() == 2:
+                target_column = column
+                has_target_column = True
+                break
+
+        if not has_target_column:
+            print('No target column found')
+            return "No target column found"
+
+        target = df[target_column]
+        unique_values = target.unique()
+
+        target = target.apply(lambda x: 1 if x == unique_values[0] else 0)
+
+        if df.shape[0] > 2000:
+            df = df.sample(2000)
+
+        df.drop(df.columns[-1], axis=1, inplace=True)
+
+        numerical_features = []
+        categorical_features = []
+
+# Loop through all columns
+        for col in df.columns:
+            # Check if column is numeric
+            # check the number of unique values
+            if df[col].nunique() < 15 or df[col].dtype == 'object':
+                categorical_features.append(col)
+            else:
+                numerical_features.append(col)
+
[…]

### 2024-06-12 SMEML/get_attributes.py

@@ -1,0 +1,102 @@
+import numpy as np
+import pandas as pd
+import os
+
+
+def get_attributes(data_path):
+    data = pd.read_csv(data_path)
+    # Get the attributes of the data
+    attributes = {}
+
+    # Get the number of rows and columns
+    attributes['num_rows'] = data.shape[0]
+    print("Number of rows: ", data.shape[0])
+    attributes['num_cols'] = data.shape[1]
+    print("Number of columns: ", data.shape[1])
+
+    # get the output distribution of 1 percentage
+    attributes['output_distribution'] = max(data.iloc[:, -
+                                                      1].value_counts(normalize=True))
+    print("Output distribution: ", max(
+        data.iloc[:, -1].value_counts(normalize=True)))
+
+    # get percentage of numerical and categorical columns
+    numerical_features = 0
+    binary_categorical = 0
+    categorical_average_count = 0
+    categorical_count = 0
+    iqr_values = []
+    q1_values = []
+    q3_values = []
+    for col in data.columns:
+        if data[col].nunique() > 15:
+            numerical_features += 1
+
+            # get the interquartile range
+            q1 = data[col].quantile(0.25)
+            q3 = data[col].quantile(0.75)
+            iqr = q3 - q1
+
+            iqr_values.append(iqr)
+            q1_values.append(q1)
+            q3_values.append(q3)
+        else:
+            categorical_count += 1
+            # categorical
+            # check if binary or not
+            if data[col].nunique() == 2:
+                binary_categorical += 1
+
+            categorical_average_count += data[col].nunique()
+
+    attributes['numerical_columns'] = numerical_features/data.shape[1]
+    attributes['binary_categorical'] = binary_categorical/categorical_count
+    attributes['categorical_average_count'] = categorical_average_count / \
+        categorical_count
+    attributes['average_iqr'] = np.mean(iqr_values)
+    attributes['average_q1'] = np.mean(q1_values)
+    attributes['average_q3'] = np.mean(q3_values)
+    attributes['iqr_std'] = np.mean(np.std(iqr_values))
+    attributes['q1_std'] = np.mean(np.std(q1_values))
+    attributes['q3_std'] = np.mean(np.std(q3_values))
+    print("Numerical columns: ", numerical_features/data.shape[1])
+    print("Binary categorical: ", binary_categorical/categorical_count)
+    print("Categorical average count: ",
[…]

### 2024-06-12 SMEML/models.py

@@ -1,0 +1,70 @@
+from sklearn.svm import SVC
+from sklearn.linear_model import SGDClassifier
+from sklearn.linear_model import RidgeClassifierCV
+from sklearn.linear_model import RidgeClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.neighbors import RadiusNeighborsClassifier
+from sklearn.discriminant_analysis import QuadraticDiscriminantAnalysis
+from sklearn.linear_model import Perceptron
+from sklearn.linear_model import PassiveAggressiveClassifier
+from sklearn.neighbors import NearestCentroid
+from sklearn.neural_network import MLPClassifier
+from sklearn.linear_model import LogisticRegressionCV
+from sklearn.linear_model import LogisticRegression
+from sklearn.svm import LinearSVC
+from sklearn.discriminant_analysis import LinearDiscriminantAnalysis
+from sklearn.semi_supervised import LabelSpreading
+from sklearn.semi_supervised import LabelPropagation
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.ensemble import HistGradientBoostingClassifier
+from sklearn.ensemble import GradientBoostingClassifier
+from sklearn.naive_bayes import GaussianNB
+from sklearn.ensemble import ExtraTreesClassifier
+from sklearn.tree import ExtraTreeClassifier
+from sklearn.dummy import DummyClassifier
+from sklearn.tree import DecisionTreeClassifier
+from sklearn.naive_bayes import BernoulliNB
+from sklearn.ensemble import AdaBoostClassifier
+from xgboost import XGBClassifier
+from lightgbm import LGBMClassifier
+from catboost import CatBoostClassifier
+from sklearn.naive_bayes import MultinomialNB
+from sklearn.naive_bayes import ComplementNB
+from sklearn.naive_bayes import CategoricalNB
+import numpy as np
+
+classifiers = np.array([
+    SVC(kernel='rbf', C=1.0, verbose=False),
+    SGDClassifier(loss='hinge', max_iter=1000, tol=1e-3),
+    RidgeClassifierCV(alphas=[0.1, 1.0, 10.0]),
+    RidgeClassifier(alpha=1.0),
+    Perceptron(max_iter=1000, tol=1e-3),
+    PassiveAggressiveClassifier(max_iter=1000, tol=1e-3),
[…]

### 2024-06-12 SMEML/run_gen_dataset.py

@@ -1,0 +1,58 @@
+import os
+import argparse as ap
+import subprocess
+from gen_dataset import gen_dataset
+from get_attributes import get_attributes
+import pandas as pd
+
+parser = ap.ArgumentParser(description='Generate datasets')
+
+parser.add_argument('-f',
+                    '--folder',
+                    type=str,
+                    help='Folder containing datasets',
+                    required=True)
+
+parser.add_argument('-o',
+                    '--output',
+                    type=str,
+                    help='Output folder',
+                    required=True)
+
+args = parser.parse_args()
+
+datasets_folder = args.folder
+output_folder = args.output
+
+# read the datasets folder
+datasets = os.listdir(datasets_folder)
+
+columns = ["num_rows", "num_cols", "output_distribution",
+           "numerical_columns", "binary_categorical",
+           "categorical_average_count", "average_iqr", "average_q1",
+           "average_q3", "iqr_std", "q1_std", "q3_std",
+           "z_score_average", "z_score_std", "average_correlation",
+           "correlation_std", "dataset"]
+
+attributes_df = pd.DataFrame(columns=columns)
+
+
+for index, dataset in enumerate(datasets):
+    if dataset.endswith('.csv'):
+        print(f"[{index}] Generating {dataset}")
+        # print subprocess output
+        error_ = gen_dataset(os.path.join(datasets_folder, dataset),
+                             os.path.join(output_folder, dataset.split('.')[0]))
+
+        if error_:
+            print(f"Error: {error_}")
+            continue
+
+        attributes = get_attributes(os.path.join(
+            output_folder, dataset.split('.')[0], 'dataset.csv'))
+
+        attributes['dataset'] = dataset
+
+        attributes_df = attributes_df._append(attributes, ignore_index=True)
+
+attributes_df.to_csv('attributes.csv', index=False)

### 2024-06-12 example.py

@@ -1,0 +1,17 @@
+from SMEML.SMEML import SMEML
+from sklearn.model_selection import train_test_split
+import pandas as pd
+
+# load the dataset
+df = pd.read_csv('./benchmarks/H2O/heart.csv')
+
+X = df.drop('target', axis=1)
+y = df['target']
+
+# create an instance of the SMEML class
+# X and y are the features and target variable
+# respectively
+smeml = SMEML()
+
+# train the model
+results, attributes = smeml.train(X, y)

### 2024-06-12 paper.tex
Update paper.tex

--- 2024-06-11 paper.tex
@@
 
+\documentclass{article}
+\usepackage{geometry}
+\usepackage{longtable}
+\usepackage{graphicx}
+
+\geometry{a4paper, margin=1in}
+
+\begin{document}
+
+\begin{longtable}{|l|l|l|l|l|}
+\hline
+\textbf{Factor} & \textbf{H2O} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
+\hline
+\endfirsthead
+
+\multicolumn{5}{c}%
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
+\hline
+\endhead
+
+\hline \multicolumn{5}{|r|}{\textit{Continued on next page}} \\
+\hline
+\endfoot
+
+\hline
+\endlastfoot
+
+\textbf{Ease of Use} & Easy-to-use GUI and API & Python library, requires coding experience & Very user-friendly web interface, detailed API & Simple API & User-friendly API with minimal coding & Python library with fairly intuitive API\\
+\hline
+\textbf{Supported Algorithms} & Linear, Tree, DNN, Clustering, etc.
+& Genetic Programming & Linear, Tree, LightGBM, CatBoost, Clustering, etc.
+(no DNN) & Linear, Tree, Clustering - More limited and lightweight & Linear, LightGBM, Catboost, etc.
+& Linear, tree, SVM, etc.
+\\
+\hline
+\textbf{Feature Engineering} & Basic & Basic & Advanced - includes feature interactions & Limited & Advanced (automatic) & Basic \\
+\hline
+\textbf{Time Management} & Time Constraints are Settable & Generations and population size & Time constraints are Settable & Optimized for quick results & Settable time constraints & Settable time constraints\\
+\textbf{Ensemble Methods} & Yes (stacking + blending) & Yes (stacking) & Yes (stacking + blending) & No & Yes (stacking) & Yes (stacking) \\
+\hline
+\textbf{Hyperparameter Tuning} & Automated & Genetic algorithm & Automated and customizable & Automated and efficient tuning & Automated & Automated \\
+\hline
+\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. & Basic (feature importance) \\
+\hline
+\hline
+\textbf{Scalability} & Good (distributed computing) & Limited & Good & Good (resource-efficient) & Good (distributing computing) & Moderate \\
+\hline
+\textbf{Customization} & High & Moderate & High & Low-Moderate & Moderate & Moderate \\
+\hline
+
+\end{longtable}
+
+\end{document}
+
 \section{Methodology}

### 2024-06-13 SMEML/SMEML.py
benchmark datasets folder and updates to SMEML

@@ -1,9 +1,13 @@
 import pickle as pkl
 import numpy as np
 from sklearn.model_selection import train_test_split
-from xgboost import XGBRegressor
+from xgboost import XGBRegressor, XGBClassifier
 from sklearn.multioutput import MultiOutputRegressor
+from sklearn.ensemble import StackingClassifier
+from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
+from sklearn.compose import ColumnTransformer
 import os
+from SMEML.models import classifiers
 
 classifier_names = [
     'SVC',
@@ -47,6 +51,10 @@ class SMEML:
     def train(self, X, y):
         self.X = X
         self.y = y
+
+        # fill nan values
+        self.preprocess()
+
         attributes = self.get_dataset_attributes()
 
         # train the model
@@ -58,9 +66,33 @@ class SMEML:
 
         results = smeml_model.predict(input)
 
-        top_3 = np.argsort(results[0])[-3:]
+        top_3 = np.argsort(results[0])[-5:]
 
-        print("Top 3 classifiers: ", [classifier_names[i] for i in top_3])
+        X_train, X_test, y_train, y_test = train_test_split(
+            self.X, self.y, test_size=0.2, random_state=42)
+
+        models = []
+        # get the top 3 classifiers
+        for i in top_3:
+            model = classifiers[i]
+
+            # train the classifier
+            model.fit(X_train, y_train)
+
+            # get the accuracy of the classifier
+            accuracy = model.score(X_test, y_test)
+            print(model, accuracy)
+
+            models.append(model)
+
+        final_stacked_model = StackingClassifier(
+            estimators=[(classifier_names[i], model) for i, model in zip(top_3, models)], final_estimator=XGBClassifier(verbosity=0))
+
+        final_stacked_model.fit(X_train, y_train)
+
+        final_accuracy = final_stacked_model.score(X_test, y_test)
+
+        print("Final stacked model accuracy: ", final_accuracy)
 
         return results, attributes
 
@@ -160,3 +192,38 @@ class SMEML:
             print("Correlation std: ", np.mean(np.std(corr_values)))
 
         return attributes
+
+    def preprocess(self):
+        columns = self.X.columns
+
+        categorical_features = self.X.select_dtypes(include=['object']).columns
+        numerical_features = self.X.select_dtypes(
+            include=['int64', 'float64']).columns
+
+        # fill missing values
+        for col in columns:
+            if col in categorical_features:
[…]

### 2024-06-13 example.py

@@ -3,15 +3,17 @@ from sklearn.model_selection import train_test_split
 import pandas as pd
 
 # load the dataset
-df = pd.read_csv('./benchmarks/H2O/heart.csv')
+df = pd.read_csv('./datasets/heart.csv')
 
 X = df.drop('target', axis=1)
 y = df['target']
+
+# label encoding
+# y = y.map({'ckd': 1, 'notckd': 0})
 
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
 smeml = SMEML()
-
 # train the model
 results, attributes = smeml.train(X, y)

### 2024-06-13 SMEML/SMEML.py
use best model

@@ -3,7 +3,7 @@ import numpy as np
 from sklearn.model_selection import train_test_split
 from xgboost import XGBRegressor, XGBClassifier
 from sklearn.multioutput import MultiOutputRegressor
-from sklearn.ensemble import StackingClassifier
+from sklearn.ensemble import VotingClassifier
 from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
 from sklearn.compose import ColumnTransformer
 import os
@@ -66,14 +66,14 @@ class SMEML:
 
         results = smeml_model.predict(input)
 
-        top_3 = np.argsort(results[0])[-5:]
+        top = np.argsort(results[0])[-10:]
 
         X_train, X_test, y_train, y_test = train_test_split(
             self.X, self.y, test_size=0.2, random_state=42)
 
         models = []
         # get the top 3 classifiers
-        for i in top_3:
+        for i in top:
             model = classifiers[i]
 
             # train the classifier
@@ -83,16 +83,12 @@ class SMEML:
             accuracy = model.score(X_test, y_test)
             print(model, accuracy)
 
-            models.append(model)
+            models.append((model, accuracy))
 
-        final_stacked_model = StackingClassifier(
-            estimators=[(classifier_names[i], model) for i, model in zip(top_3, models)], final_estimator=XGBClassifier(verbosity=0))
+        # get best model
+        best_model = max(models, key=lambda x: x[1])
 
-        final_stacked_model.fit(X_train, y_train)
-
-        final_accuracy = final_stacked_model.score(X_test, y_test)
-
-        print("Final stacked model accuracy: ", final_accuracy)
+        print("Best model: ", best_model[0], best_model[1])
 
         return results, attributes
 

### 2024-06-13 example.py

@@ -3,7 +3,7 @@ from sklearn.model_selection import train_test_split
 import pandas as pd
 
 # load the dataset
-df = pd.read_csv('./datasets/heart.csv')
+df = pd.read_csv('./benchmark_datasets/heart.csv')
 
 X = df.drop('target', axis=1)
 y = df['target']

### 2024-06-13 SMEML/SMEML.py
multithreading and reports

@@ -1,13 +1,33 @@
 import pickle as pkl
 import numpy as np
-from sklearn.model_selection import train_test_split
+from sklearn.model_selection import cross_val_score, train_test_split
 from xgboost import XGBRegressor, XGBClassifier
 from sklearn.multioutput import MultiOutputRegressor
 from sklearn.ensemble import VotingClassifier
 from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
 from sklearn.compose import ColumnTransformer
 import os
+import threading
 from SMEML.models import classifiers
+import logging
+
+logging.captureWarnings(capture=True)
+
+# Get logger for warnings
+logger = logging.getLogger("py.warnings")
+
+# StreamHandler outputs on sys.stderr by default
+handler = logging.StreamHandler()
+logger.addHandler(handler)
+
+warnings_to_ignore = [
+    "FutureWarning",
+    "InconsistentVersionWarning"
+]
+
+# Set rule to ignore warnings
+logger.addFilter(
+    lambda record: record.getMessage() in warnings_to_ignore)
 
 classifier_names = [
     'SVC',
@@ -68,29 +88,42 @@ class SMEML:
 
         top = np.argsort(results[0])[-10:]
 
-        X_train, X_test, y_train, y_test = train_test_split(
-            self.X, self.y, test_size=0.2, random_state=42)
-
-        models = []
+        model_threads = []
+        self.models = []
         # get the top 3 classifiers
         for i in top:
-            model = classifiers[i]
+            thread = threading.Thread(
+                target=self.train_thread, args=(classifiers[i],))
+            model_threads.append(thread)
+            thread.start()
 
-            # train the classifier
-            model.fit(X_train, y_train)
-
-            # get the accuracy of the classifier
-            accuracy = model.score(X_test, y_test)
-            print(model, accuracy)
-
-            models.append((model, accuracy))
-
+        # wait for all threads to finish
+        for thread in model_threads:
+            thread.join()
         # get best model
-        best_model = max(models, key=lambda x: x[1])
+        best_model = max(self.models, key=lambda x: (x[2], x[1], x[3]))
+        self.best_model = best_model
 
-        print("Best model: ", best_model[0], best_model[1])
+        print("Best model: ", best_model[0], "Average accuracy: ", best_model[1],
+              "Best accuracy: ", best_model[2], "Standard Deviation: ", best_model[3], "Scores: ", best_model[4])
 
-        return results, attributes
+        self.generate_report()
+
+        self.save_final_model()
[…]

### 2024-06-13 example.py

@@ -16,4 +16,4 @@ y = df['target']
 # respectively
 smeml = SMEML()
 # train the model
-results, attributes = smeml.train(X, y)
+smeml.train(X, y)

### 2024-06-14 SMEML/SMEML.py
multithreading

@@ -6,10 +6,15 @@ from sklearn.multioutput import MultiOutputRegressor
 from sklearn.ensemble import VotingClassifier
 from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
 from sklearn.compose import ColumnTransformer
+from skopt import BayesSearchCV
 import os
-import threading
-from SMEML.models import classifiers
+import multiprocessing
+from SMEML.models import classifiers, param_grids
+from multiprocessing import freeze_support
+from functools import partial
 import logging
+
+np.int = int
 
 logging.captureWarnings(capture=True)
 
@@ -72,6 +77,9 @@ class SMEML:
         self.X = X
         self.y = y
 
+        self.X_train, self.X_test, self.y_train, self.y_test = train_test_split(
+            self.X, self.y, test_size=0.2, random_state=42)
+
         # fill nan values
         self.preprocess()
 
@@ -90,40 +98,48 @@ class SMEML:
 
         model_threads = []
         self.models = []
-        # get the top 3 classifiers
+        manager = multiprocessing.Manager()
+        return_dict = manager.dict()
         for i in top:
-            thread = threading.Thread(
-                target=self.train_thread, args=(classifiers[i],))
+            thread = multiprocessing.Process(
+                target=self.train_thread, args=(classifiers[i], return_dict,))
             model_threads.append(thread)
+
+        for thread in model_threads:
             thread.start()
 
         # wait for all threads to finish
         for thread in model_threads:
             thread.join()
-        # get best model
-        best_model = max(self.models, key=lambda x: (x[2], x[1], x[3]))
-        self.best_model = best_model
 
-        print("Best model: ", best_model[0], "Average accuracy: ", best_model[1],
-              "Best accuracy: ", best_model[2], "Standard Deviation: ", best_model[3], "Scores: ", best_model[4])
+        for key, value in return_dict.items():
+            self.models.append((key, value))
+
+        # get best model
+        self.best_model = max(self.models, key=lambda x: (x[1]))
+
+        print("Best model: ", self.best_model[0],
+              " with accuracy: ", self.best_model[1])
 
         self.generate_report()
-
         self.save_final_model()
 
-    def train_thread(self, model):
-        # train the classifier
-        scores = cross_val_score(model, self.X, self.y, cv=5)
+    def train_thread(self, model, return_dict):
+        print("Training model: ", model)
+        optimizer = BayesSearchCV(
[…]

### 2024-06-14 SMEML/models.py

@@ -64,7 +64,170 @@ classifiers = np.array([
     LabelSpreading(kernel='rbf'),
     LabelPropagation(kernel='rbf'),
     DummyClassifier(strategy='most_frequent'),
-    # MultinomialNB(verbose=False),
-    # ComplementNB(verbose=False),
-    # CategoricalNB(verbose=False)
 ], dtype=object)
+
+
+param_grids = {
+    'SVC': {
+        'C': [0.1, 1, 10, 100],
+        'gamma': ['scale', 'auto'],
+    },
+    'SGDClassifier': {
+        'loss': ['hinge', 'log', 'modified_huber', 'squared_hinge', 'perceptron'],
+        'penalty': ['l2', 'l1', 'elasticnet'],
+        'alpha': [0.0001, 0.001, 0.01, 0.1],
+        'max_iter': [1000, 2000],
+        'tol': [1e-3, 1e-4],
+    },
+    'RidgeClassifierCV': {
+        'alphas': [[0.01, 0.1, 1.0, 10.0, 100.0]],
+        'fit_intercept': [True, False],
+        'normalize': [True, False],
+    },
+    'RidgeClassifier': {
+        'alpha': [0.01, 0.1, 1.0, 10.0],
+        'fit_intercept': [True, False],
+        'normalize': [True, False],
+    },
+    'Perceptron': {
+        'penalty': [None, 'l2', 'l1', 'elasticnet'],
+        'alpha': [0.0001, 0.001, 0.01, 0.1],
+        'max_iter': [1000, 2000],
+        'tol': [1e-3, 1e-4],
+    },
+    'PassiveAggressiveClassifier': {
+        'C': [0.01, 0.1, 1, 10],
+        'max_iter': [1000, 2000],
+        'tol': [1e-3, 1e-4],
+    },
+    'LogisticRegressionCV': {
+        'cv': [3, 5, 10],
+        'penalty': ['l2'],
+        'solver': ['lbfgs', 'liblinear', 'sag', 'saga'],
+        'max_iter': [1000, 2000],
+    },
+    'LogisticRegression': {
+        'C': [0.01, 0.1, 1.0, 10.0, 100.0],
+        'penalty': ['l2'],
+        'solver': ['lbfgs', 'liblinear', 'sag', 'saga'],
+        'max_iter': [1000, 2000],
+    },
+    'LinearSVC': {
+        'C': [0.01, 0.1, 1.0, 10.0, 100.0],
+        'penalty': ['l2'],
[…]

### 2024-06-14 example.py

@@ -1,12 +1,15 @@
 from SMEML.SMEML import SMEML
 from sklearn.model_selection import train_test_split
 import pandas as pd
+import time
 
-# load the dataset
-df = pd.read_csv('./benchmark_datasets/heart.csv')
+if __name__ == "__main__":
+    time_start = time.time()
+    # load the dataset
+    df = pd.read_csv('./benchmark_datasets/heart.csv')
 
-X = df.drop('target', axis=1)
-y = df['target']
+    X = df.drop('target', axis=1)
+    y = df['target']
 
 # label encoding
 # y = y.map({'ckd': 1, 'notckd': 0})
@@ -14,6 +17,8 @@ y = df['target']
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-smeml = SMEML()
+    smeml = SMEML()
 # train the model
-smeml.train(X, y)
+    smeml.train(X, y)
+    time_end = time.time()
+    print('Time taken to train the model: ', time_end - time_start)

### 2024-06-15 paper.tex
Update paper.tex

@@
 
-\begin{longtable}{|l|l|l|l|l|}
+\begin{longtable}{|l|l|l|l|l|l|l|}
 \hline
-\textbf{Factor} & \textbf{H2O} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
+\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
 \hline
@@
 
-\multicolumn{5}{c}%
+\multicolumn{7}{c}%
 {\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
@@
 
-\hline \multicolumn{5}{|r|}{\textit{Continued on next page}} \\
+\hline \multicolumn{7}{|r|}{\textit{Continued on next page}} \\
 \hline
@@
 \textbf{Time Management} & Time Constraints are Settable & Generations and population size & Time constraints are Settable & Optimized for quick results & Settable time constraints & Settable time constraints\\
+\hline
 \textbf{Ensemble Methods} & Yes (stacking + blending) & Yes (stacking) & Yes (stacking + blending) & No & Yes (stacking) & Yes (stacking) \\
@@
 \textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. & Basic (feature importance) \\
-\hline
 \hline
@@
 
-\end{document}
+Keeping the factors we have laid out in mind, namely expeditious running, accuracy, and interpretability, we uncovered a key continuity in framework design: frameworks are forced to run and train the majority of their available models to maximize accuracy at the expense of efficiency.
+Given the restricted nature of tabular data, there are some models that, in general, are less likely to perform well, thus running and training these models is frequently wasteful.
+Cutting these models completely, however, is not optimal either, as they are the best option in a minority of cases and give frameworks versatility.
+We hypothesized that using a combination of layered machine learning implementation in which we train a model to predict a basic framework's outputs and meta-feature extraction in which we accelerate the training process by reducing complicated data matrices to their measurable attributes would yield an equally versatile system that minimizes time spent on prediction while still maximizing accuracy and straightforward implementation in a medical context.
 

### 2024-06-15 SMEML/SMEML.py
SMEML final experiment

@@ -139,7 +139,7 @@ class SMEML:
 
     def bayes_cv_callback(self, res, model_name=None):
         # print the current model name
-        print(f"[{model_name}] Iteration {res['x_iters'][-1]}: ")
+        print(f"[{model_name}] Iteration {res['x']}, accuracy: {res['fun']*-1}")
 
     def get_dataset_attributes(self):
         attributes = {}

### 2024-06-15 SMEML/SMEML.py
SMEML perf upgrade

@@ -1,16 +1,19 @@
+# sklearn intel patch
+# check if x86 or arm
+import platform
+if platform.machine() == 'x86_64':
+    from sklearnex import patch_sklearn
+    patch_sklearn()
+
 import pickle as pkl
 import numpy as np
-from sklearn.model_selection import cross_val_score, train_test_split
-from xgboost import XGBRegressor, XGBClassifier
-from sklearn.multioutput import MultiOutputRegressor
-from sklearn.ensemble import VotingClassifier
+from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
 from sklearn.compose import ColumnTransformer
 from skopt import BayesSearchCV
 import os
 import multiprocessing
 from SMEML.models import classifiers, param_grids
-from multiprocessing import freeze_support
 from functools import partial
 import logging
 
@@ -37,11 +40,9 @@ logger.addFilter(
 classifier_names = [
     'SVC',
     'SGDClassifier',
-    'RidgeClassifierCV',
     'RidgeClassifier',
     'Perceptron',
     'PassiveAggressiveClassifier',
-    'LogisticRegressionCV',
     'LogisticRegression',
     'LinearSVC',
     'RandomForestClassifier',
@@ -94,15 +95,15 @@ class SMEML:
 
         results = smeml_model.predict(input)
 
-        top = np.argsort(results[0])[-10:]
+        top = np.argsort(results[0])[-8:]
 
         model_threads = []
         self.models = []
         manager = multiprocessing.Manager()
         return_dict = manager.dict()
         for i in top:
-            thread = multiprocessing.Process(
-                target=self.train_thread, args=(classifiers[i], return_dict,))
+            thread = multiprocessing.Process(name=classifier_names[i],
+                target=self.train_thread, args=(classifiers[i], classifier_names[i], return_dict,))
             model_threads.append(thread)
 
         for thread in model_threads:
@@ -124,13 +125,13 @@ class SMEML:
         self.generate_report()
         self.save_final_model()
 
-    def train_thread(self, model, return_dict):
-        print("Training model: ", model)
+    def train_thread(self, model, model_name, return_dict):
+        print("Training model: ", model_name)
         optimizer = BayesSearchCV(
-            model, param_grids[model.__class__.__name__], n_iter=10, cv=3)
+            model, param_grids[model_name], n_iter=10, cv=3, error_score=0)
 
         optimizer.fit(self.X_train, self.y_train,
[…]

### 2024-06-15 SMEML/models.py

@@ -36,11 +36,9 @@ import numpy as np
 classifiers = np.array([
     SVC(kernel='rbf', C=1.0, verbose=False),
     SGDClassifier(loss='hinge', max_iter=1000, tol=1e-3),
-    RidgeClassifierCV(alphas=[0.1, 1.0, 10.0]),
     RidgeClassifier(alpha=1.0),
     Perceptron(max_iter=1000, tol=1e-3),
     PassiveAggressiveClassifier(max_iter=1000, tol=1e-3),
-    LogisticRegressionCV(cv=5, max_iter=1000, verbose=0),
     LogisticRegression(max_iter=1000, verbose=0),
     LinearSVC(max_iter=1000, verbose=0),
     RandomForestClassifier(n_estimators=100, verbose=0),
@@ -75,14 +73,7 @@ param_grids = {
     'SGDClassifier': {
         'loss': ['hinge', 'log', 'modified_huber', 'squared_hinge', 'perceptron'],
         'penalty': ['l2', 'l1', 'elasticnet'],
-        'alpha': [0.0001, 0.001, 0.01, 0.1],
         'max_iter': [1000, 2000],
-        'tol': [1e-3, 1e-4],
-    },
-    'RidgeClassifierCV': {
-        'alphas': [[0.01, 0.1, 1.0, 10.0, 100.0]],
-        'fit_intercept': [True, False],
-        'normalize': [True, False],
     },
     'RidgeClassifier': {
         'alpha': [0.01, 0.1, 1.0, 10.0],
@@ -91,7 +82,7 @@ param_grids = {
     },
     'Perceptron': {
         'penalty': [None, 'l2', 'l1', 'elasticnet'],
-        'alpha': [0.0001, 0.001, 0.01, 0.1],
+        'alpha': [0.001, 0.01, 0.1],
         'max_iter': [1000, 2000],
         'tol': [1e-3, 1e-4],
     },
@@ -99,12 +90,6 @@ param_grids = {
         'C': [0.01, 0.1, 1, 10],
         'max_iter': [1000, 2000],
         'tol': [1e-3, 1e-4],
-    },
-    'LogisticRegressionCV': {
-        'cv': [3, 5, 10],
-        'penalty': ['l2'],
-        'solver': ['lbfgs', 'liblinear', 'sag', 'saga'],
-        'max_iter': [1000, 2000],
     },
     'LogisticRegression': {
         'C': [0.01, 0.1, 1.0, 10.0, 100.0],
[…]

### 2024-06-15 SMEML/SMEML.py
f

@@ -70,9 +70,10 @@ classifier_names = [
 
 
 class SMEML:
-    def __init__(self):
+    def __init__(self, iterations=10):
         self.X = None
         self.y = None
+        self.iterations = iterations
 
     def train(self, X, y):
         self.X = X
@@ -128,7 +129,7 @@ class SMEML:
     def train_thread(self, model, model_name, return_dict):
         print("Training model: ", model_name)
         optimizer = BayesSearchCV(
-            model, param_grids[model_name], n_iter=10, cv=3, error_score=0)
+            model, param_grids[model_name], n_iter=self.iterations, cv=3, error_score=0)
 
         optimizer.fit(self.X_train, self.y_train,
                       callback=partial(self.bayes_cv_callback, model_name=model_name))

### 2024-06-15 example.py

@@ -17,7 +17,7 @@ if __name__ == "__main__":
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-    smeml = SMEML()
+    smeml = SMEML(iterations=30)
 # train the model
     smeml.train(X, y)
     time_end = time.time()

### 2024-06-16 SMEML/SMEML.py
stack

@@ -10,7 +10,9 @@ import numpy as np
 from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
 from sklearn.compose import ColumnTransformer
+from sklearn.ensemble import StackingClassifier, VotingClassifier
 from skopt import BayesSearchCV
+from xgboost import XGBClassifier
 import os
 import multiprocessing
 from SMEML.models import classifiers, param_grids
@@ -99,7 +101,6 @@ class SMEML:
         top = np.argsort(results[0])[-8:]
 
         model_threads = []
-        self.models = []
         manager = multiprocessing.Manager()
         return_dict = manager.dict()
         for i in top:
@@ -113,15 +114,28 @@ class SMEML:
         # wait for all threads to finish
         for thread in model_threads:
             thread.join()
+        
+        self.model_accuracies = []
+        self.models = []
 
+        # loop through return dict and get the models and accuracies
         for key, value in return_dict.items():
-            self.models.append((key, value))
+            if 'accuracy' in key:
+                self.model_accuracies.append((key, value))
+            else:
+                self.models.append((key.replace('_model', ''), value))
 
-        # get best model
-        self.best_model = max(self.models, key=lambda x: (x[1]))
+        print(self.models)
 
-        print("Best model: ", self.best_model[0],
-              " with accuracy: ", self.best_model[1])
+        stacking_classifier = StackingClassifier(estimators=self.models, final_estimator=XGBClassifier())
+
+        stacking_classifier.fit(self.X_train, self.y_train)
+
+        accuracy = stacking_classifier.score(self.X_test, self.y_test)
+
+        print("stacking classifier accuracy: ", accuracy)
+
+        self.best_model = (stacking_classifier, accuracy)
 
         self.generate_report()
         self.save_final_model()
@@ -137,7 +151,9 @@ class SMEML:
         accuracy = optimizer.score(self.X_test, self.y_test)
         print("Model: ", model, " with accuracy: ", accuracy)
 
-        return_dict[model] = accuracy
+
+        return_dict[model_name + '_accuracy'] = accuracy
+        return_dict[model_name + '_model'] = optimizer.best_estimator_
 
     def bayes_cv_callback(self, res, model_name=None):
         # print the current model name

### 2024-06-16 example.py

@@ -17,7 +17,7 @@ if __name__ == "__main__":
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-    smeml = SMEML(iterations=30)
+    smeml = SMEML(iterations=5)
 # train the model
     smeml.train(X, y)
     time_end = time.time()

### 2024-06-16 kaggle-dataset-download/koogle.py
Update koogle.py

@@ -11,7 +11,7 @@ datasets = []
 start_page = 1
 page_count = 10
 topics = ["kidney", "diabetes", "renal",
-          "chickenpox", "influenza", "congenital"]
+          "chickenpox", "influenza", "congenital", "lung", "heart", "thyroid", "cancer", "COVID", "malaria", "bone", "brain", "alzheimer's", "obesity", "adrenal", "stomach", "small intestine", "ulcer"]
 for i in range(start_page, start_page + page_count + 1):
     for j in range(len(topics)):
         dataset_page = api.dataset_list(

### 2024-06-16 paper.tex
SMEML final experiment
Update paper.tex

@@
 \usepackage{xcolor}         % colors
+\usepackage{geometry}
+\usepackage{longtable}
+\usepackage{graphicx}
 
@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
-Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated.
+Many of these frameworks optimize a form of model selection, however, they all require most models to be run and evaluated.
 We propose a novel framework that automatically eliminates models that are unlikely to be performant by training a Boosting Model on hundreds of kaggle datasets.
@@
 This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue.
-
+%
 Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected.
@@
 \subsection{Survey}
-
-\documentclass{article}
-\usepackage{geometry}
-\usepackage{longtable}
-\usepackage{graphicx}
-
-\geometry{a4paper, margin=1in}
-
-\begin{document}
 
@@
 \end{longtable}
+Table 1: Comparison of six AutoML frameworks based on commonmly evaluated criteria as well as more obscure features relevant to the medical diagnosis process
 
-Keeping the factors we have laid out in mind, namely expeditious running, accuracy, and interpretability, we uncovered a key continuity in framework design: frameworks are forced to run and train the majority of their available models to maximize accuracy at the expense of efficiency.
+We systematically reviewed and compared six different AutoML frameworks, comparing every feature relevant to medical implementation.
+Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
+By testing our new framework against these four in evaluating medical data, we hoped to delineate key weaknesses and strengths in our own design.
+
+Taking a closer look at four AutoML standards, we can observe pros and cons in their theoretical application to medicine and research.
+FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere.
+It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers.
+H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average.
+In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour.
+H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users.
+MLJAR uses more advanced algorithms such as light gradient boosting and neural networks.
+It automatically deals with missing values and is known for its automated user interface.
+TPOT uses genetic programming.
+It builds pipelines over multiple generations, which can be time consuming.
+It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users.
+
+Keeping the factors we have laid out in mind, namely expeditious running, accuracy, and interpretability, we also uncovered a key continuity in framework design: frameworks are forced to run and train the majority of their available models to maximize accuracy at the expense of efficiency.
 Given the restricted nature of tabular data, there are some models that, in general, are less likely to perform well, thus running and training these models is frequently wasteful.
@@
 
-\subsection{Data Collection}
+\subsection{Training}
 
-\subsection{Model Elimination}
+Insert Table Here
+Table 2: Meta-features extracted in simplifcation of the Kaggle dataset-optimal model dataset
 
-\section{Experiments}
+We used a Kaggle API library to search Kaggle using 20 medically-relevant key words.
+We limited our search to tabular datasets and obtained 300 viable datasets for training.
+We ran the Kaggle datasets through a rudimentary framework, pairing them with ML algorithms predicted to perform most optimally on that data.
+These ML algorithms were untrained and were selected from a pool of 30 candidates.
+The resulting 2x300 matrix then went through manuel meta-feature extraction (See Table 2).
+This new matrix was then used to train an XGBoost algorithm using a rank-based prediction system.
+
+\subsection{Experiments}
 
 \section{Discussion}
-
-\section{Conclusion}
 

### 2024-06-16 paper.tex
dataset attributes

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{booktabs}
 
@@
 \hline
-\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. & Basic (feature importance) \\
+\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. Basic (feature importance) \\
 \hline
@@
 It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers.
-H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average.
+H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on Mean.
 In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour.
@@
 
-\subsection{Training}
+\subsection{Overview}
+When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best.
+For example, linear models tend to work better on datasets where there is a linear relationship between features.
+As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
 
-Insert Table Here
-Table 2: Meta-features extracted in simplifcation of the Kaggle dataset-optimal model dataset
-
-We used a Kaggle API library to search Kaggle using 20 medically-relevant key words.
-We limited our search to tabular datasets and obtained 300 viable datasets for training.
-We ran the Kaggle datasets through a rudimentary framework, pairing them with ML algorithms predicted to perform most optimally on that data.
-These ML algorithms were untrained and were selected from a pool of 30 candidates.
-The resulting 2x300 matrix then went through manuel meta-feature extraction (See Table 2).
-This new matrix was then used to train an XGBoost algorithm using a rank-based prediction system.
+\begin{table}
+  \caption{Model Options}
+  \label{model-options-table}
+  \centering
+  \begin{tabular}{lll}
+    \toprule
+    Attribute & Model & Purpose                         \\
+    \midrule
+    \# of Rows & $|\mathbf{A}|_r$ & Data Size \\
+    \hline
+    \# of Columns & $|\mathbf{A}|_c$ & Data Size \\
+    \hline
+    Target Distribution &
+    $\frac{\max(\text{count}_1, \text{count}_0)}{|\mathbf{A}|_r}$
+    & Data Type \\
+    \hline
+    Numerical Columns &
+    $\frac{|\mathbf{A}_{num}|}{|\mathbf{A}|_{c}}$
+    & Data Type \\
+    \hline
+    Binary Categorical Columns &
+    $\frac{|\mathbf{A}_{bin}|}{|\mathbf{A}|_{c}}$
+    & Data Type \\
+    \hline
+    Mean \# of Distinct Values  & $\mu \left\{\text{\# of distinct values in column}\right\}$ & Data Type \\ 
+    \hline
+    Mean IQR  & $\mu \left\{\text{IQR of column}\right\}$ & Data Distribution \\ 
+    \hline
+    Standard Deviation of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & Data Distribution \\
+    \hline
+    Mean Q1 & $\mu \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
+    \hline
+    Standard Deviation of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
+    \hline
+    Mean Q3  & $\mu \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
+    \hline
+    Standard Deviation of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
+    \hline
+    Mean Percent of Z-Score Outliers  & 
+    $\mu \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & Outlier Data Points \\
+    \hline
+    Standard Deviation of Percent of Z-Score Outliers  &
+    $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & Outlier Data Points \\
+    \hline
+    Mean Correlation& $\mu \left\{\text{Correlation Matrix}\right\}$ & Data linearity \\
+    \hline
+    Standard Deviation of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & Data Linearity \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2024-06-16 paper.tex
another dataset

@@
 
-\subsection{Overview}
+\subsection{Observation}
 When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best.
@@
 \begin{table}
-  \caption{Model Options}
+  \caption{Attributes extracted from a dataset}
   \label{model-options-table}
@@
     \toprule
-    Attribute & Model & Purpose                         \\
+    Attribute & Formula & Purpose\\
     \midrule
@@
 
+\subsection{Data Extraction}
+To train our boosting model, we collected over a thousand datasets from kaggle, a popular website for hosting public datasets.
+After used various medical terms to filter down datasets and limiting our search to tabular, binary-classification datasets, we were left with 268 datasets.
+We extracted the attributes in Table 2.
+from each dataset and ran every model on each dataset to get the performace of each model.
+We trained a multilabel regression model on these attributes to predict the rank of every model on a specific dataset.
+
 \subsection{Experiments}

### 2024-06-16 SMEML/SMEML.py

@@ -143,7 +143,7 @@ class SMEML:
     def train_thread(self, model, model_name, return_dict):
         print("Training model: ", model_name)
         optimizer = BayesSearchCV(
-            model, param_grids[model_name], n_iter=self.iterations, cv=3, error_score=0)
+            model, param_grids[model_name], n_iter=self.iterations, cv=3)
 
         optimizer.fit(self.X_train, self.y_train,
                       callback=partial(self.bayes_cv_callback, model_name=model_name))
@@ -203,8 +203,12 @@ class SMEML:
                 categorical_average_count += self.X[col].nunique()
 
         attributes['numerical_columns'] = numerical_features/self.X.shape[1]
-        attributes['binary_categorical'] = binary_categorical/categorical_count
-        attributes['categorical_average_count'] = categorical_average_count / \
+        if categorical_count == 0:
+            attributes['binary_categorical'] = 0
+            attributes['categorical_average_count'] = 0
+        else:
+            attributes['binary_categorical'] = binary_categorical/categorical_count
+            attributes['categorical_average_count'] = categorical_average_count / \
             categorical_count
         attributes['average_iqr'] = np.mean(iqr_values)
         attributes['average_q1'] = np.mean(q1_values)
@@ -213,9 +217,9 @@ class SMEML:
         attributes['q1_std'] = np.mean(np.std(q1_values))
         attributes['q3_std'] = np.mean(np.std(q3_values))
         print("Numerical columns: ", numerical_features/self.X.shape[1])
-        print("Binary categorical: ", binary_categorical/categorical_count)
+        print("Binary categorical: ", attributes['binary_categorical'])
         print("Categorical average count: ",
-              categorical_average_count/categorical_count)
+              attributes['categorical_average_count'])
         print("Average IQR: ", np.mean(iqr_values))
         print("Average Q1: ", np.mean(q1_values))
         print("Average Q3: ", np.mean(q3_values))
@@ -292,6 +296,8 @@ class SMEML:
             verbose_feature_names_out=False).set_output(transform='pandas')
 
         self.X = preprocessor.fit_transform(self.X)
+
+        print(self.X)
 
     def generate_report(self):
         lines = []

### 2024-06-16 benchmarks/FLAML/flame.py

@@ -8,11 +8,11 @@ import xgboost
 xgboost_version = xgboost.__version__
 
 # Load your dataset
-dataset_path = '../../MTF/SAHeart.csv'  # Specify the path to your dataset file
+dataset_path = '../../benchmark_datasets/parkinsons.csv'  # Specify the path to your dataset file
 data = pd.read_csv(dataset_path)
 
-X = data.drop(columns=["chd"])  # Adjust the column name as per your dataset
-y = data["chd"]  # Adjust the column name as per your dataset
+X = data.drop(columns=["status"])  # Adjust the column name as per your dataset
+y = data["status"]  # Adjust the column name as per your dataset
 
 X_train, X_test, y_train, y_test = train_test_split(
     X, y, test_size=0.2, random_state=42)
@@ -20,8 +20,6 @@ X_train, X_test, y_train, y_test = train_test_split(
 # Customize FLAML's AutoML
 automl = AutoML()
 automl_settings = {
-    "time_budget": 60,  # Set the maximum time budget for AutoML in seconds
-    # Specify the type of task (classification or regression)
     "task": "classification",
     "metric": "accuracy",  # Choose the evaluation metric to optimize
     "learner_selector": "auto",  # Let FLAML automatically select the learners

### 2024-06-16 benchmarks/H2O/water.py

@@ -7,7 +7,7 @@ time_start = time.time()
 h2o.init()
 
 # Import a sample binary outcome train/test set into H2OAutoML
-df = pd.read_csv("../../benchmark_datasets/heart.csv")
+df = pd.read_csv("../../benchmark_datasets/parkinsons.csv")
 
 # Convert the pandas DataFrame to an H2OFrame.
 h2o_df = h2o.H2OFrame(df)
@@ -15,7 +15,7 @@ h2o_df = h2o.H2OFrame(df)
 # Identify predictors and response
 x = h2o_df.columns
 
-y = "target"
+y = "status"
 
 x.remove(y)
 

### 2024-06-16 example.py

@@ -6,10 +6,10 @@ import time
 if __name__ == "__main__":
     time_start = time.time()
     # load the dataset
-    df = pd.read_csv('./benchmark_datasets/heart.csv')
+    df = pd.read_csv('./benchmark_datasets/parkinsons.csv')
 
-    X = df.drop('target', axis=1)
-    y = df['target']
+    X = df.drop('status', axis=1)
+    y = df['status']
 
 # label encoding
 # y = y.map({'ckd': 1, 'notckd': 0})
@@ -17,7 +17,7 @@ if __name__ == "__main__":
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-    smeml = SMEML(iterations=5)
+    smeml = SMEML(iterations=32)
 # train the model
     smeml.train(X, y)
     time_end = time.time()

### 2024-06-16 paper.tex
SMEML process flow chart

--- 2024-06-16 paper.tex
@@
     \hline
-    Standard Deviation of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & Data Distribution \\
+    STD of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & Data Distribution \\
     \hline
@@
     \hline
-    Standard Deviation of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
+    STD of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
     \hline
@@
     \hline
-    Standard Deviation of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
+    STD of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
     \hline
@@
     \hline
-    Standard Deviation of Percent of Z-Score Outliers  &
+    STD of Percent of Z-Score Outliers  &
     $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & Outlier Data Points \\
@@
     \hline
-    Standard Deviation of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & Data Linearity \\
+    STD of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & Data Linearity \\
     \bottomrule
@@
 \end{table}
+
+\begin {figure}
+\centering
+\fbox{\includegraphics[width=\textwidth]{smeml-flowchart.png}}
+\caption{SMEML Process}
+\end{figure}
+\subsection{Model Elimination}
 

### 2024-06-16 SMEML/SMEML.py

@@ -125,7 +125,8 @@ class SMEML:
             else:
                 self.models.append((key.replace('_model', ''), value))
 
-        print(self.models)
+        # take top 3 models
+        self.models = sorted(self.model_accuracies, key=lambda x: x[1], reverse=True)[:3]
 
         stacking_classifier = StackingClassifier(estimators=self.models, final_estimator=XGBClassifier())
 

### 2024-06-16 benchmarks/TPOT/pot.py

@@ -6,15 +6,15 @@ import time
 
 time_start = time.time()
 
-data = pd.read_csv('../../benchmark_datasets/heart.csv')
+data = pd.read_csv('../../benchmark_datasets/parkinsons.csv')
 
-X = data.drop(columns=['target'])
-y = data['target']
+X = data.drop(columns=['status'])
+y = data['status']
 
 X_train, X_test, y_train, y_test = train_test_split(
     X, y, test_size=0.2, random_state=42)
 
-tpot = TPOTClassifier(population_size=20,
+tpot = TPOTClassifier(generations=50, population_size=20,
                       verbosity=2, random_state=42)
 
 tpot.fit(X_train, y_train)

### 2024-06-16 benchmarks/TPOT/tpot_heart_pipeline.py

@@ -9,8 +9,8 @@ features = tpot_data.drop('target', axis=1)
 training_features, testing_features, training_target, testing_target = \
             train_test_split(features, tpot_data['target'], random_state=42)
 
-# Average CV score on the training set was: 0.9890243902439024
-exported_pipeline = GradientBoostingClassifier(learning_rate=1.0, max_depth=9, max_features=0.4, min_samples_leaf=20, min_samples_split=12, n_estimators=100, subsample=0.6000000000000001)
+# Average CV score on the training set was: 0.9612903225806452
+exported_pipeline = GradientBoostingClassifier(learning_rate=0.5, max_depth=6, max_features=0.6000000000000001, min_samples_leaf=10, min_samples_split=8, n_estimators=100, subsample=0.8)
 # Fix random state in exported estimator
 if hasattr(exported_pipeline, 'random_state'):
     setattr(exported_pipeline, 'random_state', 42)

### 2024-06-16 example.py

@@ -17,7 +17,7 @@ if __name__ == "__main__":
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-    smeml = SMEML(iterations=32)
+    smeml = SMEML(iterations=10)
 # train the model
     smeml.train(X, y)
     time_end = time.time()

### 2024-06-16 paper.tex
draft methodology

@@
 \section{Methodology}
-
-\subsection{Observation}
 When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best.
@@
 As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
+These extracted attributes are shown in Table 2.
 
+We considered 28 different models, including all supervised and semi-supervised sklearn classification models and common boosting models such as XGBoost, Lightgbm, and Catboost.
+
+To implement this model elimination process, we trained a boosting model on 268 kaggle datasets.
+We choose datasets that were medically related and focused our approach to binary classification.
+We extracted the attributes in Table 2 from each dataset, this is the input for the boosting model.
+We then ran a "dumb" framework that trained every model on each dataset.
+The accuracy of every model is ranked and every model is treated as a label with its value being its rank.
+Then we trained a multilabel regression to predict the rank of each model giving the extracted attributes.
+We produced a median spearman correlation of 0.7301 between the predicted rank and the actual rank and a median p-value of 1.032e-05.
+Furthermore, we guarantee that we can predict a top two model within the predicted top ten 90.12\% of the time.
+
+When a user inputs a dataset into SMEML, it first extracts the attributes from the dataset.
+It feeds these attributes into the boosting model to get the predicted rank of each model.
+Since we have determined that we can predict a top two model within the predicted top ten quite confidently we can eliminate the bottom 18 models from the list.
+We run bayseian optimization on the top ten models to get the best hyperparamters for each model.
+We select the top models that have significantly better performance than other models.
+These models are stacked together to form the final model.
+This process is shown in Figure 1.
 \begin{table}
@@
 \end{figure}
-\subsection{Model Elimination}
 

### 2024-06-16 paper.tex
fix survey

@@
 \usepackage{booktabs}
+\usepackage{caption}
 
@@
 
-\begin{longtable}{|l|l|l|l|l|l|l|}
-\hline
-\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
-\hline
-\endfirsthead
-
-\multicolumn{7}{c}%
-{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
-\hline
-\textbf{Factor} & \textbf{H2O AutoML} & \textbf{TPOT} & \textbf{MLJAR} & \textbf{FLAML} & \textbf{LightAutoML} & \textbf{GAMA} \\
-\hline
-\endhead
-
-\hline \multicolumn{7}{|r|}{\textit{Continued on next page}} \\
-\hline
-\endfoot
-
-\hline
-\endlastfoot
-
-\textbf{Ease of Use} & Easy-to-use GUI and API & Python library, requires coding experience & Very user-friendly web interface, detailed API & Simple API & User-friendly API with minimal coding & Python library with fairly intuitive API\\
-\hline
-\textbf{Supported Algorithms} & Linear, Tree, DNN, Clustering, etc.
-& Genetic Programming & Linear, Tree, LightGBM, CatBoost, Clustering, etc.
-(no DNN) & Linear, Tree, Clustering - More limited and lightweight & Linear, LightGBM, Catboost, etc.
-& Linear, tree, SVM, etc.
-\\
-\hline
-\textbf{Feature Engineering} & Basic & Basic & Advanced - includes feature interactions & Limited & Advanced (automatic) & Basic \\
-\hline
-\textbf{Time Management} & Time Constraints are Settable & Generations and population size & Time constraints are Settable & Optimized for quick results & Settable time constraints & Settable time constraints\\
-\hline
-\textbf{Ensemble Methods} & Yes (stacking + blending) & Yes (stacking) & Yes (stacking + blending) & No & Yes (stacking) & Yes (stacking) \\
-\hline
-\textbf{Hyperparameter Tuning} & Automated & Genetic algorithm & Automated and customizable & Automated and efficient tuning & Automated & Automated \\
-\hline
-\textbf{Model Interpretability} & SHAP, LIME, PDPs, MOJO & POJO, etc. & Basic & SHAP, LIME, PDPs, etc. & Basic (permutation importance) & SHAP, PDPs, etc. Basic (feature importance) \\
-\hline
-\textbf{Scalability} & Good (distributed computing) & Limited & Good & Good (resource-efficient) & Good (distributing computing) & Moderate \\
-\hline
-\textbf{Customization} & High & Moderate & High & Low-Moderate & Moderate & Moderate \\
-\hline
-
-\end{longtable}
+\begin{table}
+  \caption{Survey of Existing AutoML Frameworks}
+  \label{automl-survey}
+  \centering
+  \begin{tabular}{lllllllll}
+    \toprule
+    Framework & EOU & Algs & FE & TM & HPT & Inter & Custom\\
+    \midrule
+    H2O AutoML & Easy & 10 & Basic & Yes & Auto & SHAP & High\\
+    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
+    MLJAR & Easy & 10 & Advanced & Yes & Auto & Basic & High\\
+    FLAML & Easy & 10 & Limited & Yes & Auto & SHAP & Low-Moderate\\
+    LightAutoML & Easy & 10 & Advanced & Yes & Auto & Basic & Moderate\\
+    GAMA & Hard & 10 & Basic & Yes & Auto & SHAP & Moderate\\
+    \bottomrule
+  \end{tabular}
+  \captionsetup{font=footnotesize}
+  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, Algs: Algorithms, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
+\end{table}
 Table 1: Comparison of six AutoML frameworks based on commonmly evaluated criteria as well as more obscure features relevant to the medical diagnosis process
@@
 We run bayseian optimization on the top ten models to get the best hyperparamters for each model.
+Each model's optimization is run in its own process and in parralell.
 We select the top models that have significantly better performance than other models.

### 2024-06-17 SMEML/SMEML.py
new dataset

@@ -12,7 +12,7 @@ from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
 from sklearn.compose import ColumnTransformer
 from sklearn.ensemble import StackingClassifier, VotingClassifier
 from skopt import BayesSearchCV
-from xgboost import XGBClassifier
+from xgboost import XGBClassifier, XGBRegressor
 import os
 import multiprocessing
 from SMEML.models import classifiers, param_grids
@@ -81,11 +81,10 @@ class SMEML:
         self.X = X
         self.y = y
 
+        self.preprocess()
+
         self.X_train, self.X_test, self.y_train, self.y_test = train_test_split(
             self.X, self.y, test_size=0.2, random_state=42)
-
-        # fill nan values
-        self.preprocess()
 
         attributes = self.get_dataset_attributes()
 
@@ -116,19 +115,24 @@ class SMEML:
             thread.join()
         
         self.model_accuracies = []
-        self.models = []
+        self.models = {}
 
         # loop through return dict and get the models and accuracies
         for key, value in return_dict.items():
             if 'accuracy' in key:
-                self.model_accuracies.append((key, value))
+                self.model_accuracies.append((key.replace('_accuracy', ''), value))
             else:
-                self.models.append((key.replace('_model', ''), value))
+                self.models[key.replace('_model', '')] = value
 
+        self.model_accuracies = sorted(self.model_accuracies, key=lambda x: x[1], reverse=True)
         # take top 3 models
-        self.models = sorted(self.model_accuracies, key=lambda x: x[1], reverse=True)[:3]
+        self.top_models_accuracies = self.model_accuracies[:3]
 
-        stacking_classifier = StackingClassifier(estimators=self.models, final_estimator=XGBClassifier())
+        self.top_models = [(model_name, self.models[model_name]) for model_name, _ in self.top_models_accuracies]
+
+        # train the stacking classifier
+        print("Training stacking classifier")
+        stacking_classifier = StackingClassifier(estimators=self.top_models, final_estimator=XGBClassifier(), verbose=2, n_jobs=-1)
 
         stacking_classifier.fit(self.X_train, self.y_train)
 
@@ -270,6 +274,9 @@ class SMEML:
         numerical_features = self.X.select_dtypes(
             include=['int64', 'float64']).columns
 
+        print("Categorical features: ", categorical_features)
+        print("Numerical features: ", numerical_features)
+
         # fill missing values
[…]

### 2024-06-17 SMEML/models.py

@@ -71,7 +71,7 @@ param_grids = {
         'gamma': ['scale', 'auto'],
     },
     'SGDClassifier': {
-        'loss': ['hinge', 'log', 'modified_huber', 'squared_hinge', 'perceptron'],
+        'loss': ['squared_error', 'squared_epsilon_insensitive', 'squared_hinge', 'hinge', 'perceptron', 'huber', 'epsilon_insensitive', 'log_loss', 'modified_huber'],
         'penalty': ['l2', 'l1', 'elasticnet'],
         'max_iter': [1000, 2000],
     },

### 2024-06-17 benchmarks/FLAML/flame.py

@@ -8,22 +8,22 @@ import xgboost
 xgboost_version = xgboost.__version__
 
 # Load your dataset
-dataset_path = '../../benchmark_datasets/parkinsons.csv'  # Specify the path to your dataset file
+# Specify the path to your dataset file
+dataset_path = '../../benchmark_datasets/heart2.csv'
 data = pd.read_csv(dataset_path)
 
-X = data.drop(columns=["status"])  # Adjust the column name as per your dataset
-y = data["status"]  # Adjust the column name as per your dataset
+# Adjust the column name as per your dataset
+X = data.drop(columns=["HeartDisease"])
+y = data["HeartDisease"]  # Adjust the column name as per your dataset
 
 X_train, X_test, y_train, y_test = train_test_split(
     X, y, test_size=0.2, random_state=42)
 
 # Customize FLAML's AutoML
-automl = AutoML()
+automl = AutoML(max_iter=100, task="classification", log_file_name="flaml.log")
 automl_settings = {
     "task": "classification",
     "metric": "accuracy",  # Choose the evaluation metric to optimize
-    "learner_selector": "auto",  # Let FLAML automatically select the learners
-    # Add more parameters as needed
 }
 
 # Fit the model using the customized settings

### 2024-06-17 example.py

@@ -6,10 +6,10 @@ import time
 if __name__ == "__main__":
     time_start = time.time()
     # load the dataset
-    df = pd.read_csv('./benchmark_datasets/parkinsons.csv')
+    df = pd.read_csv('./benchmark_datasets/heart2.csv')
 
-    X = df.drop('status', axis=1)
-    y = df['status']
+    X = df.drop('HeartDisease', axis=1)
+    y = df['HeartDisease']
 
 # label encoding
 # y = y.map({'ckd': 1, 'notckd': 0})

### 2024-06-18 SMEML/SMEML.py
dumb mode

@@ -18,6 +18,7 @@ import multiprocessing
 from SMEML.models import classifiers, param_grids
 from functools import partial
 import logging
+import optuna
 
 np.int = int
 
@@ -72,9 +73,10 @@ classifier_names = [
 
 
 class SMEML:
-    def __init__(self, iterations=10):
+    def __init__(self, iterations=10, mode="SME"):
         self.X = None
         self.y = None
+        self.mode = mode
         self.iterations = iterations
 
     def train(self, X, y):
@@ -86,6 +88,15 @@ class SMEML:
         self.X_train, self.X_test, self.y_train, self.y_test = train_test_split(
             self.X, self.y, test_size=0.2, random_state=42)
 
+        if self.mode == "SME":
+            self.SMEmodel()
+        if self.mode == "dumb":
+            self.dumbmode()
+
+        self.generate_report()
+        self.save_final_model()
+
+    def SMEmodel(self):
         attributes = self.get_dataset_attributes()
 
         # train the model
@@ -142,27 +153,42 @@ class SMEML:
 
         self.best_model = (stacking_classifier, accuracy)
 
-        self.generate_report()
-        self.save_final_model()
+    def dumbmode(self):
+        # train all models
+        for i in range(len(classifiers)):
+            model = classifiers[i]
+            model_name = classifier_names[i]
+
+            study = optuna.create_study(direction='maximize', study_name=model_name, storage='sqlite:///optuna.db', load_if_exists=True)
+            study.optimize(partial(self.objective, model=model, model_name=model_name), n_trials=self.iterations)
+
+            estimator = model.set_params(**study.best_params)
+            estimator.fit(self.X_train, self.y_train)
+            accuracy = estimator.score(self.X_test, self.y_test)
+            self.model_accuracies.append((model_name, accuracy))
+            self.models[model_name + '_model'] = estimator
+            self.models[model_name + '_accuracy'] = accuracy
 
     def train_thread(self, model, model_name, return_dict):
         print("Training model: ", model_name)
-        optimizer = BayesSearchCV(
-            model, param_grids[model_name], n_iter=self.iterations, cv=3)
 
-        optimizer.fit(self.X_train, self.y_train,
-                      callback=partial(self.bayes_cv_callback, model_name=model_name))
+        study = optuna.create_study(direction='maximize', study_name=model_name, storage='sqlite:///optuna.db', load_if_exists=True)
[…]

### 2024-06-18 benchmarks/TPOT/pot.py

@@ -6,10 +6,10 @@ import time
 
 time_start = time.time()
 
-data = pd.read_csv('../../benchmark_datasets/parkinsons.csv')
+data = pd.read_csv('../../benchmark_datasets/heart2.csv')
 
-X = data.drop(columns=['status'])
-y = data['status']
+X = data.drop(columns=['HeartDisease'])
+y = data['HeartDisease']
 
 X_train, X_test, y_train, y_test = train_test_split(
     X, y, test_size=0.2, random_state=42)

### 2024-06-18 example.py

@@ -17,7 +17,7 @@ if __name__ == "__main__":
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-    smeml = SMEML(iterations=10)
+    smeml = SMEML(iterations=10, mode="dumb")
 # train the model
     smeml.train(X, y)
     time_end = time.time()

### 2024-06-19 SMEML/SMEML.py
dumb mode

@@ -11,14 +11,14 @@ from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import MinMaxScaler, OneHotEncoder
 from sklearn.compose import ColumnTransformer
 from sklearn.ensemble import StackingClassifier, VotingClassifier
-from skopt import BayesSearchCV
 from xgboost import XGBClassifier, XGBRegressor
 import os
 import multiprocessing
 from SMEML.models import classifiers, param_grids
 from functools import partial
 import logging
-import optuna
+from skopt import BayesSearchCV
+from tqdm import tqdm
 
 np.int = int
 
@@ -71,6 +71,9 @@ classifier_names = [
     'DummyClassifier'
 ]
 
+size_limits = {
+    'SVC': 10000,
+}
 
 class SMEML:
     def __init__(self, iterations=10, mode="SME"):
@@ -78,6 +81,7 @@ class SMEML:
         self.y = None
         self.mode = mode
         self.iterations = iterations
+        self.progress_bars = {}
 
     def train(self, X, y):
         self.X = X
@@ -159,20 +163,36 @@ class SMEML:
             model = classifiers[i]
             model_name = classifier_names[i]
 
-            study = optuna.create_study(direction='maximize', study_name=model_name, storage='sqlite:///optuna.db', load_if_exists=True)
-            study.optimize(partial(self.objective, model=model, model_name=model_name), n_trials=self.iterations)
+            # check if the dataset is too large for the model
+            if size_limits.get(model_name) is not None and self.X.shape[0] * self.X.shape[1] > size_limits[model_name]:
+                continue
+            
+            print("Training model: ", model_name)
+            try:
+                optimizer = BayesSearchCV(
+                    model,
+                    param_grids[model_name],
+                    n_iter=self.iterations,
+                    n_jobs=-1,
+                    verbose=0,
+                    error_score=0
+                )
 
-            estimator = model.set_params(**study.best_params)
-            estimator.fit(self.X_train, self.y_train)
-            accuracy = estimator.score(self.X_test, self.y_test)
-            self.model_accuracies.append((model_name, accuracy))
-            self.models[model_name + '_model'] = estimator
-            self.models[model_name + '_accuracy'] = accuracy
+                self.progress_bars[model_name] = tqdm(total=self.iterations, desc="Optimizing " + model_name)
+                optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
+
[…]

### 2024-06-19 SMEML/models.py

@@ -40,7 +40,7 @@ classifiers = np.array([
     Perceptron(max_iter=1000, tol=1e-3),
     PassiveAggressiveClassifier(max_iter=1000, tol=1e-3),
     LogisticRegression(max_iter=1000, verbose=0),
-    LinearSVC(max_iter=1000, verbose=0),
+    LinearSVC(max_iter=1000, dual=True, verbose=0),
     RandomForestClassifier(n_estimators=100, verbose=0),
     HistGradientBoostingClassifier(max_iter=100, verbose=0),
     GradientBoostingClassifier(n_estimators=100, verbose=0),
@@ -77,14 +77,13 @@ param_grids = {
     },
     'RidgeClassifier': {
         'alpha': [0.01, 0.1, 1.0, 10.0],
-        'fit_intercept': [True, False],
-        'normalize': [True, False],
+        'solver': ['auto', 'svd', 'cholesky', 'lsqr', 'sparse_cg', 'sag', 'saga'],
     },
     'Perceptron': {
-        'penalty': [None, 'l2', 'l1', 'elasticnet'],
-        'alpha': [0.001, 0.01, 0.1],
+        # 'penalty': [None, 'l2', 'l1', 'elasticnet'],
+        # 'alpha': [0.001, 0.01, 0.1],
         'max_iter': [1000, 2000],
-        'tol': [1e-3, 1e-4],
+        # 'tol': [1e-3, 1e-4],
     },
     'PassiveAggressiveClassifier': {
         'C': [0.01, 0.1, 1, 10],

### 2024-06-19 benchmarks/FLAML/flame.py

@@ -1,41 +1,0 @@
-from flaml import AutoML
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import accuracy_score
-import pandas as pd
-import pickle
-import xgboost
-
-xgboost_version = xgboost.__version__
-
-# Load your dataset
-# Specify the path to your dataset file
-dataset_path = '../../benchmark_datasets/heart2.csv'
-data = pd.read_csv(dataset_path)
-
-# Adjust the column name as per your dataset
-X = data.drop(columns=["HeartDisease"])
-y = data["HeartDisease"]  # Adjust the column name as per your dataset
-
-X_train, X_test, y_train, y_test = train_test_split(
-    X, y, test_size=0.2, random_state=42)
-
-# Customize FLAML's AutoML
-automl = AutoML(max_iter=100, task="classification", log_file_name="flaml.log")
-automl_settings = {
-    "task": "classification",
-    "metric": "accuracy",  # Choose the evaluation metric to optimize
-}
-
-# Fit the model using the customized settings
-automl.fit(X_train, y_train, **automl_settings)
-
-# Generate predictions using the trained model
-y_pred = automl.predict(X_test)
-
-# Evaluate the model's performance
-accuracy = accuracy_score(y_test, y_pred)
-print("Accuracy:", accuracy)
-
-# save the model
-with open('model.pkl', 'wb') as model_pkl:
-    pickle.dump(automl, model_pkl)

### 2024-06-19 benchmarks/H2O/water.py

@@ -1,38 +1,0 @@
-import h2o
-from h2o.automl import H2OAutoML
-import pandas as pd
-import time
-
-time_start = time.time()
-h2o.init()
-
-# Import a sample binary outcome train/test set into H2OAutoML
-df = pd.read_csv("../../benchmark_datasets/parkinsons.csv")
-
-# Convert the pandas DataFrame to an H2OFrame.
-h2o_df = h2o.H2OFrame(df)
-
-# Identify predictors and response
-x = h2o_df.columns
-
-y = "status"
-
-x.remove(y)
-
-# For binary classification, response should be a factor
-h2o_df[y] = h2o_df[y].asfactor()
-
-# Run AutoML for 20 base models (limited to 1 hour max runtime by default)
-aml = H2OAutoML(max_models=20, seed=1)
-
-aml.train(x=x, y=y, training_frame=h2o_df)
-
-# print accuracy
-print(aml.leaderboard)
-
-# print model
-print(aml.leader)
-
-time_end = time.time()
-
-print("Time taken: ", time_end - time_start)

### 2024-06-19 benchmarks/LIGHT/light.py

@@ -1,38 +1,0 @@
-import pandas as pd
-from lightautoml.automl.presets.tabular_presets import TabularAutoML
-from lightautoml.tasks import Task
-from sklearn.model_selection import train_test_split
-from sklearn.metrics import mean_squared_error
-
-# Load the training data from 'heart.csv'
-data = pd.read_csv('heart.csv')
-
-# Separate features (X) and target variable (y)
-X = data.drop(columns=['target'])
-y = data['target']
-
-# Split the data into training and testing sets
-X_train, X_test, y_train, y_test = train_test_split(
-    X, y, test_size=0.2, random_state=42)
-
-# Define the task and the metric
-task = Task('binary')  # binary classification
-metric = 'roc_auc'  # use ROC AUC as the metric for binary classification tasks
-
-# Create an instance of TabularAutoML
-automl = TabularAutoML(task=task, timeout=600,
-                       cpu_limit=4, reader_params={'n_jobs': 4})
-
-# Fit the model and make predictions on the test data
-predictions = automl.fit_predict(X_train, y_train, X_test)
-
-# Calculate the mean squared error
-mse = mean_squared_error(y_test, predictions.data[:, 0])
-print(f'Mean Squared Error: {mse}')
-
-# Calculate the accuracy
-accuracy = (predictions.data[:, 0] > 0.5).mean()
-print(f'Accuracy: {accuracy}')
-
-# Save the model
-automl.model.save('model.pkl')

### 2024-06-19 benchmarks/MLJAR/jar.py

@@ -1,19 +1,0 @@
-import pandas as pd
-from supervised import AutoML
-
-# Load the dataset
-data = pd.read_csv('heart.csv')
-
-# Separate features (X) and target variable (y)
-X = data.drop(columns=['target'])
-y = data['target']
-
-# Initialize AutoML
-automl = AutoML()
-
-# Train the model
-automl.fit(X, y)
-
-# Evaluate the model (optional)
-score = automl.score(X, y)
-print("Model Score:", score)

### 2024-06-19 benchmarks/TPOT/pot.py

@@ -1,32 +1,0 @@
-import joblib
-from tpot import TPOTClassifier
-from sklearn.model_selection import train_test_split
-import pandas as pd
-import time
-
-time_start = time.time()
-
-data = pd.read_csv('../../benchmark_datasets/heart2.csv')
-
-X = data.drop(columns=['HeartDisease'])
-y = data['HeartDisease']
-
-X_train, X_test, y_train, y_test = train_test_split(
-    X, y, test_size=0.2, random_state=42)
-
-tpot = TPOTClassifier(generations=50, population_size=20,
-                      verbosity=2, random_state=42)
-
-tpot.fit(X_train, y_train)
-
-print("Test Accuracy:", tpot.score(X_test, y_test))
-
-tpot.export('tpot_heart_pipeline.py')
-
-# save model
-joblib.dump(tpot.fitted_pipeline_, 'tpot_heart_model.pkl')
-
-time_end = time.time()
-
-time_total = time_end - time_start
-print("Time taken: ", time_total)

### 2024-06-19 benchmarks/TPOT/tpot_heart_pipeline.py

@@ -1,19 +1,0 @@
-import numpy as np
-import pandas as pd
-from sklearn.ensemble import GradientBoostingClassifier
-from sklearn.model_selection import train_test_split
-
-# NOTE: Make sure that the outcome column is labeled 'target' in the data file
-tpot_data = pd.read_csv('PATH/TO/DATA/FILE', sep='COLUMN_SEPARATOR', dtype=np.float64)
-features = tpot_data.drop('target', axis=1)
-training_features, testing_features, training_target, testing_target = \
-            train_test_split(features, tpot_data['target'], random_state=42)
-
-# Average CV score on the training set was: 0.9612903225806452
-exported_pipeline = GradientBoostingClassifier(learning_rate=0.5, max_depth=6, max_features=0.6000000000000001, min_samples_leaf=10, min_samples_split=8, n_estimators=100, subsample=0.8)
-# Fix random state in exported estimator
-if hasattr(exported_pipeline, 'random_state'):
-    setattr(exported_pipeline, 'random_state', 42)
-
-exported_pipeline.fit(training_features, training_target)
-results = exported_pipeline.predict(testing_features)

### 2024-06-19 example.py

@@ -2,22 +2,28 @@ from SMEML.SMEML import SMEML
 from sklearn.model_selection import train_test_split
 import pandas as pd
 import time
+import re
 
 if __name__ == "__main__":
     time_start = time.time()
     # load the dataset
     df = pd.read_csv('./benchmark_datasets/heart2.csv')
 
+    df = df.rename(columns = lambda x:re.sub('[^A-Za-z0-9_]+', '', x))
+
+    # replace No, borderline diabetes with borderline diabetes
+    df['Diabetic'] = df['Diabetic'].replace('No, borderline diabetes', 'borderline diabetes')
+
     X = df.drop('HeartDisease', axis=1)
     y = df['HeartDisease']
 
 # label encoding
-# y = y.map({'ckd': 1, 'notckd': 0})
+    y = y.map({'Yes': 1, 'No': 0})
 
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-    smeml = SMEML(iterations=10, mode="dumb")
+    smeml = SMEML(iterations=1, mode="dumb")
 # train the model
     smeml.train(X, y)
     time_end = time.time()

### 2024-06-19 SMEML/SMEML.py
update

@@ -97,9 +97,6 @@ class SMEML:
         if self.mode == "dumb":
             self.dumbmode()
 
-        self.generate_report()
-        self.save_final_model()
-
     def SMEmodel(self):
         attributes = self.get_dataset_attributes()
 
@@ -155,10 +152,9 @@ class SMEML:
 
         print("stacking classifier accuracy: ", accuracy)
 
-        self.best_model = (stacking_classifier, accuracy)
-
     def dumbmode(self):
         # train all models
+        models = []
         for i in range(len(classifiers)):
             model = classifiers[i]
             model_name = classifier_names[i]
@@ -182,12 +178,15 @@ class SMEML:
                 optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
 
                 accuracy = optimizer.score(self.X_test, self.y_test)
-
+                models.append((model_name, accuracy))
                 print("Model: ", model_name, " accuracy: ", accuracy)
             except Exception as e:
                 print("Error training model: ", model_name)
                 print(e)
                 continue
+        
+        models = sorted(models, key=lambda x: x[1], reverse=True)
+        print("Top models: ", models[:3])
 
     def train_thread(self, model, model_name, return_dict):
         print("Training model: ", model_name)
@@ -344,32 +343,3 @@ class SMEML:
             verbose_feature_names_out=False).set_output(transform='pandas')
 
         self.X = preprocessor.fit_transform(self.X)
-
-    def generate_report(self):
-        lines = []
-        lines.append("Dataset information")
-
-        print()
-
-        for key, value in self.attributes.items():
-            lines.append(f"{key}: {value}")
-
-        print()
-
-        lines.append("Top 10 classifiers predicted by SMEML")
-
-        for index, model in enumerate(self.model_accuracies):
-            lines.append("Model " + str(index) + ": " + str(model[0]) +
-                         " with accuracy: " + str(model[1]))
-
-        lines.append("Best model" + str(self.best_model[0]) +
-                     " with accuracy average: " +
-                     str(self.best_model[1]))
-
-        # save the report
-        with open('report.txt', 'w') as f:
-            for line in lines:
-                f.write("%s\n" % line)
-
-    def save_final_model(self):
-        pkl.dump(self.best_model[0], open('best_model.pkl', 'wb'))

### 2024-06-19 SMEML/SMEML.py
update

@@ -191,17 +191,30 @@ class SMEML:
     def train_thread(self, model, model_name, return_dict):
         print("Training model: ", model_name)
 
-        study = optuna.create_study(direction='maximize', study_name=model_name)
-        study.optimize(partial(self.objective, model=model, model_name=model_name), n_trials=self.iterations)
+        # check if the dataset is too large for the model
+        if size_limits.get(model_name) is not None and self.X.shape[0] * self.X.shape[1] > size_limits[model_name]:
+            return
+        
+        try:
+            optimizer = BayesSearchCV(
+                model,
+                param_grids[model_name],
+                n_iter=self.iterations,
+                n_jobs=-1,
+                verbose=0,
+                error_score=0,
+                cv=3
+            )
 
-        estimator = model.set_params(**study.best_params)
-
-        estimator.fit(self.X_train, self.y_train)
-
-        accuracy = estimator.score(self.X_test, self.y_test)
+            optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
+            accuracy = optimizer.score(self.X_test, self.y_test)
+        except Exception as e:
+            print("Error training model: ", model_name)
+            print(e)
+            return
 
         return_dict[model_name + '_accuracy'] = accuracy
-        return_dict[model_name + '_model'] = estimator
+        return_dict[model_name + '_model'] = optimizer.best_estimator_ 
 
     def bayes_cv_callback(self, res, model_name):
         self.progress_bars[model_name].update()

### 2024-06-19 SMEML/SMEML.py
update

@@ -206,6 +206,7 @@ class SMEML:
                 cv=3
             )
 
+            self.progress_bars[model_name] = tqdm(total=self.iterations, desc="Optimizing " + model_name)
             optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
             accuracy = optimizer.score(self.X_test, self.y_test)
         except Exception as e:

### 2024-06-19 example.py

@@ -23,7 +23,7 @@ if __name__ == "__main__":
 # create an instance of the SMEML class
 # X and y are the features and target variable
 # respectively
-    smeml = SMEML(iterations=1, mode="dumb")
+    smeml = SMEML(iterations=1, mode="SME")
 # train the model
     smeml.train(X, y)
     time_end = time.time()

### 2024-06-19 SMEML/SMEML.py
remove example.py

@@ -3,7 +3,7 @@
 import platform
 if platform.machine() == 'x86_64':
     from sklearnex import patch_sklearn
-    patch_sklearn()
+    # patch_sklearn()
 
 import pickle as pkl
 import numpy as np

### 2024-06-19 example.py

@@ -1,30 +1,0 @@
-from SMEML.SMEML import SMEML
-from sklearn.model_selection import train_test_split
-import pandas as pd
-import time
-import re
-
-if __name__ == "__main__":
-    time_start = time.time()
-    # load the dataset
-    df = pd.read_csv('./benchmark_datasets/heart2.csv')
-
-    df = df.rename(columns = lambda x:re.sub('[^A-Za-z0-9_]+', '', x))
-
-    # replace No, borderline diabetes with borderline diabetes
-    df['Diabetic'] = df['Diabetic'].replace('No, borderline diabetes', 'borderline diabetes')
-
-    X = df.drop('HeartDisease', axis=1)
-    y = df['HeartDisease']
-
-# label encoding
-    y = y.map({'Yes': 1, 'No': 0})
-
-# create an instance of the SMEML class
-# X and y are the features and target variable
-# respectively
-    smeml = SMEML(iterations=1, mode="SME")
-# train the model
-    smeml.train(X, y)
-    time_end = time.time()
-    print('Time taken to train the model: ', time_end - time_start)

### 2024-06-19 SMEML/SMEML.py
chronic-kidney-exp-code

@@ -81,7 +81,6 @@ class SMEML:
         self.y = None
         self.mode = mode
         self.iterations = iterations
-        self.progress_bars = {}
 
     def train(self, X, y):
         self.X = X
@@ -174,10 +173,10 @@ class SMEML:
                     error_score=0
                 )
 
-                self.progress_bars[model_name] = tqdm(total=self.iterations, desc="Optimizing " + model_name)
                 optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
 
                 accuracy = optimizer.score(self.X_test, self.y_test)
+                print("Model: ", model_name, " accuracy: ", accuracy)
                 models.append((model_name, accuracy))
                 print("Model: ", model_name, " accuracy: ", accuracy)
             except Exception as e:
@@ -206,9 +205,9 @@ class SMEML:
                 cv=3
             )
 
-            self.progress_bars[model_name] = tqdm(total=self.iterations, desc="Optimizing " + model_name)
             optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
             accuracy = optimizer.score(self.X_test, self.y_test)
+            print("Model: ", model_name, " accuracy: ", accuracy)
         except Exception as e:
             print("Error training model: ", model_name)
             print(e)
@@ -216,9 +215,6 @@ class SMEML:
 
         return_dict[model_name + '_accuracy'] = accuracy
         return_dict[model_name + '_model'] = optimizer.best_estimator_ 
-
-    def bayes_cv_callback(self, res, model_name):
-        self.progress_bars[model_name].update()
 
     def get_dataset_attributes(self):
         attributes = {}

### 2024-06-19 benchmarks/chronic-kidney-disease-dataset/dumb_exp.py

@@ -1,0 +1,29 @@
+import sys, os
+sys.path.append(os.path.abspath(os.path.join('..', '..')))
+print(sys.path)
+# import SMEML
+from SMEML.SMEML import SMEML
+import pandas as pd
+import time
+
+time_start = time.time()
+
+# Load the dataset
+data = pd.read_csv('chronic-kidney-disease-dataset.csv')
+
+# Define the target column
+target = data['classification']
+target = target.replace('ckd', 1)
+target = target.replace('notckd', 0)
+data = data.drop(columns=['classification'])
+
+if __name__ == '__main__':
+    # Initialize the SMEML object
+    smeml = SMEML(iterations=32, mode='dumb')
+
+    # Run the smart experiment
+    smeml.train(data, target)
+
+time_end = time.time()
+
+print('Time elapsed: ', time_end - time_start)

### 2024-06-19 benchmarks/chronic-kidney-disease-dataset/smart_exp.py

@@ -1,0 +1,29 @@
+import sys, os
+sys.path.append(os.path.abspath(os.path.join('..', '..')))
+print(sys.path)
+# import SMEML
+from SMEML.SMEML import SMEML
+import pandas as pd
+import time
+
+time_start = time.time()
+
+# Load the dataset
+data = pd.read_csv('chronic-kidney-disease-dataset.csv')
+
+# Define the target column
+target = data['classification']
+target = target.replace('ckd', 1)
+target = target.replace('notckd', 0)
+data = data.drop(columns=['classification'])
+
+if __name__ == '__main__':
+    # Initialize the SMEML object
+    smeml = SMEML(iterations=32, mode='SME')
+
+    # Run the smart experiment
+    smeml.train(data, target)
+
+time_end = time.time()
+
+print('Time elapsed: ', time_end - time_start)

### 2024-06-19 SMEML/SMEML.py
chronic-kidney-exp-code

@@ -33,7 +33,8 @@ logger.addHandler(handler)
 
 warnings_to_ignore = [
     "FutureWarning",
-    "InconsistentVersionWarning"
+    "InconsistentVersionWarning",
+    "ConvergenceWarning",
 ]
 
 # Set rule to ignore warnings
@@ -173,12 +174,11 @@ class SMEML:
                     error_score=0
                 )
 
-                optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
+                optimizer.fit(self.X_train, self.y_train)
 
                 accuracy = optimizer.score(self.X_test, self.y_test)
                 print("Model: ", model_name, " accuracy: ", accuracy)
                 models.append((model_name, accuracy))
-                print("Model: ", model_name, " accuracy: ", accuracy)
             except Exception as e:
                 print("Error training model: ", model_name)
                 print(e)
@@ -205,7 +205,7 @@ class SMEML:
                 cv=3
             )
 
-            optimizer.fit(self.X_train, self.y_train, callback=partial(self.bayes_cv_callback, model_name=model_name))
+            optimizer.fit(self.X_train, self.y_train)
             accuracy = optimizer.score(self.X_test, self.y_test)
             print("Model: ", model_name, " accuracy: ", accuracy)
         except Exception as e:

### 2024-06-19 paper/paper.tex
experiment design and basic table

--- 2024-06-16 paper.tex
@@
 We run bayseian optimization on the top ten models to get the best hyperparamters for each model.
-Each model's optimization is run in its own process and in parralell.
+We used  Each model's optimization is run in its own process and in parralell.
 We select the top models that have significantly better performance than other models.
@@
 
-\subsection{Experiments}
+\section{Experiments}
+\subsection{Experiment Design}
+To evaluate our framework, we choose 7 different datasets of diverse size.
+We ran SMEML on each dataset for 32 iterations of tuning.
+We compared this against a "dumb" mode which simply runs every model on the dataset.
+We used the accuracy and time to train as our metrics.
 
+All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.
+
+\subsection{Results}
+\begin{table}
+  \caption{Experiment Results}
+  \label{model-options-table}
+  \centering
+  \begin{tabular}{llllll}
+    \toprule
+    % group 2, 3 as multicolumn and 4, 5 as multicolumn
+    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train} & Size (RxC)\\
+    \cmidrule(lr){2-3} \cmidrule(lr){4-5}
+    & SMEML & Dumb & SMEML & Dumb \\
+    \midrule
+    \bottomrule
+  \end{tabular}
+\end{table}
 \section{Discussion}

### 2024-06-19 SMEML/SMEML.py
dumb chronic kidney

@@ -3,7 +3,7 @@
 import platform
 if platform.machine() == 'x86_64':
     from sklearnex import patch_sklearn
-    # patch_sklearn()
+    patch_sklearn()
 
 import pickle as pkl
 import numpy as np
@@ -170,7 +170,7 @@ class SMEML:
                     param_grids[model_name],
                     n_iter=self.iterations,
                     n_jobs=-1,
-                    verbose=0,
+                    verbose=3,
                     error_score=0
                 )
 
@@ -200,7 +200,7 @@ class SMEML:
                 param_grids[model_name],
                 n_iter=self.iterations,
                 n_jobs=-1,
-                verbose=0,
+                verbose=3,
                 error_score=0,
                 cv=3
             )

### 2024-06-19 benchmarks/brain-stroke-prediction-dataset/dumb_exp.py
brain stroke

@@ -1,0 +1,27 @@
+import sys, os
+sys.path.append(os.path.abspath(os.path.join('..', '..')))
+print(sys.path)
+# import SMEML
+from SMEML.SMEML import SMEML
+import pandas as pd
+import time
+
+time_start = time.time()
+
+# Load the dataset
+data = pd.read_csv('brain-stroke-prediction-dataset.csv')
+
+# Define the target column
+target = data['stroke']
+data = data.drop(columns=['stroke'])
+
+if __name__ == '__main__':
+    # Initialize the SMEML object
+    smeml = SMEML(iterations=32, mode='dumb')
+
+    # Run the smart experiment
+    smeml.train(data, target)
+
+time_end = time.time()
+
+print('Time elapsed: ', time_end - time_start)

### 2024-06-19 benchmarks/brain-stroke-prediction-dataset/smart_exp.py

@@ -1,0 +1,27 @@
+import sys, os
+sys.path.append(os.path.abspath(os.path.join('..', '..')))
+print(sys.path)
+# import SMEML
+from SMEML.SMEML import SMEML
+import pandas as pd
+import time
+
+time_start = time.time()
+
+# Load the dataset
+data = pd.read_csv('brain-stroke-prediction-dataset.csv')
+
+# Define the target column
+target = data['stroke']
+data = data.drop(columns=['stroke'])
+
+if __name__ == '__main__':
+    # Initialize the SMEML object
+    smeml = SMEML(iterations=32, mode='SME')
+
+    # Run the smart experiment
+    smeml.train(data, target)
+
+time_end = time.time()
+
+print('Time elapsed: ', time_end - time_start)

### 2024-06-20 paper/paper.tex
experiments

@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
+We performed a literature review of existing AutoML papers and conducted a survey on six popluar AutoML frameworks.
 Many of these frameworks optimize a form of model selection, however, they all require most models to be run and evaluated.
 We propose a novel framework that automatically eliminates models that are unlikely to be performant by training a Boosting Model on hundreds of kaggle datasets.
-Out of the 30 model options, our framework can predict a top five model within its top eight 80\% of the time.
+Our framework, SME, demonstrates the ability to generate a model with near equal accuracy to a "dumb" model that runs every model on every dataset, but in a fraction of the time.
 \end{abstract}
@@
 Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
-By testing our new framework against these four in evaluating medical data, we hoped to delineate key weaknesses and strengths in our own design.
 
@@
 We run bayseian optimization on the top ten models to get the best hyperparamters for each model.
-We used  Each model's optimization is run in its own process and in parralell.
 We select the top models that have significantly better performance than other models.
@@
 To evaluate our framework, we choose 7 different datasets of diverse size.
-We ran SMEML on each dataset for 32 iterations of tuning.
+We ran SMEML on each dataset for 20 iterations of tuning.
 We compared this against a "dumb" mode which simply runs every model on the dataset.
@@
     % group 2, 3 as multicolumn and 4, 5 as multicolumn
-    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train} & Size (RxC)\\
+    Dataset & \multicolumn{2}{c}{Accuracy} & \multicolumn{2}{c}{Time to Train (sec)} & Size (RxC)\\
     \cmidrule(lr){2-3} \cmidrule(lr){4-5}
@@
     \midrule
+    Chronic Kidney Disease Dataset & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
+    Brain Stroke Prediction Dataset & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
+    Lung Cancer Prediction & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
+    Pima Indians Diabetes Dataset & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
+    Eye State Classification & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
     \bottomrule

### 2024-06-20 SMEML/SMEML.py

@@ -111,30 +111,33 @@ class SMEML:
 
         top = np.argsort(results[0])[-8:]
 
-        model_threads = []
-        manager = multiprocessing.Manager()
-        return_dict = manager.dict()
-        for i in top:
-            thread = multiprocessing.Process(name=classifier_names[i],
-                target=self.train_thread, args=(classifiers[i], classifier_names[i], return_dict,))
-            model_threads.append(thread)
-
-        for thread in model_threads:
-            thread.start()
-
-        # wait for all threads to finish
-        for thread in model_threads:
-            thread.join()
-        
         self.model_accuracies = []
         self.models = {}
 
-        # loop through return dict and get the models and accuracies
-        for key, value in return_dict.items():
-            if 'accuracy' in key:
-                self.model_accuracies.append((key.replace('_accuracy', ''), value))
-            else:
-                self.models[key.replace('_model', '')] = value
+        for i in top:
+            print("Training model: ", classifier_names[i])
+            try:
+                optimizer = BayesSearchCV(
+                    classifiers[i],
+                    param_grids[classifier_names[i]],
+                    n_iter=self.iterations,
+                    n_jobs=-1,
+                    verbose=3,
+                    cv=3,
+                    error_score=0
+                )
+            
+                optimizer.fit(self.X_train, self.y_train)
+
+                accuracy = optimizer.score(self.X_test, self.y_test)
+                print("Model: ", classifier_names[i], " accuracy: ", accuracy)
+
+                self.model_accuracies.append((classifier_names[i], accuracy))
+                self.models[classifier_names[i]] = optimizer.best_estimator_
+            except Exception as e:
+                print("Error training model: ", classifier_names[i])
+                print(e)
+                continue
 
         self.model_accuracies = sorted(self.model_accuracies, key=lambda x: x[1], reverse=True)
         # take top 3 models
@@ -151,6 +154,13 @@ class SMEML:
         accuracy = stacking_classifier.score(self.X_test, self.y_test)
 
         print("stacking classifier accuracy: ", accuracy)
+        
+        # check if stacking classifier is better than the top model
+        if accuracy > self.top_models_accuracies[0][1]:
+            print("Stacking classifier is better than the top model")
+        else:
+            print("Stacking classifier is not better than the top model")
+            print("Top model: ", self.top_models_accuracies[0][0], " accuracy: ", self.top_models_accuracies[0][1])
 
     def dumbmode(self):
[…]

### 2024-06-20 benchmarks/brain-stroke-prediction-dataset/dumb_exp.py

@@ -1,10 +1,10 @@
-import sys, os
+import os
+import sys
 sys.path.append(os.path.abspath(os.path.join('..', '..')))
-print(sys.path)
-# import SMEML
 from SMEML.SMEML import SMEML
 import pandas as pd
 import time
+# import SMEML
 
 time_start = time.time()
 
@@ -17,11 +17,11 @@ data = data.drop(columns=['stroke'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object
-    smeml = SMEML(iterations=32, mode='dumb')
+    smeml = SMEML(iterations=20, mode='dumb')
 
     # Run the smart experiment
     smeml.train(data, target)
 
-time_end = time.time()
+    time_end = time.time()
 
-print('Time elapsed: ', time_end - time_start)
+    print('Time elapsed: ', time_end - time_start)

### 2024-06-20 benchmarks/chronic-kidney-disease-dataset/dumb_exp.py

@@ -19,7 +19,7 @@ data = data.drop(columns=['classification'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object
-    smeml = SMEML(iterations=32, mode='dumb')
+    smeml = SMEML(iterations=20, mode='dumb')
 
     # Run the smart experiment
     smeml.train(data, target)

### 2024-06-20 benchmarks/eye-state-classification-eeg-dataset/dumb_exp.py

@@ -1,24 +1,23 @@
 import os
 import sys
 sys.path.append(os.path.abspath(os.path.join('..', '..')))
-import time
-import pandas as pd
 from SMEML.SMEML import SMEML
-print(sys.path)
+import pandas as pd
+import time
 # import SMEML
 
 time_start = time.time()
 
 # Load the dataset
-data = pd.read_csv('brain-stroke-prediction-dataset.csv')
+data = pd.read_csv('eye-state-classification-eeg-dataset.csv')
 
 # Define the target column
-target = data['stroke']
-data = data.drop(columns=['stroke'])
+target = data['eyeDetection']
+data = data.drop(columns=['eyeDetection'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object
-    smeml = SMEML(iterations=20, mode='SME')
+    smeml = SMEML(iterations=20, mode='dumb')
 
     # Run the smart experiment
     smeml.train(data, target)

### 2024-06-20 benchmarks/eye-state-classification-eeg-dataset/smart_exp.py

@@ -1,21 +1,19 @@
-import sys, os
+import os
+import sys
 sys.path.append(os.path.abspath(os.path.join('..', '..')))
-print(sys.path)
-# import SMEML
 from SMEML.SMEML import SMEML
 import pandas as pd
 import time
+# import SMEML
 
 time_start = time.time()
 
 # Load the dataset
-data = pd.read_csv('chronic-kidney-disease-dataset.csv')
+data = pd.read_csv('eye-state-classification-eeg-dataset.csv')
 
 # Define the target column
-target = data['classification']
-target = target.replace('ckd', 1)
-target = target.replace('notckd', 0)
-data = data.drop(columns=['classification'])
+target = data['eyeDetection']
+data = data.drop(columns=['eyeDetection'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object
@@ -24,6 +22,6 @@ if __name__ == '__main__':
     # Run the smart experiment
     smeml.train(data, target)
 
-time_end = time.time()
+    time_end = time.time()
 
-print('Time elapsed: ', time_end - time_start)
+    print('Time elapsed: ', time_end - time_start)

### 2024-06-20 benchmarks/lung-cancer-prediction/dumb_exp.py

@@ -9,17 +9,17 @@ import time
 time_start = time.time()
 
 # Load the dataset
-data = pd.read_csv('chronic-kidney-disease-dataset.csv')
+data = pd.read_csv('lung-cancer-prediction.csv')
 
 # Define the target column
-target = data['classification']
-target = target.replace('ckd', 1)
-target = target.replace('notckd', 0)
-data = data.drop(columns=['classification'])
+target = data['LUNG_CANCER']
+target = target.replace('YES', 1)
+target = target.replace('NO', 0)
+data = data.drop(columns=['LUNG_CANCER'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object
-    smeml = SMEML(iterations=20, mode='SME')
+    smeml = SMEML(iterations=20, mode='dumb')
 
     # Run the smart experiment
     smeml.train(data, target)

### 2024-06-20 benchmarks/lung-cancer-prediction/smart_exp.py

@@ -9,13 +9,13 @@ import time
 time_start = time.time()
 
 # Load the dataset
-data = pd.read_csv('chronic-kidney-disease-dataset.csv')
+data = pd.read_csv('lung-cancer-prediction.csv')
 
 # Define the target column
-target = data['classification']
-target = target.replace('ckd', 1)
-target = target.replace('notckd', 0)
-data = data.drop(columns=['classification'])
+target = data['LUNG_CANCER']
+target = target.replace('YES', 1)
+target = target.replace('NO', 0)
+data = data.drop(columns=['LUNG_CANCER'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object

### 2024-06-20 benchmarks/pima-indians-diabetes-database/dumb_exp.py

@@ -9,21 +9,19 @@ import time
 time_start = time.time()
 
 # Load the dataset
-data = pd.read_csv('chronic-kidney-disease-dataset.csv')
+data = pd.read_csv('pima-indians-diabetes-database.csv')
 
 # Define the target column
-target = data['classification']
-target = target.replace('ckd', 1)
-target = target.replace('notckd', 0)
-data = data.drop(columns=['classification'])
+target = data['Outcome']
+data = data.drop(columns=['Outcome'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object
-    smeml = SMEML(iterations=20, mode='SME')
+    smeml = SMEML(iterations=20, mode='dumb')
 
     # Run the smart experiment
     smeml.train(data, target)
 
-time_end = time.time()
+    time_end = time.time()
 
-print('Time elapsed: ', time_end - time_start)
+    print('Time elapsed: ', time_end - time_start)

### 2024-06-20 benchmarks/pima-indians-diabetes-database/smart_exp.py

@@ -9,13 +9,11 @@ import time
 time_start = time.time()
 
 # Load the dataset
-data = pd.read_csv('chronic-kidney-disease-dataset.csv')
+data = pd.read_csv('pima-indians-diabetes-database.csv')
 
 # Define the target column
-target = data['classification']
-target = target.replace('ckd', 1)
-target = target.replace('notckd', 0)
-data = data.drop(columns=['classification'])
+target = data['Outcome']
+data = data.drop(columns=['Outcome'])
 
 if __name__ == '__main__':
     # Initialize the SMEML object
@@ -24,6 +22,6 @@ if __name__ == '__main__':
     # Run the smart experiment
     smeml.train(data, target)
 
-time_end = time.time()
+    time_end = time.time()
 
-print('Time elapsed: ', time_end - time_start)
+    print('Time elapsed: ', time_end - time_start)

### 2024-06-21 paper/paper.tex
some updates
final results

@@
 \author{%
-  Eric Su Zhang\thanks{Use footnote for providing further information
-    about author (webpage, alternative address)---\emph{not} for acknowledging
-    funding agencies.} \\
+  Eric Su Zhang$^1$ \\
   St. Mark's School of Texas\\
@@
   \And
-  Benjamin Standefer \\
+  Benjamin Standefer$^2$ \\
   St. Mark's School of Texas \\
@@
 We performed a literature review of existing AutoML papers and conducted a survey on six popluar AutoML frameworks.
-Many of these frameworks optimize a form of model selection, however, they all require most models to be run and evaluated.
-We propose a novel framework that automatically eliminates models that are unlikely to be performant by training a Boosting Model on hundreds of kaggle datasets.
-Our framework, SME, demonstrates the ability to generate a model with near equal accuracy to a "dumb" model that runs every model on every dataset, but in a fraction of the time.
+Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated.
+We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant so unnecessary time is not spent training these models.
+SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" model that runs every model on every dataset, but in a fraction of the time.
 \end{abstract}
@@
 \centering
-\fbox{\includegraphics[width=\textwidth]{smeml-flowchart.png}}
+\includegraphics[width=\textwidth]{smeml-flowchart.png}
 \caption{SMEML Process}
@@
 \subsection{Experiment Design}
-To evaluate our framework, we choose 7 different datasets of diverse size.
+To evaluate our framework, we choose 5 different datasets of diverse size.
 We ran SMEML on each dataset for 20 iterations of tuning.
@@
     \midrule
+    Lung Cancer Prediction & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
     Chronic Kidney Disease Dataset & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
+    Pima Indians Diabetes Dataset & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
     Brain Stroke Prediction Dataset & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
-    Lung Cancer Prediction & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
-    Pima Indians Diabetes Dataset & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
+    Stroke Prediction Dataset & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
     Eye State Classification & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 

### 2024-06-21 SMEML/SMEML.py

@@ -115,6 +115,9 @@ class SMEML:
         self.models = {}
 
         for i in top:
+            # check if the dataset is too large for the model
+            if size_limits.get(classifier_names[i]) is not None and self.X.shape[0] * self.X.shape[1] > size_limits[classifier_names[i]]:
+                continue 
             print("Training model: ", classifier_names[i])
             try:
                 optimizer = BayesSearchCV(

### 2024-06-21 benchmarks/stroke-prediction-dataset/dumb_exp.py

@@ -1,0 +1,27 @@
+import sys, os
+sys.path.append(os.path.abspath(os.path.join('..', '..')))
+print(sys.path)
+# import SMEML
+from SMEML.SMEML import SMEML
+import pandas as pd
+import time
+
+time_start = time.time()
+
+# Load the dataset
+data = pd.read_csv('stroke-prediction-dataset.csv')
+
+# Define the target column
+target = data['stroke']
+data = data.drop(columns=['stroke'])
+
+if __name__ == '__main__':
+    # Initialize the SMEML object
+    smeml = SMEML(iterations=20, mode='dumb')
+
+    # Run the smart experiment
+    smeml.train(data, target)
+
+    time_end = time.time()
+
+    print('Time elapsed: ', time_end - time_start)

### 2024-06-21 benchmarks/stroke-prediction-dataset/smart_exp.py

@@ -1,0 +1,27 @@
+import sys, os
+sys.path.append(os.path.abspath(os.path.join('..', '..')))
+print(sys.path)
+# import SMEML
+from SMEML.SMEML import SMEML
+import pandas as pd
+import time
+
+time_start = time.time()
+
+# Load the dataset
+data = pd.read_csv('stroke-prediction-dataset.csv')
+
+# Define the target column
+target = data['stroke']
+data = data.drop(columns=['stroke'])
+
+if __name__ == '__main__':
+    # Initialize the SMEML object
+    smeml = SMEML(iterations=20, mode='SME')
+
+    # Run the smart experiment
+    smeml.train(data, target)
+
+    time_end = time.time()
+
+    print('Time elapsed: ', time_end - time_start)

### 2024-06-21 paper/paper.tex
Update paper.tex

@@
     \midrule
-    H2O AutoML & Easy & 10 & Basic & Yes & Auto & SHAP & High\\
+    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
     TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
-    MLJAR & Easy & 10 & Advanced & Yes & Auto & Basic & High\\
-    FLAML & Easy & 10 & Limited & Yes & Auto & SHAP & Low-Moderate\\
-    LightAutoML & Easy & 10 & Advanced & Yes & Auto & Basic & Moderate\\
-    GAMA & Hard & 10 & Basic & Yes & Auto & SHAP & Moderate\\
+    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
+    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
+    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
     \bottomrule
@@
   \captionsetup{font=footnotesize}
-  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, Algs: Algorithms, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
+  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, Algs: Algorithm Types, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
 \end{table}
@@
 To implement this model elimination process, we trained a boosting model on 268 kaggle datasets.
-We choose datasets that were medically related and focused our approach to binary classification.
-We extracted the attributes in Table 2 from each dataset, this is the input for the boosting model.
+We chose datasets that were medically related and focused our approach on binary classification.
+We extracted the attributes in Table 2 from each dataset: this is the input for the boosting model.
 We then ran a "dumb" framework that trained every model on each dataset.
 The accuracy of every model is ranked and every model is treated as a label with its value being its rank.
-Then we trained a multilabel regression to predict the rank of each model giving the extracted attributes.
+Then we trained a multilabel regression to predict the rank of each model, giving the extracted attributes.
 We produced a median spearman correlation of 0.7301 between the predicted rank and the actual rank and a median p-value of 1.032e-05.
@@
 It feeds these attributes into the boosting model to get the predicted rank of each model.
-Since we have determined that we can predict a top two model within the predicted top ten quite confidently we can eliminate the bottom 18 models from the list.
-We run bayseian optimization on the top ten models to get the best hyperparamters for each model.
+Since we have determined that we can predict a top two model within the predicted top ten quite confidently, we can eliminate the bottom 18 models from the list.
+We run Bayseian optimization on the top ten models to get the best hyperparamters for each model.
 We select the top models that have significantly better performance than other models.
@@
 \end{table}
+
+After running the trials, several observations were readily apparent.
+First, accurcy did not change for 4 of the 6 trials.
+The other two trials on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively.
+Training time, however, favored SMEML in every trial.
+SMEML outperformed the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset.
+Relative to the dummy's performance, a percent decrease in time to run for SMEML of at least 46.78\% could be seen, with a decrease of up to 69.22\% observerd as well.
+SMEML's worst performance by percent decrease was also the performance in which it returned perfect accuracy.
 \section{Discussion}
+
+As evidenced by our experiment's results, SMEML manages to return comparable accuracy results compared to its dumb couterpart while more than splitting the run time in half in the majority of trials.
+Its performance is not limited by the size of the dataset, and it in fact returned its first, third, and fourth best percentage-based run times on the 'large' dataset trials (those exceeding 1000 rows).
+This is important in third world medicine where time is of the essence and there is a constant influx of new patient data.
+Further research should be done in incorporating this innovation into a full-fledged AutoML framework to expedite and improve the process further.
+A practical demonsration of this software's real-world application can be found on our SmartDx website.
 

### 2024-06-21 paper/paper.tex
Update paper.tex
change

@@
     \toprule
-    Framework & EOU & Algs & FE & TM & HPT & Inter & Custom\\
+    Framework & EOU & M & FE & TM & HPT & Inter & Custom\\
     \midrule
@@
   \captionsetup{font=footnotesize}
-  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, Algs: Algorithm Types, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
+  \caption*{\textbf{Abbreviations}: EOU: Ease of Use, M: \# of models evaluated by framework, FE: Feature Engineering, TM: Time Management, HPT: Hyper-Parameter Tuning, Inter: Interface, Custom: Customization}
 \end{table}

### 2024-06-21 paper/paper.tex
finish paper except for references

@@
 We used the accuracy and time to train as our metrics.
-
 All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.
@@
 
-After running the trials, several observations were readily apparent.
-First, accurcy did not change for 4 of the 6 trials.
-The other two trials on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively.
+After running the benchmark datasets, several observations were readily apparent.
+First, accurcy did not change for 4 of the 6 benchmarks.
+The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively.
 Training time, however, favored SMEML in every trial.
@@
 \section{Discussion}
-
-As evidenced by our experiment's results, SMEML manages to return comparable accuracy results compared to its dumb couterpart while more than splitting the run time in half in the majority of trials.
-Its performance is not limited by the size of the dataset, and it in fact returned its first, third, and fourth best percentage-based run times on the 'large' dataset trials (those exceeding 1000 rows).
+\subsection{Summary}
+As evidenced by our experiment's results, SMEML manages to return comparable accuracy results compared to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks.
+Its performance is not limited by the size of the dataset, and it in fact returned its first, third, and fourth best percentage-based run times on the 'large' dataset benchmarks (those exceeding 1000 rows).
 This is important in third world medicine where time is of the essence and there is a constant influx of new patient data.
@@
 A practical demonsration of this software's real-world application can be found on our SmartDx website.
-
+\subsection{Limitations}
+Our implementation of SMEML has limitations.
+These include a small training set due to lack of available datasets, finite computing power, time constraints, and a lack of access to paticular scientific literature.
+Our framework only improves on the model selection process and does not address the various other aspects of AutoML.
+Therefore, SMEML is not comparable to other full-featured AutoML frameworks.
+\subsection{Future Work}
+Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks on more datasets.
+Furthermore, we can examine other types of machine learning such as regression and multiclass-classification.
 \begin{ack}
-
+The authors would like to thank the St. Mark's School of Texas for supporting this research.
 \end{ack}

### 2024-06-21 paper/paper.tex
small change

@@
 \end{table}
-Table 1: Comparison of six AutoML frameworks based on commonmly evaluated criteria as well as more obscure features relevant to the medical diagnosis process
-
 We systematically reviewed and compared six different AutoML frameworks, comparing every feature relevant to medical implementation.

### 2024-06-22 paper/paper.tex
Update paper.tex

@@
 The development and optimization of these models is a time-consuming process involving statistical nuances and complex learning strategies.
-This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research.
+This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research [\1].
 
@@
 These countries have severe shortages of healthcare workers and limited tools for diagnosis.
-For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000.
-The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030.
+For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000 [\2].
+The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030 [\3].
 The use of AI in healthcare has been varied.
-Medical AI's typically automate repetitive tasks, making time consumption a primary concern.
+Medical AI's typically automate repetitive tasks, making time consumption a primary concern [\4].
 This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue.
@@
 Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected.
-However, these frameworks require that every model to be run to filter out.
+However, these frameworks require that every model to be run to filter out [\1].
 In theory, this means that much energy is spent training models that are unlikely to be selected.
@@
 \end{table}
-We systematically reviewed and compared six different AutoML frameworks, comparing every feature relevant to medical implementation.
+We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation [\5, \6, \7, \8, \9, \10, \11, \12, \13].
 Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
@@
 FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere.
-It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers.
-H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on Mean.
-In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour.
-H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users.
+It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [\11, \12].
+H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average.
+In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [\12].
+H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [\5, \6].
 MLJAR uses more advanced algorithms such as light gradient boosting and neural networks.
-It automatically deals with missing values and is known for its automated user interface.
+It automatically deals with missing values and is known for its automated user interface [\9, \10].
 TPOT uses genetic programming.
 It builds pipelines over multiple generations, which can be time consuming.
-It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users.
+It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [\7, \8].
 
@@
 When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best.
-For example, linear models tend to work better on datasets where there is a linear relationship between features.
+For example, linear models tend to work better on datasets where there is a linear relationship between features [\14].
 As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
@@
 \section*{References}
+[\1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.
+[\2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, vol. 5, no. 6, Oct. 2022, doi:10.1002/hsr2.893.
+[\3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.
+[\4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, vol. 8, no. 2, July 2021, pp. e188–94, doi:10.7861/fhj.2021-0095.
+[\5] LeDell, E., and S.
+Poirier.
+“H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf.
+[\6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) & XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.
+[\7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.
+[\8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.
+[\9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.
+[\10] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, vol. 12, no. 1, Nov. 2022, doi:10.1038/s41598-022-23327-1.
+[\11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.
+[\12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.
+[\13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.
+[\14] Akalin, Altuna.
+3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R.
+30 Sept.
+2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.
 

### 2024-06-22 paper/paper.tex
remove "

--- 2024-06-21 paper/paper.tex
@@
 The development and optimization of these models is a time-consuming process involving statistical nuances and complex learning strategies.
-This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research.
+This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research [1].
 
@@
 These countries have severe shortages of healthcare workers and limited tools for diagnosis.
-For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000.
-The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030.
+For example, Africa has 2.3 healthcare workers per 1000 individuals, while the Americas have 24.8 healthcare workers per 1000 [2].
+The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030 [3].
 The use of AI in healthcare has been varied.
-Medical AI's typically automate repetitive tasks, making time consumption a primary concern.
+Medical AI's typically automate repetitive tasks, making time consumption a primary concern [4].
 This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue.
@@
 Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected.
-However, these frameworks require that every model to be run to filter out.
+However, these frameworks require that every model to be run to filter out [1].
 In theory, this means that much energy is spent training models that are unlikely to be selected.
@@
 \end{table}
-We systematically reviewed and compared six different AutoML frameworks, comparing every feature relevant to medical implementation.
+We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation [5, 6, 7, 8, 9, 10, 11, 12, 13].
 Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
@@
 FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere.
-It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers.
-H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on Mean.
-In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour.
-H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users.
+It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [11, 12].
+H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average.
+In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [12].
+H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5, 6].
 MLJAR uses more advanced algorithms such as light gradient boosting and neural networks.
-It automatically deals with missing values and is known for its automated user interface.
+It automatically deals with missing values and is known for its automated user interface [9, 10].
 TPOT uses genetic programming.
 It builds pipelines over multiple generations, which can be time consuming.
-It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users.
+It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [7, 8].
 
@@
 When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best.
-For example, linear models tend to work better on datasets where there is a linear relationship between features.
+For example, linear models tend to work better on datasets where there is a linear relationship between features [14].
 As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
@@
 \section*{References}
-
 \medskip
@@
 
-% references here
-
+[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.
+[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, vol. 5, no. 6, Oct. 2022, doi:10.1002/hsr2.893.
+[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.
+[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, vol. 8, no. 2, July 2021, pp. e188–94, doi:10.7861/fhj.2021-0095.
+[5] LeDell, E., and S.
+Poirier.
+“H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, \url{www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.
+[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.
+[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.
+[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.
+[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.
+[10] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, vol. 12, no. 1, Nov. 2022, doi:10.1038/s41598-022-23327-1.
+[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.
+[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.
+[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.
+[14] Akalin, Altuna.
+3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R.
+30 Sept.
+2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.
 \end{document}

### 2024-06-22 paper/paper.tex
add spaces
Update paper.tex

@@
 \subsection{Experiment Design}
-To evaluate our framework, we choose 5 different datasets of diverse size.
+To evaluate our framework, we choose 5 different datasets of diverse size [/15, /16, /17, /18, /19, /20].
 We ran SMEML on each dataset for 20 iterations of tuning.
@@
 [1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.
+
 [2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, vol. 5, no. 6, Oct. 2022, doi:10.1002/hsr2.893.
+
 [3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.
+
 [4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, vol. 8, no. 2, July 2021, pp. e188–94, doi:10.7861/fhj.2021-0095.
+
 [5] LeDell, E., and S.
@@
 “H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, \url{www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.
+
 [6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.
+
 [7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.
+
 [8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.
+
 [9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.
+
 [10] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, vol. 12, no. 1, Nov. 2022, doi:10.1038/s41598-022-23327-1.
+
 [11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.
+
 [12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.
+
 [13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.
+
 [14] Akalin, Altuna.
@@
 2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.
+
+[15] Lung Cancer. 15 July 2022, www.kaggle.com/datasets/nancyalaswad90/lung-cancer.
+
+[16] Chronic KIdney Disease Dataset. 13 Apr. 2017, www.kaggle.com/datasets/mansoordaku/ckdisease.
+
+[17] Busekseolu. Diabetes Classification. 26 Nov. 2021, www.kaggle.com/code/busekseolu/diabetes-classification/input.
+
+[18] Mahendrasinghrajpoot. Brain Stroke Dataset. 21 Aug. 2022, www.kaggle.com/code/mahendrasinghrajpoot/brain-stroke-dataset/input.
+
+[19] Thomaskonstantin. Analyzing and Modeling Stroke Data. 6 July 2021, www.kaggle.com/code/thomaskonstantin/analyzing-and-modeling-stroke-data/input.
+
+[20] Robikscube. Eye State Prediction Dataset. 26 June 2022, www.kaggle.com/code/robikscube/eye-state-prediction-dataset/input?select=EEG_Eye_State_Classification.csv.
+
 \end{document}

### 2024-06-22 paper/paper.tex
switch to eight

@@
 We produced a median spearman correlation of 0.7301 between the predicted rank and the actual rank and a median p-value of 1.032e-05.
-Furthermore, we guarantee that we can predict a top two model within the predicted top ten 90.12\% of the time.
+Furthermore, we guarantee that we can predict a top two model within the predicted top eight 90.12\% of the time.
 
@@
 It feeds these attributes into the boosting model to get the predicted rank of each model.
-Since we have determined that we can predict a top two model within the predicted top ten quite confidently, we can eliminate the bottom 18 models from the list.
-We run Bayseian optimization on the top ten models to get the best hyperparamters for each model.
+Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 18 models from the list.
+We run Bayseian optimization on the top eight models to get the best hyperparamters for each model.
 We select the top models that have significantly better performance than other models.

### 2024-06-22 paper/paper.tex
urls

@@
 
-[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.
+[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, \url{arxiv.org/pdf/1908.00709}.
 
@@
 
-[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.
+[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, \url{iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1}.
 
@@
 
-[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.
+[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, \url{github.com/h2oai/h2o-3}.
 
-[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.
+[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, \url{arxiv.org/pdf/1601.07925}.
 
-[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.
+[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, \url{github.com/EpistasisLab/tpot}.
 
-[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.
+[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, \url{github.com/mljar/mljar-supervised}.
 
@@
 
-[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.
+[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, \url{arxiv.org/pdf/1911.04706}.
 
-[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.
+[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, \url{github.com/microsoft/FLAML}.
 
-[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.
+[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, \url{github.com/sb-ai-lab/LightAutoML}.
 
@@
 30 Sept.
-2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.
+2020, \url{compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.
 
-[15] Lung Cancer. 15 July 2022, www.kaggle.com/datasets/nancyalaswad90/lung-cancer.
+[15] Lung Cancer. 15 July 2022, \url{www.kaggle.com/datasets/nancyalaswad90/lung-cancer}.
 
-[16] Chronic KIdney Disease Dataset. 13 Apr. 2017, www.kaggle.com/datasets/mansoordaku/ckdisease.
+[16] Chronic KIdney Disease Dataset. 13 Apr. 2017, \url{www.kaggle.com/datasets/mansoordaku/ckdisease}.
 
-[17] Busekseolu. Diabetes Classification. 26 Nov. 2021, www.kaggle.com/code/busekseolu/diabetes-classification/input.
+[17] Busekseolu. Diabetes Classification. 26 Nov. 2021, \url{www.kaggle.com/code/busekseolu/diabetes-classification/input}.
 
-[18] Mahendrasinghrajpoot. Brain Stroke Dataset. 21 Aug. 2022, www.kaggle.com/code/mahendrasinghrajpoot/brain-stroke-dataset/input.
+[18] Mahendrasinghrajpoot. Brain Stroke Dataset. 21 Aug. 2022, \url{www.kaggle.com/code/mahendrasinghrajpoot/brain-stroke-dataset/input}.
 
-[19] Thomaskonstantin. Analyzing and Modeling Stroke Data. 6 July 2021, www.kaggle.com/code/thomaskonstantin/analyzing-and-modeling-stroke-data/input.
+[19] Thomaskonstantin. Analyzing and Modeling Stroke Data. 6 July 2021, \url{www.kaggle.com/code/thomaskonstantin/analyzing-and-modeling-stroke-data/input}.
 
-[20] Robikscube. Eye State Prediction Dataset. 26 June 2022, www.kaggle.com/code/robikscube/eye-state-prediction-dataset/input?select=EEG_Eye_State_Classification.csv.
+[20] Robikscube. Eye State Prediction Dataset. 26 June 2022, \url{www.kaggle.com/code/robikscube/eye-state-prediction-dataset/input?select=EEG_Eye_State_Classification.csv}.
 

### 2024-06-22 paper/paper.tex
Update paper.tex
diff

@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
-We performed a literature review of existing AutoML papers and conducted a survey on six popluar AutoML frameworks.
+We performed a literature review of existing AutoML papers and conducted a in depth survey on six popluar AutoML frameworks.
 Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated.
 We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant so unnecessary time is not spent training these models.
-SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" model that runs every model on every dataset, but in a fraction of the time.
+SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force model that runs every model on every dataset, but in a fraction of the time.
 \end{abstract}

### 2024-06-22 paper/paper.tex
Update paper.tex

@@
   \And
-  Benjamin Standefer$^2$ \\
+  Benjamin Joseph Michael Standefer$^2$ \\
   St. Mark's School of Texas \\
@@
 Cutting these models completely, however, is not optimal either, as they are the best option in a minority of cases and give frameworks versatility.
-We hypothesized that using a combination of layered machine learning implementation in which we train a model to predict a basic framework's outputs and meta-feature extraction in which we accelerate the training process by reducing complicated data matrices to their measurable attributes would yield an equally versatile system that minimizes time spent on prediction while still maximizing accuracy and straightforward implementation in a medical context.
+We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on prediction while still maximizing the other quantities.
 

### 2024-06-22 paper/paper.tex
artifacts
Update paper.tex

@@
 
-Machine learning (ML) is a type of artificial intelligence (AI) that uses a variety of algorithms to interpret data and extrapolate from it, making predictions based on observed trends.
-Individual models are trained on datasets to become smarter so as to make predictions based on new data.
-The development and optimization of these models is a time-consuming process involving statistical nuances and complex learning strategies.
-This has led to the emergence of Automated Machine Learning (AutoML) frameworks and research [1].
+Machine learning (ML) is a type of artificial intelligence (AI) that uses searching and trend-determining to make predictions.
+ML algorithms are trained and tested on a given dataset to become "smarter".
+Once they've learned the patterns typical of that data, they can make predictions based on similar but unseen data.
+These algorithms also require additional processes, however, like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning.
+This makes the process complex and time-inefficient.
+To do this on a larger scale and at greater speeds, recent research and effort have been put into Auto ML frameworks [1].
 
@@
 Further research should be done in incorporating this innovation into a full-fledged AutoML framework to expedite and improve the process further.
-A practical demonsration of this software's real-world application can be found on our SmartDx website.
+A practical demonsration of this software's real-world application can be found on our SmartDx website [21].
+Source code can be found at [22].
 \subsection{Limitations}
@@
 
+[21] SmartDx Website. \url{https://smartdx.vercel.app/}.
+
+[22] Github Repository. \url{www.github.com/ericspring08/SMEML-Paper}.
+}
+
 \end{document}

### 2024-06-23 paper/paper.tex
fix citations

--- 2024-06-22 paper/paper.tex
@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
-We performed a literature review of existing AutoML papers and conducted a in depth survey on six popluar AutoML frameworks.
+We performed a literature review of existing AutoML papers and conducted an in depth survey on six popluar AutoML frameworks.
 Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated.
@@
 \end{table}
-We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation [5, 6, 7, 8, 9, 10, 11, 12, 13].
+We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation [5-10].
 Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
@@
 FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere.
-It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [11, 12].
+It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [9, 12].
 H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average.
 In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [12].
-H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5, 6].
+H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5].
 MLJAR uses more advanced algorithms such as light gradient boosting and neural networks.
-It automatically deals with missing values and is known for its automated user interface [9, 10].
+It automatically deals with missing values and is known for its automated user interface [7, 8].
 TPOT uses genetic programming.
 It builds pipelines over multiple generations, which can be time consuming.
-It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [7, 8].
+It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [6, 8].
 
@@
 When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best.
-For example, linear models tend to work better on datasets where there is a linear relationship between features [14].
+For example, linear models tend to work better on datasets where there is a linear relationship between features [11].
 As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
@@
 \subsection{Experiment Design}
-To evaluate our framework, we choose 5 different datasets of diverse size [/15, /16, /17, /18, /19, /20].
+To evaluate our framework, we choose 5 different datasets of diverse size.
 We ran SMEML on each dataset for 20 iterations of tuning.
@@
     \midrule
-    Lung Cancer Prediction & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
-    Chronic Kidney Disease Dataset & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
-    Pima Indians Diabetes Dataset & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
-    Brain Stroke Prediction Dataset & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
-    Stroke Prediction Dataset & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
-    Eye State Classification & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
+    Lung Cancer Prediction [12] & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
+    Chronic Kidney Disease Dataset [13] & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
+    Pima Indians Diabetes Dataset [14] & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
+    Brain Stroke Prediction Dataset [15] & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
+    Stroke Prediction Dataset [16] & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
+    Eye State Classification [17] & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
     \bottomrule
@@
 After running the benchmark datasets, several observations were readily apparent.
-First, accurcy did not change for 4 of the 6 benchmarks.
+First, accuracy did not change for 4 of the 6 benchmarks.
 The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively.
@@
 Further research should be done in incorporating this innovation into a full-fledged AutoML framework to expedite and improve the process further.
-A practical demonsration of this software's real-world application can be found on our SmartDx website.
+A practical demonsration of this software's real-world application can be found on our SmartDx website [18].
+Source code can be found at [19].
 \subsection{Limitations}
@@
 \section*{References}
+
 \medskip
@@
 
-[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, \url{arxiv.org/pdf/1908.00709}.
+[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, 212, 106622 (2021), \url{https://doi.org/10.1016/j.knosys.2020.106622}.
 
-[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, vol. 5, no. 6, Oct. 2022, doi:10.1002/hsr2.893.
+[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, 5, 6 (2022), \url{https://doi.org/10.1002%2Fhsr2.893}.
 
-[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, \url{iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1}.
+[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 16 (2016), \url{}.
 
-[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, vol. 8, no. 2, July 2021, pp. e188–94, doi:10.7861/fhj.2021-0095.
+[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, 8, 188-94 (2021), \url{https://doi.org/10.7861%2Ffhj.2021-0095}
 
@@
 
-[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, \url{github.com/h2oai/h2o-3}.
+[6] Olson, Randal S., 1, et al.
+"Automating Biomedical Data Science Through Tree-based Pipeline Optimization." Applications of Evolutionary Computation, 19, 123 (2016), \url{https://doi.org/10.1007/978-3-319-31204-0_9}.
 
-[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, \url{arxiv.org/pdf/1601.07925}.
+[7] P\l{}o\'{n}ska, Aleksandra, et al. “MLJAR: State-of-the-art Automated Machine Learning Framework for Tabular Data.  Version 0.10.3.” MLJAR, (2021), \url{github.com/mljar/mljar-supervised}.
 
-[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, \url{github.com/EpistasisLab/tpot}.
+[8] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, 12, 19350 (2022), \url{https://doi.org/10.1038/s41598-022-23327-1}.
 
-[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, \url{github.com/mljar/mljar-supervised}.
+[9] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." 4th MLSys Conference, (2021), \url{https://doi.org/10.48550/arXiv.1911.04706} .
 
-[10] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, vol. 12, no. 1, Nov. 2022, doi:10.1038/s41598-022-23327-1.
+[10] Ryzhkov, Alexander, et al. "LightAutoML: AutoML Solution for a Large Financial Services Ecosystem." arXiv, (2021), \url{https://doi.org/10.48550/arXiv.2109.01528}
 
-[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, \url{arxiv.org/pdf/1911.04706}.
-
-[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, \url{github.com/microsoft/FLAML}.
-
-[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, \url{github.com/sb-ai-lab/LightAutoML}.
-
-[14] Akalin, Altuna.
+[11] Akalin, Altuna.
 3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R.
@@
 
-[15] Lung Cancer. 15 July 2022, \url{www.kaggle.com/datasets/nancyalaswad90/lung-cancer}.
+[12] Ms. Nancy Al Aswad. Lung Cancer. \url{www.kaggle.com/datasets/nancyalaswad90/lung-cancer}.
 
-[16] Chronic KIdney Disease Dataset. 13 Apr. 2017, \url{www.kaggle.com/datasets/mansoordaku/ckdisease}.
+[13] Mansoor Iqbal. Chronic KIdney Disease Dataset. \url{www.kaggle.com/datasets/mansoordaku/ckdisease}.
 
-[17] Busekseolu. Diabetes Classification. 26 Nov. 2021, \url{www.kaggle.com/code/busekseolu/diabetes-classification/input}.
+[14] UCI Machine Learning. Pima Indians Diabetes Dataset. \url{https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database}.
 
-[18] Mahendrasinghrajpoot. Brain Stroke Dataset. 21 Aug. 2022, \url{www.kaggle.com/code/mahendrasinghrajpoot/brain-stroke-dataset/input}.
+[15] Izzet Turkalp Akbasli. Brain stroke prediction dataset. \url{https://www.kaggle.com/datasets/zzettrkalpakbal/full-filled-brain-stroke-dataset}.
 
-[19] Thomaskonstantin. Analyzing and Modeling Stroke Data. 6 July 2021, \url{www.kaggle.com/code/thomaskonstantin/analyzing-and-modeling-stroke-data/input}.
+[16] fedesoriano. Stroke Prediction Dataset. \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.
 
-[20] Robikscube. Eye State Prediction Dataset. 26 June 2022, \url{www.kaggle.com/code/robikscube/eye-state-prediction-dataset/input?select=EEG_Eye_State_Classification.csv}.
+[17] Rob Mulla. Eye State Classification EEG Dataset. \url{https://www.kaggle.com/datasets/robikscube/eye-state-classification-eeg-dataset}.
+
+[18] SmartDx Website. \url{https://smartdx.vercel.app/}.
+
+[19] Github Repository. \url{www.github.com/ericspring08/SMEML-Paper}.
+}
 

### 2024-06-23 paper/paper.tex
Update paper.tex

@@
 FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere.
-It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [9, 12].
+It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [9].
 H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average.
-In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [12].
+In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [9].
 H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5].
 MLJAR uses more advanced algorithms such as light gradient boosting and neural networks.
-It automatically deals with missing values and is known for its automated user interface [7, 8].
+It automatically deals with missing values and is known for its automated user interface [7].
 TPOT uses genetic programming.
 It builds pipelines over multiple generations, which can be time consuming.
-It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [6, 8].
+It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [6].
 

### 2024-06-24 paper/paper.tex
Update paper.tex

@@
 
-\title{Smart Model Elimination for Efficient Automated Machine Learning}
+\title{Smart Model Elimination for Efficient Automated Machine Learning in Healthcare}
 
@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
-We performed a literature review of existing AutoML papers and conducted an in depth survey on six popluar AutoML frameworks.
+We performed a literature review of existing AutoML papers and conducted an in-depth survey on six popluar AutoML frameworks.
 Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated.
@@
 SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force model that runs every model on every dataset, but in a fraction of the time.
+We also believe this innovation is particularly to machine learning in healthcare because of the necessity for efficient diesease prediction.
 \end{abstract}

### 2024-06-24 paper/paper.tex
feature importance

@@
   \centering
-  \begin{tabular}{lll}
+  \begin{tabular}{llll}
     \toprule
-    Attribute & Formula & Purpose\\
+    Attribute & Formula & Purpose & Weight\\
     \midrule
-    \# of Rows & $|\mathbf{A}|_r$ & Data Size \\
+    \# of Rows & $|\mathbf{A}|_r$ & DS & .0422 \\
     \hline
-    \# of Columns & $|\mathbf{A}|_c$ & Data Size \\
+    \# of Columns & $|\mathbf{A}|_c$ & DS & .0415 \\
     \hline
@@
     $\frac{\max(\text{count}_1, \text{count}_0)}{|\mathbf{A}|_r}$
-    & Data Type \\
+    & DT & .0489 \\
     \hline
@@
     $\frac{|\mathbf{A}_{num}|}{|\mathbf{A}|_{c}}$
-    & Data Type \\
+    & DT & .0428 \\
     \hline
@@
     $\frac{|\mathbf{A}_{bin}|}{|\mathbf{A}|_{c}}$
-    & Data Type \\
+    & DT & .0117 \\
     \hline
-    Mean \# of Distinct Values  & $\mu \left\{\text{\# of distinct values in column}\right\}$ & Data Type \\ 
+    Mean \# of Distinct Values  & $\mu \left\{\text{\# of distinct values in column}\right\}$ & DT & .0076 \\ 
     \hline
-    Mean IQR  & $\mu \left\{\text{IQR of column}\right\}$ & Data Distribution \\ 
+    Mean IQR  & $\mu \left\{\text{IQR of column}\right\}$ & DD & .0594 \\ 
     \hline
-    STD of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & Data Distribution \\
+    STD of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & DD & .0700 \\
     \hline
-    Mean Q1 & $\mu \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
+    Mean Q1 & $\mu \left\{\text{Q1 of column}\right\}$ & DD & .0789 \\
     \hline
-    STD of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
+    STD of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & DD & .0613 \\
     \hline
-    Mean Q3  & $\mu \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
+    Mean Q3  & $\mu \left\{\text{Q3 of column}\right\}$ & DD & .0812 \\
     \hline
-    STD of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
+    STD of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & DD & .1103 \\
     \hline
     Mean Percent of Z-Score Outliers  & 
-    $\mu \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & Outlier Data Points \\
+    $\mu \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0558 \\
     \hline
     STD of Percent of Z-Score Outliers  &
-    $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & Outlier Data Points \\
+    $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0798 \\
     \hline
-    Mean Correlation& $\mu \left\{\text{Correlation Matrix}\right\}$ & Data linearity \\
+    Mean Correlation& $\mu \left\{\text{Correlation Matrix}\right\}$ & DL & .0559 \\
     \hline
-    STD of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & Data Linearity \\
+    STD of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & DL & .1526 \\
     \bottomrule
   \end{tabular}
+  \captionsetup{font=footnotesize}
+  \caption*{\textbf{Abbreviations}: DS: Data Size, DT: Data Type, DD: Data Distribution, ODP: Outlier Data Points, DL: Data Linearity}
 \end{table}

### 2024-06-24 paper/paper.tex
variable importance
Update paper.tex

@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
-We performed a literature review of existing AutoML papers and conducted an in-depth survey on six popluar AutoML frameworks.
+We performed a literature review of existing AutoML papers and conducted an in-depth survey on five popluar AutoML frameworks.
 Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated.
-We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant so unnecessary time is not spent training these models.
-SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force model that runs every model on every dataset, but in a fraction of the time.
-We also believe this innovation is particularly to machine learning in healthcare because of the necessity for efficient diesease prediction.
+We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant.
+SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force model, but in a fraction of the time.
+We also believe this innovation is particularly relevant to machine learning in healthcare because of the necessity for efficient diesease prediction.
 \end{abstract}
@@
 The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030 [3].
-The use of AI in healthcare has been varied.
 Medical AI's typically automate repetitive tasks, making time consumption a primary concern [4].
@@
     \midrule
-    H2O AutoML & Easy & 6 & Basic & Yes & Auto & SHAP & High\\
+    H2O AutoML & Easy & 12 & Basic & Yes & Auto & SHAP & High\\
     TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
@@
 
-Taking a closer look at four AutoML standards, we can observe pros and cons in their theoretical application to medicine and research.
-FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks in the medical sphere.
-It supports imputation techniques for missing values with user specification and has an intuitive API, making it moderately user-friendly for minimally trained healthcare workers [9].
-H2O has a wider variety of supported algorithms that may or may not be appropriate for medical diagnosis, making it slower than FLAML on average.
+We can observe pros and cons in the four models' theoretical applications.
+FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks.
+It supports user-specified imputation techniques for missing values and has an intuitive API, making it moderately user-friendly for healthcare workers [9].
+H2O has a wider variety of supported algorithms that may be appropriate for medical diagnosis, making it slower than FLAML on average.
 In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [9].
 H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5].
-MLJAR uses more advanced algorithms such as light gradient boosting and neural networks.
+MLJAR uses advanced algorithms such as light gradient boosting and neural networks.
 It automatically deals with missing values and is known for its automated user interface [7].
@@
 Keeping the factors we have laid out in mind, namely expeditious running, accuracy, and interpretability, we also uncovered a key continuity in framework design: frameworks are forced to run and train the majority of their available models to maximize accuracy at the expense of efficiency.
-Given the restricted nature of tabular data, there are some models that, in general, are less likely to perform well, thus running and training these models is frequently wasteful.
-Cutting these models completely, however, is not optimal either, as they are the best option in a minority of cases and give frameworks versatility.
+Given the restricted nature of tabular data, there are some models that are less likely to perform well, thus running and training these models is frequently wasteful.
+Cutting these models completely, however, is not optimal either, as they are the best option in a minority of cases.
 We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on prediction while still maximizing the other quantities.
@@
 These extracted attributes are shown in Table 2.
+Each attribute attempts to capture a specific type of relationship or distribution within the data.
+The variable importance of each attribute is shown in the "Weight" column.
+Linearity and data distribution are the most important attributes in determining the best model.
 
@@
 
-After running the benchmark datasets, several observations were readily apparent.
+Several observations were readily apparent from running these datasets.
 First, accuracy did not change for 4 of the 6 benchmarks.
@@
 \subsection{Summary}
-As evidenced by our experiment's results, SMEML manages to return comparable accuracy results compared to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks.
+SMEML manages to return comparable accuracy results compared to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks.
 Its performance is not limited by the size of the dataset, and it in fact returned its first, third, and fourth best percentage-based run times on the 'large' dataset benchmarks (those exceeding 1000 rows).
@@
 \subsection{Future Work}
-Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks on more datasets.
+Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks.
 Furthermore, we can examine other types of machine learning such as regression and multiclass-classification.

### 2024-06-24 paper/paper.tex
Update paper.tex

@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
-We performed a literature review of existing AutoML papers and conducted an in-depth survey on five popluar AutoML frameworks.
-Many of these frameworks optimize a form of model selection, however, they all require every model to be run and evaluated.
+We performed a literature review of existing AutoML papers and conducted a survey on five popular AutoML frameworks.
+Many of these frameworks optimize a form of model selection, but they all require every model to be run and evaluated.
 We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant.
@@
 ML algorithms are trained and tested on a given dataset to become "smarter".
-Once they've learned the patterns typical of that data, they can make predictions based on similar but unseen data.
+Once they've learned the patterns typical of that data, they can make predictions based on similar data.
 These algorithms also require additional processes, however, like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning.
@@
 
-Keeping the factors we have laid out in mind, namely expeditious running, accuracy, and interpretability, we also uncovered a key continuity in framework design: frameworks are forced to run and train the majority of their available models to maximize accuracy at the expense of efficiency.
-Given the restricted nature of tabular data, there are some models that are less likely to perform well, thus running and training these models is frequently wasteful.
-Cutting these models completely, however, is not optimal either, as they are the best option in a minority of cases.
+Keeping the factors we have laid out in mind, we also uncovered a key continuity in framework design: frameworks must run the majority of their models to maximize accuracy at the expense of efficiency.
+Given the restricted nature of tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful.
+Cutting these models completely, however, is not optimal, as they are the best option in a minority of cases.
 We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on prediction while still maximizing the other quantities.
@@
 \section{Methodology}
-When considering a specific dataset, various aspects regarding the distribution and relationship within the data can give us clues as to which models are likely to perform best.
+When considering a specific dataset, the distribution and relationship between datapoints can give us clues as to which models are likely to perform best.
 For example, linear models tend to work better on datasets where there is a linear relationship between features [11].
-As a result, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
+Accordingly, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
 These extracted attributes are shown in Table 2.
@@
 To implement this model elimination process, we trained a boosting model on 268 kaggle datasets.
-We chose datasets that were medically related and focused our approach on binary classification.
+We chose medical datasets and focused our approach on binary classification.
 We extracted the attributes in Table 2 from each dataset: this is the input for the boosting model.
@@
 
-Several observations were readily apparent from running these datasets.
+Several observations were made from running these datasets.
 First, accuracy did not change for 4 of the 6 benchmarks.
@@
 \subsection{Summary}
-SMEML manages to return comparable accuracy results compared to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks.
-Its performance is not limited by the size of the dataset, and it in fact returned its first, third, and fourth best percentage-based run times on the 'large' dataset benchmarks (those exceeding 1000 rows).
+SMEML manages to return comparable accuracy results to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks.
+Its performance is not limited by the size of the dataset, and it returned its first, third, and fourth best percentage-based run times on the 'large' dataset benchmarks (those exceeding 1000 rows).
 This is important in third world medicine where time is of the essence and there is a constant influx of new patient data.
-Further research should be done in incorporating this innovation into a full-fledged AutoML framework to expedite and improve the process further.
 A practical demonsration of this software's real-world application can be found on our SmartDx website [18].

### 2024-06-24 paper/paper.tex
remove ack

--- 2024-06-24 paper/paper.tex
@@
 Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks.
-Furthermore, we can examine other types of machine learning such as regression and multiclass-classification.
-\begin{ack}
-The authors would like to thank the St. Mark's School of Texas for supporting this research.
-\end{ack}
+Furthermore, we will examine other types of machine learning such as regression and multiclass-classification.
 

### 2024-06-25 paper/paper.tex
update emails
new citations

@@
   10600 Preston Rd, Dallas, TX 75230\\
-  \texttt{ericspring08@gmail.com} \\
+  \texttt{26zhange@smtexas.org} \\
   % examples of more authors
@@
   10600 Preston Rd, Dallas, TX 75230 \\
-  \texttt{bjmstandefer@gmail.com} \\
+  \texttt{26standeferb@smtexas.org} \\
   % \AND
@@
 We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant.
-SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force model, but in a fraction of the time.
+SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force framework, but in a fraction of the time.
 We also believe this innovation is particularly relevant to machine learning in healthcare because of the necessity for efficient diesease prediction.
@@
 This makes the process complex and time-inefficient.
-To do this on a larger scale and at greater speeds, recent research and effort have been put into Auto ML frameworks [1].
+To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks [1].
 
@@
 The World Health Organization (WHO) emphasized that this deficit is growing every year and will likely reach 18 million personnel by 2030 [3].
-Medical AI's typically automate repetitive tasks, making time consumption a primary concern [4].
+Medical AIs typically automate repetitive tasks, making time consumption a primary concern [4].
 This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue.
@@
 Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected.
-However, these frameworks require that every model to be run to filter out [1].
+However, these frameworks require that every model be run [1].
 In theory, this means that much energy is spent training models that are unlikely to be selected.
@@
     \midrule
-    H2O AutoML & Easy & 12 & Basic & Yes & Auto & SHAP & High\\
-    TPOT & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
-    MLJAR & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
-    FLAML & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
-    LightAutoML & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
+    H2O AutoML [5] & Easy & 12 & Basic & Yes & Auto & SHAP & High\\
+    TPOT [6] & Hard & 10 & Basic & No & Genetic & POJO & Moderate\\
+    MLJAR [7,8] & Easy & 12 & Advanced & Yes & Auto & Basic & High\\
+    FLAML [9] & Easy & 9 & Limited & Yes & Auto & SHAP & Low-Moderate\\
+    LightAutoML [10] & Easy & 11 & Advanced & Yes & Auto & Basic & Moderate\\
     \bottomrule
@@
 \end{table}
-We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation [5-10].
+We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation.
 Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
@@
 Keeping the factors we have laid out in mind, we also uncovered a key continuity in framework design: frameworks must run the majority of their models to maximize accuracy at the expense of efficiency.
-Given the restricted nature of tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful.
+Given the specific nature of certain tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful.
 Cutting these models completely, however, is not optimal, as they are the best option in a minority of cases.
-We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on prediction while still maximizing the other quantities.
+We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on training without sacrificing accuracy.
 
 \section{Methodology}
-When considering a specific dataset, the distribution and relationship between datapoints can give us clues as to which models are likely to perform best.
+When considering a specific dataset, the distribution, relationship between datapoints, and various other attributes can give us clues as to which models are likely to perform best.
 For example, linear models tend to work better on datasets where there is a linear relationship between features [11].
@@
 Each attribute attempts to capture a specific type of relationship or distribution within the data.
-The variable importance of each attribute is shown in the "Weight" column.
-Linearity and data distribution are the most important attributes in determining the best model.
 
-We considered 28 different models, including all supervised and semi-supervised sklearn classification models and common boosting models such as XGBoost, Lightgbm, and Catboost.
+We considered 28 different models, including all supervised and semi-supervised sklearn [12] classification models and common boosting models such as XGBoost [13], LightGBM [14], and Catboost [15].
 
@@
 We then ran a "dumb" framework that trained every model on each dataset.
-The accuracy of every model is ranked and every model is treated as a label with its value being its rank.
+The accuracy of every model is ranked, and every model is treated as a label with its value being its rank.
 Then we trained a multilabel regression to predict the rank of each model, giving the extracted attributes.
@@
 It feeds these attributes into the boosting model to get the predicted rank of each model.
-Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 18 models from the list.
-We run Bayseian optimization on the top eight models to get the best hyperparamters for each model.
+Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 20 models from the list.
+We run Bayseian optimization using scikit-optimize [16] on the top eight models to get the best hyperparamters for each model.
 We select the top models that have significantly better performance than other models.
@@
   \captionsetup{font=footnotesize}
-  \caption*{\textbf{Abbreviations}: DS: Data Size, DT: Data Type, DD: Data Distribution, ODP: Outlier Data Points, DL: Data Linearity}
+  \caption*{\textbf{Abbreviations}: DS: Data Size, DT: Data Type, DD: Data Distribution, ODP: Outlier Data Points, DL: Data Linearity, Weight: Variable Importance}
 \end{table}
@@
 \includegraphics[width=\textwidth]{smeml-flowchart.png}
-\caption{SMEML Process}
+\caption{Illustration of the SMEML Process}
 \end{figure}
@@
     \midrule
-    Lung Cancer Prediction [12] & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
-    Chronic Kidney Disease Dataset [13] & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
-    Pima Indians Diabetes Dataset [14] & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
-    Brain Stroke Prediction Dataset [15] & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
-    Stroke Prediction Dataset [16] & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
-    Eye State Classification [17] & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
+    Lung Cancer Prediction [17] & .9839 & .9839 & 143.07 & 317.04 & 309x16\\
+    Chronic Kidney Disease Dataset [18] & 1.0 & 1.0 & 419.64 & 788.46 & 400x26\\
+    Pima Indians Diabetes Dataset [19] & .7857 & .8052 & 161.99 & 374.01 & 768x8 \\
+    Brain Stroke Prediction Dataset [20] & .9458 & .9458 & 114.16 & 370.95 & 4892x11\\
+    Stroke Prediction Dataset [21] & .9393 & .9393 & 172.67 & 385.23 & 5110x12 \\
+    Eye State Classification [22] & .9536 & .9549 & 312.57 & 696.51 & 14980x15\\ 
     \bottomrule
@@
 This is important in third world medicine where time is of the essence and there is a constant influx of new patient data.
-A practical demonsration of this software's real-world application can be found on our SmartDx website [18].
-Source code can be found at [19].
+A practical demonsration of this software's real-world application can be found on our SmartDx website [23].
+Source code can be found at [24].
 \subsection{Limitations}
@@
 
-[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, 212, 106622 (2021), \url{https://doi.org/10.1016/j.knosys.2020.106622}.
+[1] He, X., et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems. 212, 106622 (2021). \url{https://doi.org/10.1016/j.knosys.2020.106622}.
 
-[2] Nchasi, Goodluck, et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports, 5, 6 (2022), \url{https://doi.org/10.1002%2Fhsr2.893}.
+[2] Nchasi, G., et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports. 5, 6 (2022). \url{https://doi.org/10.1002/hsr2.893}.
 
-[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 16 (2016), \url{}.
+[3] "Global Strategy on Human Resources for Health: Workforce 2030." World Health Organization. 16 (2020). \url{https://www.who.int/publications/i/item/9789241511131}.
 
-[4] Bajwa, Junaid, et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal, 8, 188-94 (2021), \url{https://doi.org/10.7861%2Ffhj.2021-0095}
+[4] Bajwa, J., et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal. 8, 188-94 (2021). \url{https://doi.org/10.7861/fhj.2021-0095}.
 
@@
 Poirier.
-“H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning, 2020, \url{www.automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.
+“H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning.
+(2020).
+\url{https://automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.
 
-[6] Olson, Randal S., 1, et al.
-"Automating Biomedical Data Science Through Tree-based Pipeline Optimization." Applications of Evolutionary Computation, 19, 123 (2016), \url{https://doi.org/10.1007/978-3-319-31204-0_9}.
+[6] Olson, S., et al.
+"Automating Biomedical Data Science Through Tree-based Pipeline Optimization." Applications of Evolutionary Computation.
+19, 123 (2016).
+\url{https://doi.org/10.1007/978-3-319-31204-0_9}.
 
-[7] P\l{}o\'{n}ska, Aleksandra, et al. “MLJAR: State-of-the-art Automated Machine Learning Framework for Tabular Data.  Version 0.10.3.” MLJAR, (2021), \url{github.com/mljar/mljar-supervised}.
+[7] P\l{}o\'{n}ska, A., et al. “MLJAR: State-of-the-art Automated Machine Learning Framework for Tabular Data.  Version 0.10.3.” MLJAR. (2021). \url{https://github.com/mljar/mljar-supervised}.
 
-[8] Conrad, Felix, et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports, 12, 19350 (2022), \url{https://doi.org/10.1038/s41598-022-23327-1}.
+[8] Conrad, F., et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports. 12, 19350 (2022). \url{https://doi.org/10.1038/s41598-022-23327-1}.
 
-[9] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." 4th MLSys Conference, (2021), \url{https://doi.org/10.48550/arXiv.1911.04706} .
+[9] Shang, Z., et al. "FLAML: A Fast and Lightweight AutoML Library." 4th MLSys Conference. (2021). \url{https://doi.org/10.48550/arXiv.1911.04706}.
 
-[10] Ryzhkov, Alexander, et al. "LightAutoML: AutoML Solution for a Large Financial Services Ecosystem." arXiv, (2021), \url{https://doi.org/10.48550/arXiv.2109.01528}
+[10] Ryzhkov, A., et al. "LightAutoML: AutoML Solution for a Large Financial Services Ecosystem." arXiv:2109.01528. (2021). \url{https://doi.org/10.48550/arXiv.2109.01528}.
 
-[11] Akalin, Altuna.
-3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R.
-30 Sept.
-2020, \url{compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.
+[11] Akalin, A., "Computational Genomics With R." Chapman and Hall/CRC. 1, Section 3.3, (2020). \url{compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.
 
-[12] Ms. Nancy Al Aswad. Lung Cancer. \url{www.kaggle.com/datasets/nancyalaswad90/lung-cancer}.
+[12] Pedregosa, F., et al. "Scikit-learn: Machine Learning in Python." Journal of Machine Learning Research. 12, 2825 (2011). \url{https://doi.org/10.48550/arXiv.1201.0490}.
 
-[13] Mansoor Iqbal. Chronic KIdney Disease Dataset. \url{www.kaggle.com/datasets/mansoordaku/ckdisease}.
+[13] Chen, T., et al.
+"XGBoost: A Scalable Tree Boosting System." 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining.
+(2016).
+\url{https://doi.org/10.1145/2939672.2939785}.
 
-[14] UCI Machine Learning. Pima Indians Diabetes Dataset. \url{https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database}.
+[14] Ke, G., et al. "LightGBM: A Highly Efficient Gradient Boosting Decision Tree." Advances in Neural Information Processing Systems. 30, 3149 (2017). \url{https://doi.org/10.48550/arXiv.1706.08359}.
 
-[15] Izzet Turkalp Akbasli. Brain stroke prediction dataset. \url{https://www.kaggle.com/datasets/zzettrkalpakbal/full-filled-brain-stroke-dataset}.
+[15] Prokhorenkova, L., et al.
+"CatBoost: Unbiased Boosting with Categorical Features." Advances in Neural Information Processing Systems.
+32, 6639 (2018).
+\url{https://doi.org/10.48550/arXiv.1706.09516}.
 
-[16] fedesoriano. Stroke Prediction Dataset. \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.
+[16] Head, T. et al. "Scikit-Optimize: Sequential Model-Based Optimization." Zenodo. (2020). \url{https://doi.org/10.5281/zenodo.1170575}.
 
-[17] Rob Mulla. Eye State Classification EEG Dataset. \url{https://www.kaggle.com/datasets/robikscube/eye-state-classification-eeg-dataset}.
+[17] Ms. Nancy Al Aswad. Lung Cancer (dataset). \url{https://kaggle.com/datasets/nancyalaswad90/lung-cancer}.
 
-[18] SmartDx Website. \url{https://smartdx.vercel.app/}.
+[18] Mansoor Iqbal. Chronic KIdney Disease Dataset (dataset). \url{https://kaggle.com/datasets/mansoordaku/ckdisease}.
 
-[19] Github Repository. \url{www.github.com/ericspring08/SMEML-Paper}.
+[19] UCI Machine Learning. Pima Indians Diabetes Dataset (dataset). \url{https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database}.
+
+[20] Izzet Turkalp Akbasli. Brain stroke prediction dataset (dataset). \url{https://www.kaggle.com/datasets/zzettrkalpakbal/full-filled-brain-stroke-dataset}.
+
+[21] fedesoriano. Stroke Prediction Dataset (dataset). \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.
+
+[22] Rob Mulla. Eye State Classification EEG Dataset (dataset). \url{https://www.kaggle.com/datasets/robikscube/eye-state-classification-eeg-dataset}.
+
+[23] SmartDx Website. \url{https://smartdx.vercel.app/}.
+
+[24] Github Repository. \url{https://github.com/ericspring08/SMEML-Paper}.
 }

### 2024-06-25 paper/paper.tex
add ack
more edits

@@
 This coupled with a lack of adequate resources makes designing faster diagnostic systems for developing countries' medical sectors a pivotal issue.
-%
+
 Most AutoML frameworks implement some form of model selection where a pool of models are filtered until a final model is selected.
@@
 \end{table}
-We systematically reviewed and compared five different AutoML frameworks, comparing every feature relevant to medical implementation.
-Of these six, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
+We systematically review and compare five different AutoML frameworks, comparing every feature relevant to medical implementation in Table 1.
+Of these five, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
 
@@
 H2O has a wider variety of supported algorithms that may be appropriate for medical diagnosis, making it slower than FLAML on average.
-In one trial, more than half of FLAML's performances in one minute were better than or equal to H20's performances in one hour [9].
+In one trial, more than half of FLAML's performances in one minute were better than or equal to H2O's performances in one hour [9].
 H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5].
@@
 It builds pipelines over multiple generations, which can be time consuming.
-It has built-in pre-processing for missing values, but the genetic programming can require fine-tuning from users [6].
+It has built-in pre-processing for missing values, but the genetic programming requires fine-tuning from users [6].
 
-Keeping the factors we have laid out in mind, we also uncovered a key continuity in framework design: frameworks must run the majority of their models to maximize accuracy at the expense of efficiency.
+Through this survey, we uncovered a key continuity in these frameworks' design: frameworks must run all of their models to maximize accuracy at the expense of efficiency.
 Given the specific nature of certain tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful.
 Cutting these models completely, however, is not optimal, as they are the best option in a minority of cases.
-We hypothesized that using a combination of layered machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on training without sacrificing accuracy.
+We hypothesized that using a combination of multi-layer machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on training without sacrificing accuracy.
 
@@
 For example, linear models tend to work better on datasets where there is a linear relationship between features [11].
-Accordingly, we can develop a boosting model to predict the best models based off extracted attributes from a dataset.
+Accordingly, we can develop a boosting model to predict the best models based on extracted attributes from a dataset.
 These extracted attributes are shown in Table 2.
@@
 
-To implement this model elimination process, we trained a boosting model on 268 kaggle datasets.
-We chose medical datasets and focused our approach on binary classification.
-We extracted the attributes in Table 2 from each dataset: this is the input for the boosting model.
-We then ran a "dumb" framework that trained every model on each dataset.
+To implement the model elimination process, we train a multilabel-regression boosting model called the SME Model-Ranker on 268 kaggle datasets.
+We choose medical datasets and focus our approach on binary classification.
+We extract the attributes in Table 2 from each dataset: this is the input for the boosting model.
+We then run a "dumb", brute-force framework that trains every model every each dataset.
 The accuracy of every model is ranked, and every model is treated as a label with its value being its rank.
-Then we trained a multilabel regression to predict the rank of each model, giving the extracted attributes.
-We produced a median spearman correlation of 0.7301 between the predicted rank and the actual rank and a median p-value of 1.032e-05.
+We train the SME to predict the rank of each model, given the extracted attributes.
+SME produces a median spearman correlation of 0.7301 between the predicted rank and the actual rank and a median p-value of 1.032e-05.
 Furthermore, we guarantee that we can predict a top two model within the predicted top eight 90.12\% of the time.
 
-When a user inputs a dataset into SMEML, it first extracts the attributes from the dataset.
-It feeds these attributes into the boosting model to get the predicted rank of each model.
+When a user inputs a dataset into SMEML, it first extracts the attributes from the dataset and then feeds them into the SME to get the predicted rank of each model.
 Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 20 models from the list.
@@
 \begin{table}
-  \caption{Experiment Results}
+  \caption{Comparing experiment results for SMEML and dumb mode}
   \label{model-options-table}
@@
 SMEML manages to return comparable accuracy results to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks.
-Its performance is not limited by the size of the dataset, and it returned its first, third, and fourth best percentage-based run times on the 'large' dataset benchmarks (those exceeding 1000 rows).
+Its performance is not limited by the size of the dataset, and it returned its first, third, and fourth overall best run times for SMEML relative to the dumb mode on the 'large' dataset benchmarks (those exceeding 1000 rows).
 This is important in third world medicine where time is of the essence and there is a constant influx of new patient data.
@@
 
+\begin{ack}
+We would like to thank St. Mark's School of Texas for supporting this research.
+\end{ack}
+
 \section*{References}
@@
 
-[1] He, X., et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems. 212, 106622 (2021). \url{https://doi.org/10.1016/j.knosys.2020.106622}.
+[1] He, X., et al., “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems 212, 106622 (2021). \url{https://doi.org/10.1016/j.knosys.2020.106622}.
 
-[2] Nchasi, G., et al. “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports. 5, 6 (2022). \url{https://doi.org/10.1002/hsr2.893}.
+[2] Nchasi, G., et al., “Challenges Faced by African Healthcare Workers During the Third Wave of the Pandemic.” Health Science Reports 5, 6 (2022). \url{https://doi.org/10.1002/hsr2.893}.
 
-[3] "Global Strategy on Human Resources for Health: Workforce 2030." World Health Organization. 16 (2020). \url{https://www.who.int/publications/i/item/9789241511131}.
+[3] "Global Strategy on Human Resources for Health: Workforce 2030." World Health Organization, pg. 16 (2020). \url{https://www.who.int/publications/i/item/9789241511131}.
 
-[4] Bajwa, J., et al. “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal. 8, 188-94 (2021). \url{https://doi.org/10.7861/fhj.2021-0095}.
+[4] Bajwa, J., et al., “Artificial Intelligence in Healthcare: Transforming the Practice of Medicine.” Future Healthcare Journal 8, 188 (2021). \url{https://doi.org/10.7861/fhj.2021-0095}.
 
 [5] LeDell, E., and S.
-Poirier.
-“H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning.
-(2020).
+Poirier, “H2O AutoML: Scalable Automatic Machine Learning.” 7th ICML Workshop on Automated Machine Learning (2020).
 \url{https://automl.org/wp-content/uploads/2020/07/AutoML_2020_paper_61.pdf}.
 
-[6] Olson, S., et al.
-"Automating Biomedical Data Science Through Tree-based Pipeline Optimization." Applications of Evolutionary Computation.
-19, 123 (2016).
+[6] Olson, S., et al., "Automating Biomedical Data Science Through Tree-based Pipeline Optimization." Applications of Evolutionary Computation 19, 123 (2016).
 \url{https://doi.org/10.1007/978-3-319-31204-0_9}.
 
-[7] P\l{}o\'{n}ska, A., et al. “MLJAR: State-of-the-art Automated Machine Learning Framework for Tabular Data.  Version 0.10.3.” MLJAR. (2021). \url{https://github.com/mljar/mljar-supervised}.
+[7] P\l{}o\'{n}ska, A., et al., “MLJAR: State-of-the-art Automated Machine Learning Framework for Tabular Data.  Version 0.10.3.” MLJAR (2021). \url{https://github.com/mljar/mljar-supervised}.
 
-[8] Conrad, F., et al. “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports. 12, 19350 (2022). \url{https://doi.org/10.1038/s41598-022-23327-1}.
+[8] Conrad, F., et al., “Benchmarking AutoML for Regression Tasks on Small Tabular Data in Materials Design.” Scientific Reports 12, 19350 (2022). \url{https://doi.org/10.1038/s41598-022-23327-1}.
 
-[9] Shang, Z., et al. "FLAML: A Fast and Lightweight AutoML Library." 4th MLSys Conference. (2021). \url{https://doi.org/10.48550/arXiv.1911.04706}.
+[9] Shang, Z., et al., "FLAML: A Fast and Lightweight AutoML Library." 4th MLSys Conference (2021). \url{https://doi.org/10.48550/arXiv.1911.04706}.
 
-[10] Ryzhkov, A., et al. "LightAutoML: AutoML Solution for a Large Financial Services Ecosystem." arXiv:2109.01528. (2021). \url{https://doi.org/10.48550/arXiv.2109.01528}.
+[10] Ryzhkov, A., et al., "LightAutoML: AutoML Solution for a Large Financial Services Ecosystem." arXiv:2109.01528 (2021). \url{https://doi.org/10.48550/arXiv.2109.01528}.
 
-[11] Akalin, A., "Computational Genomics With R." Chapman and Hall/CRC. 1, Section 3.3, (2020). \url{compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.
+[11] Akalin, A., "Computational Genomics With R." Chapman and Hall/CRC, Vol.
+1, Section 3.3, (2020).
+\url{https://compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.
 
-[12] Pedregosa, F., et al. "Scikit-learn: Machine Learning in Python." Journal of Machine Learning Research. 12, 2825 (2011). \url{https://doi.org/10.48550/arXiv.1201.0490}.
+[12] Pedregosa, F., et al., "Scikit-learn: Machine Learning in Python." Journal of Machine Learning Research 12, 2825 (2011). \url{https://doi.org/10.48550/arXiv.1201.0490}.
 
-[13] Chen, T., et al.
-"XGBoost: A Scalable Tree Boosting System." 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining.
-(2016).
+[13] Chen, T., et al., "XGBoost: A Scalable Tree Boosting System." 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (2016).
 \url{https://doi.org/10.1145/2939672.2939785}.
 
-[14] Ke, G., et al. "LightGBM: A Highly Efficient Gradient Boosting Decision Tree." Advances in Neural Information Processing Systems. 30, 3149 (2017). \url{https://doi.org/10.48550/arXiv.1706.08359}.
+[14] Ke, G., et al., "LightGBM: A Highly Efficient Gradient Boosting Decision Tree." Advances in Neural Information Processing Systems 30, 3149 (2017). \url{https://doi.org/10.48550/arXiv.1706.08359}.
 
-[15] Prokhorenkova, L., et al.
-"CatBoost: Unbiased Boosting with Categorical Features." Advances in Neural Information Processing Systems.
-32, 6639 (2018).
+[15] Prokhorenkova, L., et al., "CatBoost: Unbiased Boosting with Categorical Features." Advances in Neural Information Processing Systems 32, 6639 (2018).
 \url{https://doi.org/10.48550/arXiv.1706.09516}.
 
-[16] Head, T. et al. "Scikit-Optimize: Sequential Model-Based Optimization." Zenodo. (2020). \url{https://doi.org/10.5281/zenodo.1170575}.
+[16] Head, T. et al., "Scikit-Optimize: Sequential Model-Based Optimization." Zenodo (2020). \url{https://doi.org/10.5281/zenodo.1170575}.
 
-[17] Ms. Nancy Al Aswad. Lung Cancer (dataset). \url{https://kaggle.com/datasets/nancyalaswad90/lung-cancer}.
+[17] Ms. Nancy Al Aswad, "Lung Cancer" (dataset). \url{https://kaggle.com/datasets/nancyalaswad90/lung-cancer}.
 
-[18] Mansoor Iqbal. Chronic KIdney Disease Dataset (dataset). \url{https://kaggle.com/datasets/mansoordaku/ckdisease}.
+[18] Mansoor Iqbal, "Chronic KIdney Disease Dataset" (dataset). \url{https://kaggle.com/datasets/mansoordaku/ckdisease}.
 
-[19] UCI Machine Learning. Pima Indians Diabetes Dataset (dataset). \url{https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database}.
+[19] UCI Machine Learning, "Pima Indians Diabetes Dataset" (dataset). \url{https://www.kaggle.com/datasets/uciml/pima-indians-diabetes-database}.
 
-[20] Izzet Turkalp Akbasli. Brain stroke prediction dataset (dataset). \url{https://www.kaggle.com/datasets/zzettrkalpakbal/full-filled-brain-stroke-dataset}.
+[20] Izzet Turkalp Akbasli, "Brain stroke prediction dataset" (dataset). \url{https://www.kaggle.com/datasets/zzettrkalpakbal/full-filled-brain-stroke-dataset}.
 
-[21] fedesoriano. Stroke Prediction Dataset (dataset). \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.
+[21] fedesoriano, "Stroke Prediction Dataset" (dataset). \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.
 
-[22] Rob Mulla. Eye State Classification EEG Dataset (dataset). \url{https://www.kaggle.com/datasets/robikscube/eye-state-classification-eeg-dataset}.
+[22] Rob Mulla, "Eye State Classification EEG Dataset" (dataset). \url{https://www.kaggle.com/datasets/robikscube/eye-state-classification-eeg-dataset}.
 

### 2024-06-25 paper/paper.tex
small changes

@@
   Automated Machine Learning or AutoML has emerged as a popular field of research.
-We performed a literature review of existing AutoML papers and conducted a survey on five popular AutoML frameworks.
+We perform a literature review of existing AutoML papers and conduct a survey on five popular AutoML frameworks.
 Many of these frameworks optimize a form of model selection, but they all require every model to be run and evaluated.
@@
 We choose medical datasets and focus our approach on binary classification.
-We extract the attributes in Table 2 from each dataset: this is the input for the boosting model.
+We extract the attributes in Table 2 from each dataset: which are the inputs for the boosting model.
 We then run a "dumb", brute-force framework that trains every model every each dataset.
@@
 
-\section{Experiments}
+\section{Evaluation}
 \subsection{Experiment Design}
@@
 
-\subsection{Results}
+\subsection{Experiment Results}
 \begin{table}

### 2024-06-25 paper/paper.tex
improve abstract and summary

@@
 \begin{abstract}
-  Automated Machine Learning or AutoML has emerged as a popular field of research.
-We perform a literature review of existing AutoML papers and conduct a survey on five popular AutoML frameworks.
-Many of these frameworks optimize a form of model selection, but they all require every model to be run and evaluated.
-We propose a novel framework, SMEML (Smart Model Elimination Machine Learning), that automatically eliminates models that are unlikely to be performant.
-SMEML demonstrates the ability to generate a model with near equal accuracy to a "dumb" brute-force framework, but in a fraction of the time.
-We also believe this innovation is particularly relevant to machine learning in healthcare because of the necessity for efficient diesease prediction.
+  Automated Machine Learning (AutoML) has emerged as a popular field of research.
+We present a literature review of existing AutoML papers and conduct a survey on five popular AutoML frameworks.
+Typically, these frameworks engage in model selection by requiring every model to be run and assessed, a process both time-intensive and computationally expensive.
+In response, we propose a novel framework, Smart Model Elimination Machine Learning (SMEML), that strategically eliminates models that are unlikely to yield high accuracy.
+SMEML demonstrates the ability to achieve comparable accuracy to a traditional brute-force approach while significantly reducing the time required.
+We also believe this innovation is particularly beneficial to machine learning in healthcare, where efficient and accurate disease prediction is crucial.
 \end{abstract}
@@
 \subsection{Summary}
-SMEML manages to return comparable accuracy results to its dumb couterpart while more than splitting the run time in half in the majority of benchmarks.
-Its performance is not limited by the size of the dataset, and it returned its first, third, and fourth overall best run times for SMEML relative to the dumb mode on the 'large' dataset benchmarks (those exceeding 1000 rows).
-This is important in third world medicine where time is of the essence and there is a constant influx of new patient data.
-A practical demonsration of this software's real-world application can be found on our SmartDx website [23].
+SMEML consistently achieves comparable accuracy to its dumb counterpart while significantly reducing the time required to train the model.
+Notably, SMEML's performance is not limited by the size of the dataset, achieving its best runtimes--first, third, and fourth fastest overall--on 'large' datasets (those exceeding 1000 rows).
+This efficiency is important in third world medicine where there is a constant influx of new patient data that must be processed quickly.
+A practical demonstration of this software's real-world application can be found on our SmartDx website [23].
 Source code can be found at [24].
@@
 
-[21] fedesoriano, "Stroke Prediction Dataset" (dataset). \url{www.kaggle.com/fedesoriano/stroke-prediction-dataset}.
+[21] fedesoriano, "Stroke Prediction Dataset" (dataset). \url{https://kaggle.com/fedesoriano/stroke-prediction-dataset}.
 

### 2024-06-26 paper/paper.tex
new diagram
Update paper.tex

@@
 
-Machine learning (ML) is a type of artificial intelligence (AI) that uses searching and trend-determining to make predictions.
-ML algorithms are trained and tested on a given dataset to become "smarter".
-Once they've learned the patterns typical of that data, they can make predictions based on similar data.
-These algorithms also require additional processes, however, like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning.
-This makes the process complex and time-inefficient.
-To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks [1].
+Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning.
+To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks.
+These frameworks create comfortable environments for models to excel in.
+They handle missing values, preprocess data, and optimize training to ensure the best results [1].
 
@@
 We select the top models that have significantly better performance than other models.
-These models are stacked together to form the final model.
+These models are stacked together and compared to the best individual model.
+The final model is the better one out of these two.
 This process is shown in Figure 1.
@@
 Notably, SMEML's performance is not limited by the size of the dataset, achieving its best runtimes--first, third, and fourth fastest overall--on 'large' datasets (those exceeding 1000 rows).
-This efficiency is important in third world medicine where there is a constant influx of new patient data that must be processed quickly.
-A practical demonstration of this software's real-world application can be found on our SmartDx website [23].
-Source code can be found at [24].
+SMEML also chose several different kinds of algorithms rather than defaulting to industry-standard boosting algorithms [23].
+This efficiency and versatility is important in third world medicine where there is a constant influx of new patient data that must be processed quickly.
+A practical demonstration of this software's real-world application can be found on our SmartDx website [24].
+Source code can be found at [25].
 \subsection{Limitations}
@@
 
-[23] SmartDx Website. \url{https://smartdx.vercel.app/}.
+[23] Mayr, A. et al., "The Evolution of Boosting Algorithms From Machine Learning to Statistical Modelling." Methods Inf Med 2014; 53(06): 419-427. \url{https://doi.org/10.48550/arXiv.1403.1452}.
 
-[24] Github Repository. \url{https://github.com/ericspring08/SMEML-Paper}.
+[24] SmartDx Website. \url{https://smartdx.vercel.app/}.
+
+[25] Github Repository. \url{https://github.com/ericspring08/SMEML-Paper}.
 }

### 2024-06-26 paper/paper.tex
small changes

@@
 We considered 28 different models, including all supervised and semi-supervised sklearn [12] classification models and common boosting models such as XGBoost [13], LightGBM [14], and Catboost [15].
+The majority of these models are implemented in the frameworks mentioned in Table 1.
 
@@
 Notably, SMEML's performance is not limited by the size of the dataset, achieving its best runtimes--first, third, and fourth fastest overall--on 'large' datasets (those exceeding 1000 rows).
-SMEML also chose several different kinds of algorithms rather than defaulting to industry-standard boosting algorithms [23].
+SMEML also chose less common algorithms, such as selecting SGDClassifier for the Pima Indians Diabetes Dataset [19] rather than defaulting to industry-standard boosting algorithms [23].
 This efficiency and versatility is important in third world medicine where there is a constant influx of new patient data that must be processed quickly.

### 2024-06-27 paper/paper.tex
Update paper.tex

@@
 To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks.
-These frameworks create comfortable environments for models to excel in.
+These frameworks create comfortable environments in which models can excel.
 They handle missing values, preprocess data, and optimize training to ensure the best results [1].
@@
 
-Several observations were made from running these datasets.
-First, accuracy did not change for 4 of the 6 benchmarks.
+The first observation made was that accuracy did not change for 4 of the 6 benchmarks.
 The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively.
@@
 Future work will include increasing the size of the training set, implementing a fully fledged AutoML framework, and conducting a detailed experiment comparing SMEML to other popular AutoML frameworks.
-Furthermore, we will examine other types of machine learning such as regression and multiclass-classification.
 

### 2024-06-27 paper/paper.tex
small changes

--- 2024-06-26 paper/paper.tex
@@
 To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks.
-These frameworks create comfortable environments for models to excel in.
+These frameworks automate the complicated processes of producing effective ML models, making it more accessable to non-experts.
 They handle missing values, preprocess data, and optimize training to ensure the best results [1].
@@
 \subsection{Experiment Design}
-To evaluate our framework, we choose 5 different datasets of diverse size.
+To evaluate our framework, we choose six different datasets of diverse size.
 We ran SMEML on each dataset for 20 iterations of tuning.

### 2024-06-27 paper/paper.tex

--- 2024-06-27 paper/paper.tex
@@
 Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning.
+These frameworks automate the complicated processes of producing effective ML models, making it more accessable to non-experts.
 To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks.

### 2024-06-27 paper/paper.tex
Update paper.tex

@@
 Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning.
-These frameworks automate the complicated processes of producing effective ML models, making it more accessable to non-experts.
-To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks.
+AutoML frameworks automate the complicated processes of producing effective ML models, making it more accessable to non-experts.
 These frameworks create comfortable environments in which models can excel.

### 2024-06-27 paper/paper.tex
Update paper.tex

@@
 \end{table}
-We systematically review and compare five different AutoML frameworks, comparing every feature relevant to medical implementation in Table 1.
-Of these five, we wanted to take a closer look at four: FLAML, H2O, MLJAR, and TPOT.
-
-We can observe pros and cons in the four models' theoretical applications.
+We can observe pros and cons in four of the five models' theoretical applications (see Table 1).
 FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks.

### 2024-06-27 paper/paper.tex
some tense stuff

@@
 
-Through this survey, we uncovered a key continuity in these frameworks' design: frameworks must run all of their models to maximize accuracy at the expense of efficiency.
+Through this survey, we uncover a key continuity in these frameworks' design: frameworks must run all of their models to maximize accuracy at the expense of efficiency.
 Given the specific nature of certain tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful.
 Cutting these models completely, however, is not optimal, as they are the best option in a minority of cases.
-We hypothesized that using a combination of multi-layer machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on training without sacrificing accuracy.
+We hypothesize that using a combination of multi-layer machine learning implementation and meta-feature extraction would yield an equally versatile system that minimizes time spent on training without sacrificing accuracy.
 
@@
 
-We considered 28 different models, including all supervised and semi-supervised sklearn [12] classification models and common boosting models such as XGBoost [13], LightGBM [14], and Catboost [15].
+We consider 28 different models, including all supervised and semi-supervised sklearn [12] classification models and common boosting models such as XGBoost [13], LightGBM [14], and Catboost [15].
 The majority of these models are implemented in the frameworks mentioned in Table 1.
@@
 We choose medical datasets and focus our approach on binary classification.
-We extract the attributes in Table 2 from each dataset: which are the inputs for the boosting model.
-We then run a "dumb", brute-force framework that trains every model every each dataset.
+We extract the attributes in Table 2 from each dataset, which are the inputs for the boosting model.
+Then a "dumb", brute-force framework that trains every model on every dataset is run.
 The accuracy of every model is ranked, and every model is treated as a label with its value being its rank.
@@
 To evaluate our framework, we choose six different datasets of diverse size.
-We ran SMEML on each dataset for 20 iterations of tuning.
-We compared this against a "dumb" mode which simply runs every model on the dataset.
-We used the accuracy and time to train as our metrics.
+We run SMEML on each dataset for 20 iterations of tuning.
+We compare this against a "dumb" mode which simply runs every model on the dataset.
+We use the accuracy and time to train as our metrics.
 All experiments are run on an Ubuntu server with Intel Xeon E5520 @ 2.27GHz and 24GB of RAM.
@@
 The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively.
-Training time, however, favored SMEML in every trial.
-SMEML outperformed the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset.
+Training time, however, favores SMEML in every trial.
+SMEML outperforms the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset.
 Relative to the dummy's performance, a percent decrease in time to run for SMEML of at least 46.78\% could be seen, with a decrease of up to 69.22\% observerd as well.
-SMEML's worst performance by percent decrease was also the performance in which it returned perfect accuracy.
+SMEML's worst performance by percent decrease is also the performance in which it returned perfect accuracy.
 \section{Discussion}

### 2024-06-27 paper/paper.tex
changes

@@
 \begin{table}
-  \caption{Survey of Existing AutoML Frameworks}
+  \caption{Survey of Five Existing AutoML Frameworks. A common feature is that they all run every model to maximize accuracy.}
   \label{automl-survey}
@@
 \end{table}
+We systematically review and compare five differnet AutoML frameworks, comparing every feature relevant to medical implementation in Table 1.
 We can observe pros and cons in four of the five models' theoretical applications (see Table 1).
@@
 
-Through this survey, we uncover a key continuity in these frameworks' design: frameworks must run all of their models to maximize accuracy at the expense of efficiency.
+Through this survey, we uncover a key continuity in the above frameworks' design: these frameworks must run all of their models to maximize accuracy at the expense of efficiency.
 Given the specific nature of certain tabular data, there are some models that are less likely to perform well, thus running and training these models is wasteful.
@@
 Notably, SMEML's performance is not limited by the size of the dataset, achieving its best runtimes--first, third, and fourth fastest overall--on 'large' datasets (those exceeding 1000 rows).
-SMEML also chose less common algorithms, such as selecting SGDClassifier for the Pima Indians Diabetes Dataset [19] rather than defaulting to industry-standard boosting algorithms [23].
+SMEML also chose less common algorithms, such as selecting SGDClassifier for the Pima Indians Diabetes Dataset [19] rather than defaulting to industry-standard boosting algorithms [23] because it produced better accuracy.
+This showcases the advantages of SMEMl comparing to a simple selection of the most popular models that may work well for a majority of datasets, but not for some minority cases.
 This efficiency and versatility is important in third world medicine where there is a constant influx of new patient data that must be processed quickly.
@@
 \begin{ack}
-We would like to thank St. Mark's School of Texas for supporting this research.
+We would like to thank St. Mark's School of Texas for supporting the associated NASA Hunch project, where this research was initially motivated.
 \end{ack}

### 2024-06-27 paper/paper.tex
final draft

@@
 We systematically review and compare five differnet AutoML frameworks, comparing every feature relevant to medical implementation in Table 1.
-We can observe pros and cons in four of the five models' theoretical applications (see Table 1).
+We can observe pros and cons in their applications.
 FLAML uses blend search hyper-parameter optimization and focuses on lightweight models, making it quick and applicable to repetitive tasks.
-It supports user-specified imputation techniques for missing values and has an intuitive API, making it moderately user-friendly for healthcare workers [9].
+It supports user-specified input techniques for missing values and has an intuitive API, making it moderately user-friendly for healthcare workers [9].
 H2O has a wider variety of supported algorithms that may be appropriate for medical diagnosis, making it slower than FLAML on average.
 In one trial, more than half of FLAML's performances in one minute were better than or equal to H2O's performances in one hour [9].
-H2O has automatic and multi-faceted methods of dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5].
+H2O has automatic and multi-faceted methods for dealing with missing values and flexible interfaces in R and Python, making it intuitive for users [5].
 MLJAR uses advanced algorithms such as light gradient boosting and neural networks.
@@
 The other two benchmarks on eye states and diabetes prediction represented a loss of accuracy for SMEML by 0.13\% and 1.95\%, respectively.
-Training time, however, favores SMEML in every trial.
-SMEML outperforms the dummy framework by 173.96 seconds in its worst performance on the lung cancer trial and by 383.94 seconds in its best performance on the eye state dataset.
+Training time, however, favors SMEML in every benchmark.
+SMEML outperforms the dummy framework by 173.96 seconds in its worst performance on the lung cancer benchmark and by 383.94 seconds in its best performance on the eye state benchmark.
 Relative to the dummy's performance, a percent decrease in time to run for SMEML of at least 46.78\% could be seen, with a decrease of up to 69.22\% observerd as well.
@@
 Notably, SMEML's performance is not limited by the size of the dataset, achieving its best runtimes--first, third, and fourth fastest overall--on 'large' datasets (those exceeding 1000 rows).
-SMEML also chose less common algorithms, such as selecting SGDClassifier for the Pima Indians Diabetes Dataset [19] rather than defaulting to industry-standard boosting algorithms [23] because it produced better accuracy.
-This showcases the advantages of SMEMl comparing to a simple selection of the most popular models that may work well for a majority of datasets, but not for some minority cases.
+SMEML also chooses less common algorithms, such as selecting SGDClassifier for the Pima Indians Diabetes Dataset [19] rather than defaulting to industry-standard boosting algorithms [23] because SGDClassifier produces better accuracy.
+This showcases the advantages of SMEML compared to a simple selection of the most popular models that may work well for a majority of datasets, but not for a minority of cases.
 This efficiency and versatility is important in third world medicine where there is a constant influx of new patient data that must be processed quickly.
